### 2020-10-30 article/main.tex
lot of work!!!

\documentclass{article}

\usepackage{hyperref}
\usepackage{enumerate}
\usepackage{enumitem}
\usepackage{amssymb,amsmath,amsthm} %must be before unicode-math
\usepackage[mathletters]{ucs}
\DeclareUnicodeCharacter{8339}{_x}
\DeclareUnicodeCharacter{8345}{_n}
\DeclareUnicodeCharacter{7522}{_i}
\DeclareUnicodeCharacter{11388}{_j}
\DeclareUnicodeCharacter{7523}{_r}
\usepackage[utf8x]{inputenc}
\usepackage{bussproofs}
\usepackage{graphicx}
\usepackage{stmaryrd}
\usepackage[autosize]{dot2texi}
\usepackage{multicol}
\setlength{\multicolsep}{0pt}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows,tikzmark,decorations.pathreplacing,calc}
\usepackage{adjustbox}

% Title portion. Note the short title for running heads
\title{Solving smooth system of algebraic equations}
\author{Christophe Raffalli}

\newcommand{\interior}[1]{%
  #1^{\mathrm{o}}%
}
\newcommand{\cardinal}[1]{%
  \#{#1}%
}

\newtheorem{theo}{Theorem}
\newtheorem{nota}[theo]{Notation}
\newtheorem{defi}[theo]{Definition}
\newtheorem{prop}[theo]{Proposition}

% Document starts
\begin{document}

\maketitle

\begin{nota}
  We consider the real projective plane $Pⁿ(ℝ)$.
  When ${x ∈ ℝ^{n+1}}$, we write $\overline{x} = \{ λx, λ∈ℝ_* \} ∈
  Pⁿ(ℝ)$ the equivalent class of $x$. We define $πₙ:ℝ^{n+1} → Pⁿ(ℝ)$ the
  projection $x ↦ \overline{x}$.
  We use on $Pⁿ(ℝ)$ the measure induced by
  the chord metric of $Sⁿ(ℝ)$:
  $$d(\overline{x},\overline{y}) = \min\left(
  \left\|{x \over \|x\|} - {y \over \|y\|}\right\|, \left\|{x \over \|x\|} + {y \over \|y\|}\right\|\right) (∀\overline{x},\overline{y} ∈ Pⁿ(ℝ)).$$
\end{nota}

\begin{defi}
  A \emph{simplicial partition} of
  $Pⁿ(ℝ)$ is a finite set of closed simplices $(Δᵢ)_{i∈I}$ such that
  \begin{itemize}
  \item $⋃_{i∈I} Δᵢ = Pⁿ(ℝ)$,
  \item for all $i≠j ∈ I$, $Δᵢ ∩ Δⱼ$ is a common lower-dimensional facet of $Δᵢ$
    and $Δⱼ$.
  \end{itemize}
  We say that $Δᵢ$ and $Δⱼ$ are neighbour if $Δᵢ ∩ Δⱼ$ is infinite,
  i.e. contains at least two points. The neighbourhood
  relation
  is clearly reflexive and symmetric.
  For $i \in I$, we define $v(i) = \{ j \in I; \cardinal{Δᵢ ∩ Δⱼ} > 2\}$.
\end{defi}

\begin{defi}
  Let $ε$ be a positive real. A \emph{simplicial partition} $(Δᵢ)_{i∈I}$ of $Pⁿ(ℝ)$ is said to be
  $ε$-thin if for any $i,j ∈ I$, for any $x∈Δᵢ$ and $y ∈ Δⱼ$, if $d(x,y) <
  ε$, then $Δᵢ ∩ Δⱼ ≠ ∅$.
\end{defi}

\begin{prop}
  Any \emph{simplicial partition} $(Δᵢ)_{i∈I}$ of $Pⁿ(ℝ)$ is $ε$-thin for
  some $ε > 0$ small enough.
\end{prop}

\begin{proof}
  Take $ε = \displaystyle{\min_{i,j ∈ I, Δᵢ ∩ Δⱼ = ∅} d(Δᵢ,Δⱼ)}$ which is positive because $I$ is
  finite and for all $i ∈ I$, $Δᵢ$ is compact.
\end{proof}

plan: on prend p un polynome, qui ne s'annule pas au sommet des Δᵢ.
on définit f linéaire sur chaque $̣Δᵢ$ et qui coincide avec p au sommet des $Δᵢ$.

On définit $ε$ tel que $p$ et $f$ ne s'annule dans aucune boule centrée au
sommet d'un $Δᵢ$ et de rayon $ε$.

  Let $s:ℝ^{n+1} → ℝ$ a $C^∞$ map with support included in $B_ε(0)$ and such
  that $∫_{ℝ^{n+1}} s(t)dt = 1$ (1) for the usual measure $dt$ of $ℝ^{n+1}$.

  We define $g(x) = (f ∗ s)(x) = ∫_{ℝ^{n+1}} f(t)s(x-t) dt$ the convolution product of $f$ and
  $s$. $g$ is $C^∞$. $|f(x) - g(x)| = |∫_{ℝ^{n+1}} (f(x) - f(t))s(x-t) dt| <
  \max_{t∈B_ε(x)} |f(x) - f(t)| → 0$ when $ε → 0$.

  Finally, we define $gₜ = tg + (1 - t)p$.

  on montre que $f = 0$ et $g = 0$ sont homémorphes et
  que $g$ et $gₜ$ aussi si la condition sur les gradients est vérifié.

  Ce qui donne $f = 0$ et $p = 0$ homéomorphe.

\begin{defi}
   Let $Δ = (Δᵢ)_{i∈I}$ be  a \emph{simplicial partition} of $Pⁿ(ℝ)$, a
   \emph{$Δ$-piecewise linear map}
   is a map $f : ℝ^{n+1} → ℝ$ which is
continuous, piecewise linear and linear
  on each $πₙ^{-1}(Δᵢ)$ for $i ∈ I$.
\end{defi}

\begin{nota}
  For such a map, we write $∇ᵢf$ for $∇f(x)$, for any $x ∈
  \interior{Δᵢ}$. We also define $C_\epsilon f(x)$ the convex hull
  of $\{ ∇f(y), y∈Sⁿ(ℝ) ∩ B_ε(x))\}$. $Hᵢ$ is also a convex cone because $f$ is
  homogeneous.

\end{nota}
\begin{defi}
  We say that a $Δ$-map $f$ is smooth if for all $i ∈ I$, $Hᵢf$ does not
    contains $0$.
\end{defi}

\begin{prop}
  Let $Δ = (Δᵢ)_{i∈I}$ be  a \emph{simplicial partition} of $Pⁿ(ℝ)$ and
  let $f$ be a smooth \emph{$Δ$-map}.
  There exists $ε>0$ and a $C^∞$ function
  $f_ε : ℝ^{n+1} → ℝ$ such that
  \begin{itemize}
  \item $∀x ∈ Sⁿ, \|f(x) - f_ε(x)\| < ε$
  \item $∀i ∈ I, ∀x ∈ πₙ^{-1}(Δᵢ) ∩ Sⁿ(ℝ), ∇f_ε(x)$ is in $Hᵢ$. the convex hull of
    $\{ ∇f(x), x ∈ πₙ^{⁻1}(\interior{Δⱼ} ∩ B_ε(x)), Δᵢ ∩ Δⱼ ≠ 0\}$ where
    $B_ε(x)$ denotes the ball of $ℝ^{n+1}$ of radius $ε$ and center $x$.
  \end{itemize}
\end{prop}

\begin{proof}
  Let $s:ℝ^{n+1} → ℝ$ a $C^∞$ map with support included in $B_ε(x)$ and such
  that $∫_{ℝ^{n+1}} s(t)dt = 1$ (1) for the usual measure $dt$ of $ℝ^{n+1}$.

  We define $f_ε(x) = f ∗ s = ∫_{ℝ^{n+1}} f(t)s(x-t) dx$ the convolution product of $f$ and
  $s$. $f_ε$ is $C^∞$. $|f(x) - f_ε(x)| = |∫_{ℝ^{n+1}} (f(x) - f(t))s(x-t) dt| <
  \max_{t∈B_ε(x)} |f(x) - f(t)| → 0$.

  Finally, $∇f_ε(x) = ∫_{ℝ^{n+1}} f(t)∇s(x-t) dx = Σ_{i∈I(x)}∫_{Δᵢ} f(t)∇s(x-t) dx =
    Σ_{i∈I(x)}∫_{Δᵢ} ∇f(t)s(x-t) dx = Σ_{i∈I(x)} λᵢ ∇ᵢf$ with
    $λᵢ = ∫_{Δᵢ} s(x-t) dx$. By (1) we have $Σ_{i∈I(x)} λᵢ = 1$.

  \end{proof}

  \begin{prop}
    Let $p$ be an homogeneous polynomial in $n+1$ variables.
    Let $Δ$ be an ad
  \end{prop}
  \begin{proof}

  \end{proof}
\end{document}

### 2020-10-31 article/main.tex
progress on the article

@@
 \usepackage[mathletters]{ucs}
+\DeclareUnicodeCharacter{8348}{_t}
 \DeclareUnicodeCharacter{8339}{_x}
@@
 }
+\newcommand{\PNR}{{\cal P}^n(ℝ)}
+\newcommand{\SNR}{{\cal S}^n(ℝ)}
 
@@
 \begin{nota}
-  We consider the real projective plane $Pⁿ(ℝ)$.
+  We consider the real projective plane $\PNR$.
   When ${x ∈ ℝ^{n+1}}$, we write $\overline{x} = \{ λx, λ∈ℝ_* \} ∈
-  Pⁿ(ℝ)$ the equivalent class of $x$. We define $πₙ:ℝ^{n+1} → Pⁿ(ℝ)$ the
+  \PNR$ the equivalent class of $x$. We define $πₙ:ℝ^{n+1} → \PNR$ the
   projection $x ↦ \overline{x}$.
-  We use on $Pⁿ(ℝ)$ the measure induced by
-  the chord metric of $Sⁿ(ℝ)$:
+  We use on $\PNR$ the measure induced by
+  the chord metric of the unit sphere $\SNR$:
   $$d(\overline{x},\overline{y}) = \min\left(
-  \left\|{x \over \|x\|} - {y \over \|y\|}\right\|, \left\|{x \over \|x\|} + {y \over \|y\|}\right\|\right) (∀\overline{x},\overline{y} ∈ Pⁿ(ℝ)).$$
+  \left\|{x \over \|x\|} - {y \over \|y\|}\right\|, \left\|{x \over \|x\|} + {y
+    \over \|y\|}\right\|\right) (∀\overline{x},\overline{y} ∈ \PNR).$$
+
+  We write $\cardinal{S}$ the cardinal of a set $S$.
 \end{nota}
@@
   A \emph{simplicial partition} of
-  $Pⁿ(ℝ)$ is a finite set of closed simplices $(Δᵢ)_{i∈I}$ such that
+  $\PNR$ is a finite set of closed simplices $(Δᵢ)_{i∈I}$ such that
   \begin{itemize}
-  \item $⋃_{i∈I} Δᵢ = Pⁿ(ℝ)$,
-  \item for all $i≠j ∈ I$, $Δᵢ ∩ Δⱼ$ is a common lower-dimensional facet of $Δᵢ$
-    and $Δⱼ$.
+  \item $⋃_{i∈I} Δᵢ = \PNR$,
+  \item for all $i≠j ∈ I$, $Δᵢ ∩ Δⱼ$ is a included in an hyperplane of $\PNR$.
+  \item for all simplices in $Δ$, there is a projective plane of $\PNR$ that do
+    not meet $Δ$.
   \end{itemize}
   We say that $Δᵢ$ and $Δⱼ$ are neighbour if $Δᵢ ∩ Δⱼ$ is infinite,
-  i.e. contains at least two points. The neighbourhood
-  relation
-  is clearly reflexive and symmetric.
-  For $i \in I$, we define $v(i) = \{ j \in I; \cardinal{Δᵢ ∩ Δⱼ} > 2\}$.
+  i.e. contains at least two points. We do not consider simplices sharing only
+  on vertex to be neighbour.  The neighbourhood relation is clearly reflexive
+  and symmetric.  For $i \in I$, we define $V(i) = \{ j \in I; \cardinal{(Δᵢ ∩
+    Δⱼ)} > 2\}$.
 \end{defi}
@@
 \begin{defi}
-  Let $ε$ be a positive real. A \emph{simplicial partition} $(Δᵢ)_{i∈I}$ of $Pⁿ(ℝ)$ is said to be
-  $ε$-thin if for any $i,j ∈ I$, for any $x∈Δᵢ$ and $y ∈ Δⱼ$, if $d(x,y) <
-  ε$, then $Δᵢ ∩ Δⱼ ≠ ∅$.
+  Let $ε$ be a positive real. A \emph{simplicial partition} $(Δᵢ)_{i∈I}$ of $\PNR$ is said to be
+  $ε$-fat if for any $i,j ∈ I$, for any $x∈Δᵢ$ and $y ∈ Δⱼ$, if $d(x,y) <  ε$,
+  then $Δᵢ ∩ Δⱼ ≠ ∅$.
 \end{defi}
@@
 \begin{prop}
-  Any \emph{simplicial partition} $(Δᵢ)_{i∈I}$ of $Pⁿ(ℝ)$ is $ε$-thin for
+  Any \emph{simplicial partition} $(Δᵢ)_{i∈I}$ of $\PNR$ is $ε$-fat for
   some $ε > 0$ small enough.
@@
 
-plan: on prend p un polynome, qui ne s'annule pas au sommet des Δᵢ.
-on définit f linéaire sur chaque $̣Δᵢ$ et qui coincide avec p au sommet des $Δᵢ$.
-
-On définit $ε$ tel que $p$ et $f$ ne s'annule dans aucune boule centrée au
-sommet d'un $Δᵢ$ et de rayon $ε$.
-
-  Let $s:ℝ^{n+1} → ℝ$ a $C^∞$ map with support included in $B_ε(0)$ and such
-  that $∫_{ℝ^{n+1}} s(t)dt = 1$ (1) for the usual measure $dt$ of $ℝ^{n+1}$.
-
-  We define $g(x) = (f ∗ s)(x) = ∫_{ℝ^{n+1}} f(t)s(x-t) dt$ the convolution product of $f$ and
-  $s$. $g$ is $C^∞$. $|f(x) - g(x)| = |∫_{ℝ^{n+1}} (f(x) - f(t))s(x-t) dt| <
-  \max_{t∈B_ε(x)} |f(x) - f(t)| → 0$ when $ε → 0$.
-
-  Finally, we define $gₜ = tg + (1 - t)p$.
-
-  on montre que $f = 0$ et $g = 0$ sont homémorphes et
-  que $g$ et $gₜ$ aussi si la condition sur les gradients est vérifié.
-
-  Ce qui donne $f = 0$ et $p = 0$ homéomorphe.
-
 \begin{defi}
-   Let $Δ = (Δᵢ)_{i∈I}$ be  a \emph{simplicial partition} of $Pⁿ(ℝ)$, a
+   Let $Δ = (Δᵢ)_{i∈I}$ be  a \emph{simplicial partition} of $\PNR$, a
    \emph{$Δ$-piecewise linear map}
@@
 on each $πₙ^{-1}(Δᵢ)$ for $i ∈ I$.
+
+  For such a map, an for all $x ∈ π^{-1}Δᵢ$, we define $∇ᵢf(x) = ∇ᵢf = ∇f(y)$ for any $y ∈
+  π^{-1}\interior{Δᵢ}$. For
+  any point $x∈ℝ^{n+1}$, we define $∇_cf(x)$ the convex-hull of $\{∇ᵢf(x),
+  \hbox{ for } i \hbox{ s.t. } x ∈
+  π^{-1}Δᵢ\}$. For $x$ in $π^{-1}\interior{Δᵢ}$, $∇_cf(x) = \{∇f(x)\}$.
 \end{defi}
 
-\begin{nota}
-  For such a map, we write $∇ᵢf$ for $∇f(x)$, for any $x ∈
-  \interior{Δᵢ}$. We also define $C_\epsilon f(x)$ the convex hull
-  of $\{ ∇f(y), y∈Sⁿ(ℝ) ∩ B_ε(x))\}$. $Hᵢ$ is also a convex cone because $f$ is
-  homogeneous.
-
-\end{nota}
 \begin{defi}
-  We say that a $Δ$-map $f$ is smooth if for all $i ∈ I$, $Hᵢf$ does not
+  We say that a $Δ$-map $f$ is smooth if for all $x ∈ \PNR$, $∇_cf(x)$ does not
     contains $0$.
@@
 \begin{prop}
-  Let $Δ = (Δᵢ)_{i∈I}$ be  a \emph{simplicial partition} of $Pⁿ(ℝ)$ and
+  Let $Δ = (Δᵢ)_{i∈I}$ be a \emph{simplicial partition} of $\PNR$ and
   let $f$ be a smooth \emph{$Δ$-map}.
-  There exists $ε>0$ and a $C^∞$ function
-  $f_ε : ℝ^{n+1} → ℝ$ such that
+  For any $ε_M>0$ such that $Δ$ is $ε$-fat, there exists a family of $C^∞$ function
+  $ε ↦ f_ε : \SNR → ℝ$ such that
   \begin{itemize}
-  \item $∀x ∈ Sⁿ, \|f(x) - f_ε(x)\| < ε$
-  \item $∀i ∈ I, ∀x ∈ πₙ^{-1}(Δᵢ) ∩ Sⁿ(ℝ), ∇f_ε(x)$ is in $Hᵢ$. the convex hull of
-    $\{ ∇f(x), x ∈ πₙ^{⁻1}(\interior{Δⱼ} ∩ B_ε(x)), Δᵢ ∩ Δⱼ ≠ 0\}$ where
-    $B_ε(x)$ denotes the ball of $ℝ^{n+1}$ of radius $ε$ and center $x$.
+  \item $∀x ∈ \SNR, f(x) - f_ε(x) → 0$ when $ε → 0$
+  \item $∀i ∈ I, ∀x ∈ ℝ^{n+1}, ∇f_ε(x) ∈ ∇_cf(x)$.
+  \item All functions $f_ε$ and $f$ have homeomorphic zero level.
   \end{itemize}
@@
 \begin{proof}
-  Let $s:ℝ^{n+1} → ℝ$ a $C^∞$ map with support included in $B_ε(x)$ and such
-  that $∫_{ℝ^{n+1}} s(t)dt = 1$ (1) for the usual measure $dt$ of $ℝ^{n+1}$.
+  Let $B_r(x)$ denote the unit ball of center $x$ and radius $r$.
+  Let $s:ℝ^{n+1} → ℝ⁺$ a $C^∞$ map with support included in $B_1(x)$ and such
+  that $∫_{ℝ^{n+1}} s(t)dt = 1$ for the usual measure $dt$ of $ℝ^{n+1}$. We also
+  assume that $s(-x) = s(x)$.
+  We define $s_ε(x) = ε^{-n-1}s(ε^{-1} x)$, which has support in $B_ε(x)$ and
+  satisfies $∫_{ℝ^{n+1}} s_\epsilon(t)dt = 1$
 
-  We define $f_ε(x) = f ∗ s = ∫_{ℝ^{n+1}} f(t)s(x-t) dx$ the convolution product of $f$ and
-  $s$. $f_ε$ is $C^∞$. $|f(x) - f_ε(x)| = |∫_{ℝ^{n+1}} (f(x) - f(t))s(x-t) dt| <
-  \max_{t∈B_ε(x)} |f(x) - f(t)| → 0$.
+  We define $f_ε(x) = f ∗ s = ∫_{ℝ^{n+1}} f(x-t)s_ε(t) dt$ the convolution product of $f$ and
+  $s_{ε}$. $f_ε$ is $C^∞$ on $\SNR$. $|f(x) - f_ε(x)| = |∫_{ℝ^{n+1}} (f(x) - f(t))s_{ε}(x-t) dt| <
+  \max_{t∈B_ε(x)} |f(x) - f(t)| → 0$  when $ε → 0$ because $f$ is continuous.
 
-  Finally, $∇f_ε(x) = ∫_{ℝ^{n+1}} f(t)∇s(x-t) dx = Σ_{i∈I(x)}∫_{Δᵢ} f(t)∇s(x-t) dx =
-    Σ_{i∈I(x)}∫_{Δᵢ} ∇f(t)s(x-t) dx = Σ_{i∈I(x)} λᵢ ∇ᵢf$ with
-    $λᵢ = ∫_{Δᵢ} s(x-t) dx$. By (1) we have $Σ_{i∈I(x)} λᵢ = 1$.
+  Remark: $f_ε$ is not homogeneous, this is why we restrict its domain to
+  $\SNR$.
+
+  For the gradient, we have,
+  \begin{eqnarray*}
+    ∇f_ε(x) &=& ∇∫_{ℝ^{n+1}} f(x-t)s_{ε}(t) dt\cr
+     &=& ∇∫_{ℝ^{n+1}} f(u)∇s_{ε}(x-u) du\cr
+     &=& ∫_{ℝ^{n+1}} f(u)∇s_{ε}(x-u) du\cr
+    &=& Σ_{i∈V(x)}∫_{Δᵢ} f(x-t)∇s_{ε}(t) dt\cr
+    &=& Σ_{i∈v(x)}∫_{Δᵢ} ∇f(x-t)s_{ε}(t) dt\cr
+    &=& Σ_{i∈V(x)} λᵢ ∇ᵢf \hbox{ with } λᵢ = ∫_{Δᵢ} s_{ε}(x-t) dx > 0
+  \end{eqnarray*}
+
+  Hence $∇f_ε(x)$ is in the convex hull of the $∇ᵢf$ for $i ∈ V(x)$ because
+  $$Σ_{i∈I(x)} λᵢ = Σ_{i∈v(x)}∫_{Δᵢ} s_ε(x-t) dx =  1$$
+
+  To build the homeomorphism between the variaous zero levels, we consider the
+  following differential equation on for $γ(ε) : ℝ ↦ ℝ^{n+1}$:
+
+  $$ γ'(ε) = g(ε,γ(ε)) \hbox{ with } g(ε,x) = \frac{\frac{∂f_ε}{∂ε}(x) ∇f_ε(x)}{||∇f_ε(x)||} $$
+
+  The function $g$ is ${\cal
+    C}^∞$ for $0 < ε < ε_M$ and $x ∈ ℝ^{n+1}$ because $∇f_ε(x) ≠ 0$ on the
+  considered domain. the first thing to show it can be
+  prolongated to $ε = 0$. We have
+
+  \begin{eqnarray*}
+    ∇s_ε(x) &=& ∇(ε\|x\|)^{-n-1} s((ε\|x\|)^{-1}x) \cr
+                    &=& (-n-1) (ε\|x\|)^{-n-2} s((ε\|x\|)^{-1}x)
+    }\frac{x}{\|x\|} \cr
+     && + (ε\|x\|)^{-n-1} ∇s((ε\|x\|)^{-1}x) \left((ε\|x\|)^{-1} -
+      (ε\|x\|)^{-2}  \frac{x}{\|x\|}\right) \cr
+     && + (ε\|x\|)^{-n-1} ∇s((ε\|x\|)^{-1}x) \left((ε\|x\|)^{-1} -
+      (ε\|x\|)^{-2}\right)  \frac{x}{\|x\|} \cr
+  \end{eqnarray*}
+  \begin{eqnarray*}
+    \frac{∂}{∂ε} s_{ε\|x\|}(x-t)
+      &=& \frac{∂}{∂ε} (ε\|x\|)^{-n-1} s((ε\|x\|)^{-1}(x-t)) \cr
+    &=& \frac{∂}{∂ε} (-n-1)\|x\|(ε\|x\|)^{-n-2} s((ε\|x\|)^{-1}(x-t))
+                      - ε^{-1}(ε\|x\|)^{-n-2} ∇s((ε\|x\|)^{-1}(x-t)).(x-t)\cr
+    &=& \frac{∂}{∂ε} (-n-1)ε s_ε(x-t)
+                      - ε^{-1}(ε\|x\|)^{-n-2} ∇s((ε\|x\|)^{-1}(x-t)).(x-t)\cr
+  \end{eqnarray*}
+
+    \begin{eqnarray*}
+    \frac{∂f_ε(x)}{∂ε} &=& \frac{∂}{∂ε} ∫_{ℝ^{n+1}} f(x-t)s_{ε}(t) dt \cr
+    &=& \frac{∂}{∂ε} ∫_{ℝ^{n+1}} f(t)s_{ε\|x\|}(x-t) dt \cr
+    &=&  \frac{∂}{∂ε} Σ_{i∈V(x)} ∫_{Δᵢ} f(t)s_{ε\|x\|}(x-t) du \cr
+    &=&  Σ_{i∈V(x)} ∫_{Δᵢ} f(t) \frac{∂}{∂ε} s_{ε\|x\|}(x-t) du \cr
+       &=& Σ_{i∈V(x)}∫_{Δᵢ} f(x-t) s_{ε\|x\|}(t) dt
+  \end{eqnarray*}
 

### 2021-01-14 article/main.tex
work on article

--- 2020-10-30 article/main.tex
@@
 \usepackage[mathletters]{ucs}
+\DeclareUnicodeCharacter{8348}{_t}
+\DeclareUnicodeCharacter{8342}{_k}
 \DeclareUnicodeCharacter{8339}{_x}
@@
 \DeclareUnicodeCharacter{7523}{_r}
+\DeclareUnicodeCharacter{7580}{^c}
+\DeclareUnicodeCharacter{7496}{^d}
 \usepackage[utf8x]{inputenc}
-\usepackage{bussproofs}
 \usepackage{graphicx}
@@
 \newcommand{\cardinal}[1]{%
-  \#{#1}%
+  \#({#1})%
 }
+\newcommand{\hull}[1]{%
+  \mathcal H({#1})%
+}
+\newcommand{\cone}[1]{%
+  \mathcal C({#1})%
+}
+\newcommand{\vertices}[1]{%
+  \mathcal V({#1})%
+}
+\newcommand{\ball}[2]{%
+  \mathcal B_{#2}({#1})%
+}
+
+\newcommand{\PNR}{{\cal P}^n(ℝ)}
+\newcommand{\SNR}{{\cal S}^n(ℝ)}
 
@@
 \newtheorem{prop}[theo]{Proposition}
+\newtheorem{exam}[theo]{Example}
 
@@
 
-\begin{nota}
-  We consider the real projective plane $Pⁿ(ℝ)$.
-  When ${x ∈ ℝ^{n+1}}$, we write $\overline{x} = \{ λx, λ∈ℝ_* \} ∈
-  Pⁿ(ℝ)$ the equivalent class of $x$. We define $πₙ:ℝ^{n+1} → Pⁿ(ℝ)$ the
-  projection $x ↦ \overline{x}$.
-  We use on $Pⁿ(ℝ)$ the measure induced by
-  the chord metric of $Sⁿ(ℝ)$:
+\section{Introduction}
+
+\section{Conventions and notations}
+
+We consider the real projective plane $\PNR$.
+ We define $πₙ:ℝ^{n+1}∖\{0\} → \PNR$ the
+projection $x ↦  \{ λx, λ∈ℝ^⋆ \} ∈ \PNR$. To simplify, we often write $\overline{x}$ for $πₙ(x)$.
+
+We use on $\PNR$ and $\SNR$ the measure induced by
+the chord metric of the unit sphere:
 $$d(\overline{x},\overline{y}) = \min\left(
-  \left\|{x \over \|x\|} - {y \over \|y\|}\right\|, \left\|{x \over \|x\|} + {y \over \|y\|}\right\|\right) (∀\overline{x},\overline{y} ∈ Pⁿ(ℝ)).$$
-\end{nota}
+\left\|{x \over \|x\|} - {y \over \|y\|}\right\|, \left\|{x \over \|x\|} + {y
+  \over \|y\|}\right\|\right) (∀\overline{x},\overline{y} ∈ \PNR).$$
+
+If $x ∈ \PNR$ (resp. $ℝ^{n+1}$), $\ball{x}{r}$ denotes the closed ball of center $x$
+and radius $r$.
+
+We write $\cardinal{S}$ the cardinal of a set $S$.
+
+For $A ⊂ ℝ^{n+1}$, $\hull{A}$ denotes the convex hull of $A$ and $\cone{A}$ its
+convex cone.
+
+We use the following notation for simplices:
+\begin{itemize}
+\item If $Δ ⊂ \PNR$ is a simplex, we denote $\vertices{Δ} ⊂ \SNR$ a finite set of
+  represents of the vertices of $Δ$.
+\item $\vertices{Δ}$ must verify that $Δ = πₙ(\hull{\vertices{Δ}})$. This is why we take $\vertices{Δ} ⊂
+    \SNR$ instead of $\vertices{Δ} ⊂ \PNR$ as the convex hull is not well defined in
+    the projective plane.
+\item Simplices should not be too big, in particular, $\PNR$ is not a simplex!
+  For this we require $\vertices{Δ}$ to fit in an open half space of
+  $\SNR$. If this is not possible, we consider that $Δ$ is not a simplex.
+\item We take $\vertices{Δ}$ to be minimal and consider only non degenerated simplex: removing one point in
+    $\vertices{Δ}$
+    changes it convex hull and the dimension of the
+    simplex $Δ$ is always exactly $\cardinal{\vertices{Δ} - 1}$. This also means that
+    $\vertices{Δ}$ is the set of extremal points of its convex hull.
+  \item Because we require simplices to be not too big $πₙ^{-1}(Δ)$ has exactly two connected components:
+    $$πₙ^{-1}(Δ) = \cone{\vertices{Δ}} ∪ -\cone{\vertices{Δ}}.$$
+    We write $Δ⁺ =  \cone{\vertices{Δ}}$ and $Δ⁻ = - Δ⁺$. Here $-A$ denotes
+    $\{-x, x ∈ A\}$.
+
+\end{itemize}
+
+\section{Simplicial partition}
 
@@
   A \emph{simplicial partition} of
-  $Pⁿ(ℝ)$ is a finite set of closed simplices $(Δᵢ)_{i∈I}$ such that
+  $\PNR$ is a finite set of closed simplices $(Δᵢ)_{i∈I}$ such that
   \begin{itemize}
-  \item $⋃_{i∈I} Δᵢ = Pⁿ(ℝ)$,
-  \item for all $i≠j ∈ I$, $Δᵢ ∩ Δⱼ$ is a common lower-dimensional facet of $Δᵢ$
-    and $Δⱼ$.
+  \item Each $Δᵢ$ is a simplex of dimension $n$, i.e. $\cardinal{\vertices{Δ}} = n + 1$.
+  \item $⋃_{i∈I} Δᵢ = \PNR$,
+  \item For all $i₁ < i₂ < \dots iₖ ∈ I$, $Δ_{i₁} ∩ \dots ∩ Δ_{iₖ}$ is empty or is a simplex of dimension at most
+    $n-k+1$ and $πₙ(\vertices{Δ_{i₁} ∩ \dots ∩ Δ_{iₖ}}) =
+    πₙ(\vertices{Δ_{i₁}}) ∩ \dots ∩ πₙ(\vertices{Δ_{iₖ}})$.
+    We can not require  $\vertices{Δᵢ ∩ Δⱼ} = \vertices{Δᵢ} ∩ \vertices{Δⱼ}$ because we may have $x ∈
+    \vertices{Δᵢ}$ and $y ∈ \vertices{Δⱼ}$ with $x ≠ y$ and $\overline{x} = \overline{y}$ (see
+    the example below). This conditions ensures that the intersection of
+    simplices are exactly faces of lower dimensions defined by the common vertices.
+%  \item We say that $Δᵢ$ and $Δⱼ$ are neighbour if $Δᵢ ∩ Δⱼ ≠ ∅$. The neighbourhood relation is clearly reflexive and symmetric.
   \end{itemize}
-  We say that $Δᵢ$ and $Δⱼ$ are neighbour if $Δᵢ ∩ Δⱼ$ is infinite,
-  i.e. contains at least two points. The neighbourhood
-  relation
-  is clearly reflexive and symmetric.
-  For $i \in I$, we define $v(i) = \{ j \in I; \cardinal{Δᵢ ∩ Δⱼ} > 2\}$.
 \end{defi}
 
-\begin{defi}
-  Let $ε$ be a positive real. A \emph{simplicial partition} $(Δᵢ)_{i∈I}$ of $Pⁿ(ℝ)$ is said to be
-  $ε$-thin if for any $i,j ∈ I$, for any $x∈Δᵢ$ and $y ∈ Δⱼ$, if $d(x,y) <
-  ε$, then $Δᵢ ∩ Δⱼ ≠ ∅$.
+Here is as example a partition of $\PNR$ with $2ⁿ$ simplices:
+\begin{exam}\label{init_part}
+Consider $B = \{x₀,\dots,xₙ\}$, the canonical base of $ℝ^{n+1}$ and
+$(εᵢ)_{i ∈ \{1,\dots,2ⁿ\}}$ an enumeration of all sequences of length $n$ of
+$1$ or $-1$. Then, we define $(Δᵢ)_{i∈\{1,\dots,2ⁿ\}}$ by
+$$Δᵢ = πₙ(\hull{\{x₀,ε_{i,1} x₁, \dots, ε_{i,n} xₙ\}}).$$
+\end{exam}
+
+We remark in this example, that all simplices use $B$ as set of vertices. This
+means that for all $i < j ∈ \{1,\dots,2ⁿ\}$, we have
+  $πₙ(\vertices{Δᵢ}) = πₙ(\vertices{Δⱼ}) = πₙ(B)$ while $\vertices{Δᵢ} ≠ \vertices{Δⱼ}$.
+
+In this examples, we have
+\begin{eqnarray*}
+  Δ⁺ᵢ &=& \cone{\{x₀,ε_{i,1} x₁, \dots, ε_{i,n} xₙ\}} \cr
+  Δ⁻ᵢ &=& \cone{\{-x₀,-ε_{i,1} x₁, \dots, -ε_{i,n} xₙ\}} \cr
+\end{eqnarray*}
+
+\begin{defi} Let $(Δᵢ)_{i∈I}$ be a simplicial partition of $\PNR$. For $x ∈
+  ℝ^{n+1} ∖\{0\}$ we define
+  $I^Δ(x) = \{(i,σ) ∈ I × \{-,+\}, x ∈ Δᵢ^σ\}$ and
+  $I^Δ_ε(x) = \{(i,σ) ∈ I × \{-,+\}, Δᵢ^σ ∩ \ball{x}{ε\|x\|} ≠ ∅\}$. In general we only use one
+  simplicial partition at a time and we simply write $I(x)$ and $I_ε(x)$.
 \end{defi}
 
+\begin{prop}\label{Ihomo}
+  Let $(Δᵢ)_{i∈I}$ be a simplicial partition of $\PNR$.
+  For $x ∈  ℝ^{n+1} ∖\{0\}$ and $λ > 0$, we have $I(λx) = I(x)$ and $I_ε(λx) = I_ε(x)$.
+\end{prop}
+
+\begin{proof}
+  From the fact that the set $Δᵢ^σ$ are convex cones.
+\end{proof}
+
 \begin{prop}
-  Any \emph{simplicial partition} $(Δᵢ)_{i∈I}$ of $Pⁿ(ℝ)$ is $ε$-thin for
+  Let $(Δᵢ)_{i∈I}$ be a simplicial partition of $\PNR$.
+  For any $x ∈ ℝ^{n+1} ∖\{0\}$, if $ε>0$ is small enough, then $I_ε(x) = I(x)$.
+\end{prop}
+
+\begin{proof}
+  Take $ε < \min_{(i,σ) ∉ I(x)} d(x,Δᵢ^σ)$, then we have $I_ε(x) = I(x)$.
+\end{proof}
+
+\begin{defi}
+  Let $ε$ be a positive real. A \emph{simplicial partition} $(Δᵢ)_{i∈I}$ of
+  $\PNR$ is said to be $ε$-fat if for all $x ∈ ℝ^{n+1} ∖\{0\}$ we have:
+$$ ⋂_{(i,σ) ∈ I_ε(x)} Δᵢ^σ ≠ ∅$$
+\end{defi}
+
+\begin{prop} If a simplicial partition $(Δᵢ)_{i∈I}$ is $ε$-fat for $ε > 0$
+  then it is $η$-fat if $0 < η ≤ ε$.
+\end{prop}
+
+\begin{proof} From the fact that for $x ∈ ℝ^{n+1} ∖\{0\}$, $I_η(x) ⊆ I_ε(x)$ if $η ≤ ε$.
+\end{proof}
+
+\begin{prop}
+  Any \emph{simplicial partition} $(Δᵢ)_{i∈I}$ of $\PNR$ is $ε$-fat for
   some $ε > 0$ small enough.
@@
 \begin{proof}
-  Take $ε = \displaystyle{\min_{i,j ∈ I, Δᵢ ∩ Δⱼ = ∅} d(Δᵢ,Δⱼ)}$ which is positive because $I$ is
-  finite and for all $i ∈ I$, $Δᵢ$ is compact.
+  First, thanks to proposition \ref{Ihomo}, we only have to check the condition
+  for $ε$-fatness in $\SNR$.
+
+  Consider a set $J ⊂ I × \{-,+\}$ with $⋂_{(i,σ)∈J} Δⱼ^σ = ∅$ (1), we first
+  prove that there exists $ε_J > 0$ such that for all $x ∈ \SNR$, $J \not⊆
+  I_{ε_J}(x)$. For this we assume the contrary: For any $ε>0$ there exists $x_ε
+  ∈ \SNR$ such that $J ⊆ I_{ε}(x_ε)$. As $\SNR$ is compact, we can extract a
+  sequence $(εₙ,xₙ)_{n ∈ \mathbb N}$ which converges to $(0,x)$ for some $x ∈
+  \SNR$, with $J ⊆ I_{εₙ}(x_{εₙ})$ for all $n ∈ \mathbb N$. Thus, for any $(i,σ)
+  ∈ J$ and $n ∈ \mathbb N$, we have $\ball{xₙ}{εₙ} ∩ Δᵢ^σ ≠ ∅$ which implies
+  $d(xₙ,Δᵢ^σ) < εₙ$. As $Δᵢ^σ$ are closed convex cone, this implies that $x ∈
+  Δᵢ^σ$ for any $(i,σ) ∈ J$ which contradicts the hypothesis (1).
+
+  We end the proof by remarking that the simplicial partition is $ε$-fat if we
+  take $ε$ the minimum of all $ε_J$ for $J ⊂ I$ with $∩_{(i,σ)∈J} Δᵢ^σ =
+  ∅$. This is well defined as $I$ hence his power-set are finite. Indeed, if $J
+  = I_{ε}(x)$, and $∩_{(i,σ)∈J} Δᵢ^σ = ∅$, then $J \not ⊆ I_{ε_J}(x) ⊇ I_{ε}(x)
+  = J$ which is contradictory.
 \end{proof}
 
-plan: on prend p un polynome, qui ne s'annule pas au sommet des Δᵢ.
-on définit f linéaire sur chaque $̣Δᵢ$ et qui coincide avec p au sommet des $Δᵢ$.
-
-On définit $ε$ tel que $p$ et $f$ ne s'annule dans aucune boule centrée au
-sommet d'un $Δᵢ$ et de rayon $ε$.
-
-  Let $s:ℝ^{n+1} → ℝ$ a $C^∞$ map with support included in $B_ε(0)$ and such
-  that $∫_{ℝ^{n+1}} s(t)dt = 1$ (1) for the usual measure $dt$ of $ℝ^{n+1}$.
-
-  We define $g(x) = (f ∗ s)(x) = ∫_{ℝ^{n+1}} f(t)s(x-t) dt$ the convolution product of $f$ and
-  $s$. $g$ is $C^∞$. $|f(x) - g(x)| = |∫_{ℝ^{n+1}} (f(x) - f(t))s(x-t) dt| <
-  \max_{t∈B_ε(x)} |f(x) - f(t)| → 0$ when $ε → 0$.
-
-  Finally, we define $gₜ = tg + (1 - t)p$.
-
-  on montre que $f = 0$ et $g = 0$ sont homémorphes et
-  que $g$ et $gₜ$ aussi si la condition sur les gradients est vérifié.
-
-  Ce qui donne $f = 0$ et $p = 0$ homéomorphe.
+\section{Δ-linear approximation of a polynomial}
 
 \begin{defi}
-   Let $Δ = (Δᵢ)_{i∈I}$ be  a \emph{simplicial partition} of $Pⁿ(ℝ)$, a
-   \emph{$Δ$-piecewise linear map}
-   is a map $f : ℝ^{n+1} → ℝ$ which is
-continuous, piecewise linear and linear
-  on each $πₙ^{-1}(Δᵢ)$ for $i ∈ I$.
+Let $p$ be an homogeneous polynomial of degree $d$ on
+$ℝ^{n+1}$. Let $(Δᵢ)_{i∈I}$ be a simplicial partition of $\PNR$.
+We define $\overline{p} : ℝ^{n+1} → ℝ$, the \emph{$Δ$-linear approximation of $p$},
+the piecewice linear function
+that is linear on all $Δ^σᵢ$ for $i ∈ I$, $σ ∈ \{+,-\}$, and equal to $p$
+on all points in $\vertices{Δ}$.
+
+For $i ∈ I$, $σ ∈ \{+,-\}$, we define $∇ᵢ^σp = ∇\overline{p}(x)$
+for any $x ∈ Δ^σᵢ$, as the gradient is constant over $Δ^σᵢ$ for a linear function.
 \end{defi}
 
-\begin{nota}
-  For such a map, we write $∇ᵢf$ for $∇f(x)$, for any $x ∈
-  \interior{Δᵢ}$. We also define $C_\epsilon f(x)$ the convex hull
-  of $\{ ∇f(y), y∈Sⁿ(ℝ) ∩ B_ε(x))\}$. $Hᵢ$ is also a convex cone because $f$ is
-  homogeneous.
+Remark: if $d$ is even (resp. odd), $\overline{p}$ is even (resp. odd).
 
-\end{nota}
 \begin{defi}
-  We say that a $Δ$-map $f$ is smooth if for all $i ∈ I$, $Hᵢf$ does not
-    contains $0$.
+Let $p$ be an homogeneous polynomial of degree $d$ on
+$ℝ^{n+1}$. Let $(Δᵢ)_{i∈I}$ be an $ε$-fat simplicial partition of $\PNR$.
+Let $\overline{p}$ be the $Δ$-linear approximation of $p$.
+We define the condition $Π_ε(x)$ to be true if and only if $p$ and
+$\overline{p}$ are both positive or both negative on $\ball{x}{ε}$.
+\end{defi}
+
+\begin{prop}\label{adaptedeq}
+Let $p$ be an homogeneous polynomial of degree $d$ on
+$ℝ^{n+1}$. Let $(Δᵢ)_{i∈I}$ be an $ε$-fat simplicial partition of $\PNR$.
+Let $\overline{p}$ be the $Δ$-linear approximation of $p$.
+
+The following conditions are equivalent:
+\begin{enumerate}
+\item $∀x ∈  ℝ^{n+1}∖\{0\}, Π_ε(x) \hbox{ or } 0 ∉ \cone{\{∇p(x)\} ∪ \{∇ᵢ^σp, (i,σ) ∈ I_ε(x)\}}$
+\item $∀x ∈  ℝ^{n+1}∖\{0\}, Π_ε(x) \hbox{ or } 0 ∉ \hull{\{∇p(x)\} ∪ \{∇ᵢ^σp, (i,σ) ∈ I_ε(x)\}}$
+\item $∀x ∈  \SNR, Π_ε(x) \hbox{ or } 0 ∉ \cone{\{∇p(x)\} ∪ \{∇ᵢ^σp, (i,σ) ∈ I_ε(x)\}}$
+\item $∀x ∈  \SNR, Π_ε(x) \hbox{ or } 0 ∉ \hull{\{∇p(x)\} ∪ \{∇ᵢ^σp, (i,σ) ∈ I_ε(x)\}}$
+\item\label{hb} $∀x ∈  ℝ^{n+1}∖\{0\}, Π_ε(x) \hbox{ or } ∃d ∈ ℝ^{n+1}∖\{0\},
+  \left\{\begin{array}{l} d.∇p(x) > 0 \hbox{ and}\cr
+    ∀(i,σ) ∈ I_ε(x), d.∇ᵢ^σp > 0
+  \end{array}\right.$
+\end{enumerate}
+\end{prop}
+
+\begin{proof}
+  The equivalences (1) ↔ (2) and (3) ↔ (4) are a general property of convex hull
+  and convex cone: for any set $X ⊂ ℝ^{n+1}$, $0 ∈ \hull{X} ↔ 0 ∈ \cone{X}$.
+  %Left to right is because $\hull{X} ⊆ \cone{X}$. For right to left, if $0 ∈
+  %\cone{X}$, if means we write $0 = λᵢ x₁ + \dots + λₙ xₙ$ with $λᵢ > 0$ and
+  %$xᵢ ∈ X$ for $1 < i < n$. Hence, taking $μᵢ = \frac{λᵢ}{λᵢ + \dots + λₙ}$, we
+  %have $0 = μᵢ x₁ + \dots + μₙ xₙ$ with $μ₁ + \dots + μₙ = 1$ and $μᵢ > 0$, $xᵢ
+  %∈ X$ for $1 < i < n$.
+
+  The equivalence (1)  ↔ (3) comes from the fact that $p$ is homogeneous hence
+  $\nabla(p)(λx) = λ^{d-1}\nabla(p)(x)$ for $λ > 0$ and from proposition $\ref{Ihomo}$.
+
+  The equivalence (2) ↔ (5) is a form of Han-Banach theorem \cite{?}.
+\end{proof}
+
+\begin{defi}
+Let $p$ be an homogeneous polynomial of degree $d$ on
+$ℝ^{n+1}$. Let $(Δᵢ)_{i∈I}$ be an $ε$-fat simplicial partition of $\PNR$.
+
+We say that the partition is \emph{adapted} to $p$ if it satisfies the condition
+of proposition \ref{adaptedeq}.
 \end{defi}
@@
 \begin{prop}
-  Let $Δ = (Δᵢ)_{i∈I}$ be  a \emph{simplicial partition} of $Pⁿ(ℝ)$ and
-  let $f$ be a smooth \emph{$Δ$-map}.
-  There exists $ε>0$ and a $C^∞$ function
-  $f_ε : ℝ^{n+1} → ℝ$ such that
-  \begin{itemize}
-  \item $∀x ∈ Sⁿ, \|f(x) - f_ε(x)\| < ε$
-  \item $∀i ∈ I, ∀x ∈ πₙ^{-1}(Δᵢ) ∩ Sⁿ(ℝ), ∇f_ε(x)$ is in $Hᵢ$. the convex hull of
-    $\{ ∇f(x), x ∈ πₙ^{⁻1}(\interior{Δⱼ} ∩ B_ε(x)), Δᵢ ∩ Δⱼ ≠ 0\}$ where
-    $B_ε(x)$ denotes the ball of $ℝ^{n+1}$ of radius $ε$ and center $x$.
-  \end{itemize}
+  Let $p$ be an homogeneous polynomial of degree $d$ on
+$ℝ^{n+1}$.
+  Let $(Δᵢ)_{i∈I}$ be an $ε$-fat simplicial partition of $\PNR$ adapted to $p$.
+  We can find a $C^∞$ function $d$ in $ℝ^{n+1} ∖ \{0\} → ℝ^{n+1}∖\{0\} $
+  and $μ > 0$ such that:
+$$∀x ∈  ℝ^{n+1}∖\{0\}, d(x).∇p(x) > μ\|x\|^{d-1} \hbox{ and }∀(i,σ) ∈
+  I_ε(x), d(x).∇ᵢ^σp > μ.$$
 \end{prop}
@@
 \begin{proof}
-  Let $s:ℝ^{n+1} → ℝ$ a $C^∞$ map with support included in $B_ε(x)$ and such
-  that $∫_{ℝ^{n+1}} s(t)dt = 1$ (1) for the usual measure $dt$ of $ℝ^{n+1}$.
+From proposition \ref{adaptedeq}.\ref{hb}, for any $x ∈ ℝ^{n+1}∖\{0\}$, we find $d₀(x)
+∈ ℝ^{n+1}$ such that $d₀(x).∇p(x) > 0$ and $∀(i,σ) ∈ I_ε(x), d₀(x).∇ᵢ^σp > 0.$.
+We can also assume that $d₀(λ x) = d₀(x)$ for $λ > 0$ for the same reason as in
+the proof of $(1) ↔ (3)$ above.
 
-  We define $f_ε(x) = f ∗ s = ∫_{ℝ^{n+1}} f(t)s(x-t) dx$ the convolution product of $f$ and
-  $s$. $f_ε$ is $C^∞$. $|f(x) - f_ε(x)| = |∫_{ℝ^{n+1}} (f(x) - f(t))s(x-t) dt| <
-  \max_{t∈B_ε(x)} |f(x) - f(t)| → 0$.
+We start with the following lemma: for each $x ∈
+ℝ^{n+1}∖\{0\}$, we find $0 < η(x) < ε$ such that
+$∀y ∈ \ball{x}{2η(x)}$, $d₀(x).∇p(y) > 0$ and $∀(i,σ) ∈ I_ε(y),
+d₀(x).∇ᵢ^σp > 0.$.
 
-  Finally, $∇f_ε(x) = ∫_{ℝ^{n+1}} f(t)∇s(x-t) dx = Σ_{i∈I(x)}∫_{Δᵢ} f(t)∇s(x-t) dx =
-    Σ_{i∈I(x)}∫_{Δᵢ} ∇f(t)s(x-t) dx = Σ_{i∈I(x)} λᵢ ∇ᵢf$ with
-    $λᵢ = ∫_{Δᵢ} s(x-t) dx$. By (1) we have $Σ_{i∈I(x)} λᵢ = 1$.
+First, $(i,σ) ∈ I_ε(y) ↔ \ball{y}{ε} ∩ Δᵢ^σ ≠ ∅$ is a closed condition and the
+contrary is an open condition. Hence, for $x ∈ℝ^{n+1}∖\{0\}$, we find $η > 0$
+small enough to have $y ∈
+\ball{x}{2η}$ gives $(i,σ) ∉ I_ε(x)$ implies $(i,σ) ∉ I_ε(y)$, which means that
+for $y ∈ \ball{x}{2η}$, we have $I_ε(y) ⊆ I_ε(x)$ and therefore,
 
+$$∀y ∈ \ball{x}{2η(x)}, ∀(i,σ) ∈ I_ε(y), d₀(x).∇ᵢ^σp > 0.$$
+
+Second, $∇p(x)$ is continuous, thus for  $x ∈ℝ^{n+1}∖\{0\}$, we find $η > 0$
+small enough to have $y ∈ \ball{x}{2η}$
+implies $d₀(x).∇p(y) > 0$. Grouping both results yields the wanted real $η(x)$
+such that
+
+$$∀x ∈ℝ^{n+1}∖\{0\}, ∀y ∈ \ball{x}{2η(x)},
+\left\{\begin{array}{l} d₀(x).∇p(y) > 0 \hbox{ and}\cr
+∀(i,σ) ∈ I_ε(y), d₀(x).∇ᵢ^σp > 0
+\end{array}\right.
+$$
+
+Now, for $x ∈ \SNR$, the balls $\ball{x}{η(x)}$ cover $\SNR$, so we can
+find a finite family $(xⱼ)_{j∈J}$ such that the balls $\ball{x}{η(xⱼ)}$ cover
+$\SNR$. We also take $η = min_{j ∈ J} η(xⱼ)$.
+
+Nest, for each $xⱼ ∈ \SNR$, $j ∈ J$, we choose a measurable set
+$Dⱼ ⊂ \ball{x}{η(xⱼ)}$ such that $\SNR$ is a disjoin union of all
+$Dⱼ$. And we define $d₁ : \SNR → ℝ^{n+1}∖\{0\}$ with $d₁(x) = d₀(xⱼ)$ if $x ∈ Dⱼ$.
+
+We choose $s : ℝ^{n+1} → ℝ$, a $C^∞$ function with support in
+$\ball{0}{1}$ and $∫_{ℝ^{n+1}} s(t) dt = 1$ for the standard measure $dt$
+on $ℝ^{n+1}$.
+
+We define
+
+$$ d : \SNR → ℝ^{n+1}∖\{0\} \hbox{ with } d(x) = ∫_{ℝ^{n+1}} d₁(x - η t)
+s(t) dt$$
+
+Similarly to a convolution product, we have $d(x) = ∫_{ℝ^{n+1}} η^{n +1} d₁(u)
+s(\frac{x - u}{η}) du$ and therefore $d$ is $C^∞$ on $\SNR$.
+
+Moreover, if we take $x ∈ \SNR$, we can write
+$$ d(x) = Σ_{j∈J} d₁(xⱼ) ∫_{x - η t ∈ Dⱼ} s(t) dt$$
+
+Let us define $λⱼ(x) = ∫_{x - η t ∈ Dⱼ} s(t) dt$. As $Dⱼ ⊂ \ball{xⱼ}{η(xⱼ)}$,
+if $λⱼ(x) > 0$, we have $d(x - η t,xⱼ) ≤ η(xⱼ)$ otherwise $x  - η t ∉ Dⱼ$
+and $d(x, x - η t) < η ≤ η(xⱼ)$ otherwise $s(t) = 0$. Therefore,
+if $λⱼ(x) > 0$, we have $d(x,xⱼ) < 2η(xⱼ)$.
+which implies $d₁(xⱼ).∇p(x) > 0$ and $∀(i,σ) ∈ I_ε(x), d₁(xⱼ).∇ᵢ^σp > 0$.
+
+Moreover, the coefficient $λⱼ$ are positive. Therefore, $d(x) = Σ_{j∈J}
+λⱼ(x) d₁(xⱼ)$ implies $d(x).∇p(x) > 0$ and $∀(i,σ) ∈ I_ε(x), d(x).∇ᵢ^σp >
+0$.  Thus, we have:
+$$∀x ∈ \SNR, d(x).∇p(x) > 0 \hbox{ and }∀(i,σ) ∈
+  I_ε(x), d(x).∇ᵢ^σp > 0.$$
+
+  As $\SNR$ is compact, we can find $μ > 0$ such that
+$$∀x ∈ \SNR, d(x).∇p(x) > μ \hbox{ and }∀(i,σ) ∈
+  I_ε(x), d(x).∇ᵢ^σp > μ.$$
+
+  To extend this to $ℝ^{n+1}∖\{0\}$, we just have to set $d(λx) = d(x)$ for $λ >
+  0$ and as $p$ is homogeneous of degree $d$, we have:
+
+  $$∀x ∈  ℝ^{n+1} ∖ \{0\}, d(x).∇p(x) > μ\|x\|^{d-1} \hbox{ and }∀(i,σ) ∈
+  I_ε(x), d(x).∇ᵢ^σp > μ.$$
 \end{proof}
@@
 \begin{prop}
-    Let $p$ be an homogeneous polynomial in $n+1$ variables.
-    Let $Δ$ be an ad
+  Let $p$ be an homogeneous polynomial of degree $d$ on
+$ℝ^{n+1}$.
+  Let $(Δᵢ)_{i∈I}$ be an $ε$-fat simplicial partition of $\PNR$ adapted to $p$.
+  the function  $p$ and $\overline{p}$ have homeomorphic zero locus on
+  $ℝ^{n+1}∖\{0\}$.
 \end{prop}
+
 \begin{proof}
+  The function $\overline{p}$ as a gradient defined in any direction $d$ which
+  may be defined as
+  $$
+  \nabla \overline{p}(x). d = \lim_{h → 0⁺} \frac{\overline{p}(x + hd) - \overline{p}(x)}{h}
+  $$
+  This is true because for $h > 0$ and small enough, $x + hd$ and $x$ belong to
+  at least one common cone $Δᵢ^σ$ with $(i, σ) ∈ I(x)$.
+  If they belong to more than one cone, the
+  gradient $∇ᵢ^σ . d$ coincide and are the limit.
+  This tells us moreover that we have
+  $$\nabla \overline{p}(x). d = ∇ᵢ^σp . d \hbox{ for some }
+  (i, σ) ∈ I(x).$$
 
+  Next, we Consider the differential equation $x'(t) = d(x(t))$.
+  This differential equation has
+  unique solutions in the neighbourhood of $x$ because $d$ is $C^∞$.
+
+  Now consider a closed and connnected region $Ω$ of $ℝ^{n+1} ∖ \{0\}$
+  where $p(x) ≤ 0$ and $\overline{p}(x) ≥ 0$, and a maximal solution
+  $x : L → Ω$ with $0$ in the interior of the interval $L$ and $x(0)$ in
+  the interior of $Ω$.
+
+  We define $\|p\| = max_{x ∈ \SNR} |p(x)|$ and  $\|\overline{p}\| = max_{x ∈
+    \SNR} |\overline{p}(x)|$.
+
+  From the definition of this region,
+  no $x ∈ Ω$ satisfies the condition $Π_ε(x)$. Hence we have
+  $d(x). ∇p(x) > 0$, so the solution is increasing in $p$.
+  Similarly, $∀(i,σ) ∈ I_ε(x), d(x). ∇ᵢ^σ > 0$, hence the solution is also
+  increasing in $\overline{p}$.
+
+  Therefore, for $t < 0$, we have $|p(x(0))| < |p(x(t))| < \|p\| \|x(t)\|ᵈ$.
+  for $t > 0$, we have  $|\overline{p}(x(0))| < |\overline{p}(x(t))| <
+  \|\overline{p}\| \|x(t)\|$.
+  Let use take $R = min(\frac{\overline{p}(x(0))}{\|\overline{p}\|},
+  \left(\frac{p(x(0))}{\|p\|}\right)^{\frac{1}{d}})$,
+  we have $\|x(t)\| > R$.
+
+  Next, consider $f(t) = p(x(t))$, $f'(t) = ∇p(x(t)).d(x(t)) > μ R^{d-1} $
+  Hence $-p(x(0)) > ∫_J⁺ f'(t) dt > t μ R^{d-1}$. Therefore the interval $J$ has
+  an upper bound $b > 0$.
+
+  Similarely, we considering $g(t) = \overline{p}(x(t))$, we find that
+  $J$ as a lower bound $a < 0$.
+
+  %% Thus, our maximal solution may only
+  %% start at $0$, infinity or a border of $Ω$ where $\overline{p} = 0$ and may only end
+  %% at $0$, infinity or a border of $Ω$ where $p = 0$.
+
+  %% First, we rule out zero, as $p(x(t))$ is increasing and $p(x(t)) ≤ 0$ on the
+  %% whole region, the solution can not start at $x = 0$, because $p(0) = 0$.  as
+  %% $\overline{p}(x(t)) ≥ 0$ and $\overline{p}(x(t))$ is increasing the solution can
+  %% not end at $0$.
+
+  %% If a the solution starts at infinity, $\overline{p}(x(t))$ is increasing
+  %% and $\overline{p}(x(t)) ≥ 0$, Hence when $x(t)$ converges to the beginning of
+  %% the interval $I$, we have $\overline{p}(x(t))$ which converges to a finite
+  %% limite. And if $x(t)$ approaches infinity ...
+
+  %% $p(x(t))$ must have a finite limit at the begginning
+  %% of the solution which implies that $∇p(x(t)).x'(t)$ should converge toward $0$
+  %% when $t$ converges to the beginning of $I$. This is not possible
+
+  %% over $ℝ^{n+1} \setminus \{0\}$, it has maximal solution. We consider maximal solution
+  %% $x : [0, a[ \to ℝ^{n+1} \setminus \{0\}$ starting with $p(x(0)) = 0$, with
+  %%     $x_0 \in ℝ^{n+1} \setminus \{0\}$.
+
+  %%     We have $p(x(t))' = \nabla p(x(t)) . d(x(t)) > 0$, which means that
+  %%     $p(x(t))$ is increasing.
+
+  %%     We have $\overline{p(x(t))} = \nabla \overline{p}(x(t)). d(x(t)) > 0$
+  %%     hence $\overline{p(x(t))}$ is decreasing. If $x(t)$ would approach
+  %%     infinity, the it would do so with a derivate approaching the plane
 \end{proof}
+
  \end{document}

### 2021-01-17 article/main.tex
work on article

@@
 \DeclareUnicodeCharacter{7496}{^d}
+\DeclareUnicodeCharacter{7511}{^t}
+
 \usepackage[utf8x]{inputenc}
@@
 $$d(\overline{x},\overline{y}) = \min\left(
-\left\|{x \over \|x\|} - {y \over \|y\|}\right\|, \left\|{x \over \|x\|} + {y
-  \over \|y\|}\right\|\right) (∀\overline{x},\overline{y} ∈ \PNR).$$
+\left\|{\frac{x}{\|x\|}} - {\frac{y}{\|y\|}}\right\|, \left\|{\frac{x}{\|x\|}} + {\frac{y}{\|y\|}}\right\|\right) (∀\overline{x},\overline{y} ∈ \PNR).$$
 
@@
 
+\appendix
+
+\section{Testing zero in convex hull}
+
+The central test in our algorith is to know if the null vector is in the convex
+hull of a given set of vector of $ℝ^d$, or as it is clearly equivalent, in its convex
+cone.
+
+More precisely, the problem we want to solve can be defined as follows:
+\begin{defi}
+  \begin{tabular}{ll}
+  Input:& a real $n × d$ matrix $A$. \cr
+  Output:& a non nul vector $X ∈ ℝ_+^n$ such that $^tX A = 0$ \cr
+  or& a vector $N ∈ ℝ^d$ such that $A N > 0$
+  \end{tabular}
+\end{defi}
+
+This does correspond to our problem: if zero is in the convex hull of the lines
+of the matrix $A$, then we can produce the wanted vector $X∈ ℝ_+^n$. It zero is not in
+the convex hull, then we can return the normal $N∈ ℝ^d$ of a linear plane such that
+all the lines of $A$ lie on the same side of this plane.
+
+We start the algorithm with an initial vector $X_0∈ ℝ_+^n$, with positive coefficients
+summing to one, for instance $X₀=\frac{1}{n}ᵗ(1,1,\dots,1,1)$.
+We define $N_i = tX_i A$. We also define a vector $P_0 = 0 ∈ ℝ_+^n $.
+
+The algorithm then perform two kind of steps:
+
+\paragraph*{Conjugate steps}, which are somehow inspired by the conjugate
+gradient method.
+
+First we define $J ∈ ℝ_+^n = (1,1,\dots,1,1)$ and $ν(X) = \frac{1}{J.X} X$ which
+normalise the vector $X$ to have all its coefficient sum to one. We will use
+$ν(X)$ only one non null vector in $ℝ_+^n$.
+
+If for all lines $Aⱼ$ of $A$ we have $Aⱼ.Nᵢ > 0$ then the algorithm
+stops and output $N = Nᵢ$. Otherwise we select $Dᵢ = δⱼ$ such that $Aⱼ.Nᵢ ≤ 0$ and minimum.
+Then we compute $α>0,β ∈ ℝ$, $X_{i+1) = ν(Xᵢ + αDᵢ+βPᵢ)$, such that
+  $\|ᵗX_{i+1} A\|²$ is minimum. We have
+  \begin{eqnarray*}
+    f(α,β) &=& \|ᵗX_{i+1} A\|² \cr
+    &=& \frac{\|ᵗXᵢ A + αᵗDᵢA + βᵗPᵢA\|²}{(1 + α + β)²}\cr
+    &=& \frac{\|Nᵢ + αᵗAⱼ + βᵗPᵢA\|²}{(1 + α + βPᵢ.J)²}\cr
+    &=& \frac{\|Nᵢ\|² + α² + β²\|ᵗPᵢA\|² + 2 α Nᵢ.Aⱼ + 2 β Nᵢ.ᵗPᵢA + 2αβ Aⱼ.ᵗPᵢA}
+    {1 + α² + β²(Pᵢ.J)² + 2α + 2βPᵢ.J + 2αβPᵢJ}\cr
+    \frac{∂f(α,β)}{∂α}
+    &=& \frac{\begin{array}{cl}
+        &(2α + 2 Nᵢ.Aⱼ + 2βAⱼ.ᵗPᵢA)(1 + α² + β²(Pᵢ.J)² + 2α + 2βPᵢ.J + 2αβPᵢJ)\cr
+        - &(\|Nᵢ\|² + α² + β²\|ᵗPᵢA\|² + 2 α Nᵢ.Aⱼ + 2 β Nᵢ.ᵗPᵢA + 2αβ
+      Aⱼ.ᵗPᵢA)(2α + 2 + 2βPᵢJ)
+      \end{array}}
+    {(1 + α² + β²(Pᵢ.J)² + 2α + 2βPᵢ.J + 2αβPᵢJ)²}\cr
+    &=& \frac{
+    {(1 + α² + β²(Pᵢ.J)² + 2α + 2βPᵢ.J + 2αβPᵢJ)²}\cr
+
+  \end{eqnarray*}
 \end{document}

### 2021-01-22 article/attic.tex
new tex file to keep old stuff

$$f_{ε,u,v}(x) = v p(x) + u \|x\|^{d-1} ∫ f(x - ε v \|x\| t) s(t) dt  $$

\begin{eqnarray*}
  ∇f_{ε,u,v}(x) &=& v ∇p(x) + u (d-1) x \|x\|^{d-3} ∫ f(x - ε v \|x\| t) s(t)
  dt \cr
  && + u \|x\|^{d-1} ∫ ∇f(x - ε v \|x\| t) s(t) dt  \cr
 && - ε v u \|x\|^{d-2} ∫ ∇f(x - ε v \|x\| t)^tx t s(t) dt
\end{eqnarray*}

If $∇f = 0$, then $f = 0$ and
$$∫ f(x - ε v \|x\| t) s(t) dt = - \frac{v p(x)}{u \|x\|^{d-1}} $$

If $∇f = 0$, then
\begin{eqnarray*}
  ∇f_{ε,u,v}(x) &=& v ∇p(x) + v (d-1) x \|x\|^{-2} p(x)
  dt \cr
  && + u \|x\|^{d-1} ∫ ∇f(x - ε v \|x\| t) s(t) dt  \cr
 && - ε v u \|x\|^{d-2} ∫ ∇f(x - ε v \|x\| t)^tx t s(t) dt
\end{eqnarray*}

\begin{defi}
   Let $Δ = (Δᵢ)_{i∈I}$ be  a \emph{simplicial partition} of $\PNR$, a
   \emph{$Δ$-linear map}
   is a map $f : ℝ^{n+1} → ℝ$ which is continuous, piecewise linear and linear
on each $Δᵢ⁺$ and $Δᵢ⁻$ for $i ∈ I$.

  For such a map, and for all $i∈I$, we define $fᵢ⁺$ (resp. $fᵢ⁻$) the restriction of $f$ to
  $Δᵢ⁺$ (resp. $Δᵢ⁻$). We also define $∇fᵢ⁺$ (resp. $∇fᵢ⁻$) the gradient of
  $fᵢ⁺$ (resp. $fᵢ⁻$), which is constant as these functions are linear.

  For any point $x∈\SNR$, we define $$∇ᶜf(x) = \cone{\{∇fᵢσ, (i,σ) ∈ I_ε(x ∈ Δᵢ⁺\} ∪ \{∇fᵢ⁻, x ∈ Δᵢ⁻\}}$$

  And for $x∈\SNR$ and $ε > 0$, we define
\begin{eqnarray*}
  ∇ᶜ_εf(x) &=& \cone{\{∇fᵢ⁺, \ball{x}{ε}
    ∩ Δᵢ⁺ ≠ ∅\} ∪ \{∇fᵢ⁻, \ball{x}{ε} ∩ Δᵢ⁻ ≠ ∅\}} \cr
  &=& \cone{\{∇f^σᵢ, (i, σ) ∈ I_ε(x)\}}
\end{eqnarray*}

\end{defi}

Remarks:
\begin{itemize}
  \item if $x ∈ πₙ^{-1}(\interior{Δᵢ})$
    for some $i ∈ I$, then $∇ᶜf(x) = \{∇f(x)\}$.

 \item In this paper, we will only consider odd or even $Δ$-linear map, meaning that
   it exists $σ ∈ \{-1,1\}$ such that for all $i ∈ I$ we have $fᵢ⁺ = σ fᵢ⁻$. For
   such a map, the zero locus is well defined on $\PNR$.
\end{itemize}

\begin{defi}
  We say that a $Δ$-linear map $f$ is smooth if for all $x ∈ ℝ^{n+1}∖\{0\}$, $∇ᶜf(x)$
  does not contains the vector $0$.
\end{defi}

\begin{prop}\label{ghull}
  If $Δ = (Δᵢ)_{i∈I}$ is an $ε$-fat \emph{simplicial partition} for some $ε>0$
  and if $f$ is a $Δ$-linear map, then for any $x ∈
     \SNR$ there exists $y ∈
     \SNR$ such that $$∇ᶜf(x) ⊆ ∇ᶜ_εf(x) ⊆ ∇ᶜf(y).$$ Moreover, if $f$ is smooth, then $0 ∉ ∇ᶜ_εf(x)$.
\end{prop}

\begin{proof}
  $∇ᶜf(x) ⊆ ∇ᶜ_εf(x)$ comes from $I(x) ⊂ I_ε(x)$.
  Let use define $J = I_ε(x)$. By definition $∇ᶜ_εf(x) = \cone{\{∇ᵢ^σ, (i,σ) ∈
    J\}}$.
  As the simplicial partition is $ε$-fat, we can take $y ∈ ∩_{(i,σ)
    ∈ J} Δᵢ^σ ∩ \SNR$. Therefore, $J ⊂ \{(i,σ), y ∈ Δᵢ^σ\}$ which implies
  $∇ᶜ_εf(x) ⊆ ∇ᶜf(y)$. The last part is a direct consequence of the definition
  of $f$ smooth.
\end{proof}

\begin{prop}
  Let $Δ = (Δᵢ)_{i∈I}$ be a \emph{simplicial partition} of $\PNR$ and
  let $f$ be a smooth \emph{$Δ$-linear map}.
  For any $ε_M ∈ ]0,1[$ such that $Δ$ is $ε_M$-fat, there exists a family of $C^∞$ function
  $ε ↦ f_ε : ]0,ε_M] → \SNR → ℝ$ such that
  \begin{enumerate}
  \item $∀x ∈ \SNR, f(x) - f_ε(x) → 0$ when $ε → 0$
  \item $∀x ∈ \SNR, ∇f_ε(x) ∈ ∇ᶜ_εf(x)$ and $∇f_ε(x) ≠ 0$.
  \item All functions $f_ε$ and $f$ have homeomorphic zero locus.
  \end{enumerate}
\end{prop}

\begin{proof} We first start with few notations:
  \begin{itemize}
  \item Let $s:ℝ^{n+1} → ℝ⁺$ a $C^∞$ map with support included in $B_1(0)$ and such
  that $∫_{ℝ^{n+1}} s(t)dt = 1$ for the usual measure $dt$ of $ℝ^{n+1}$. We also
  assume that $s(-x) = s(x)$.

  \item We define $s_ε(x) = ε^{-n-1}s(ε^{-1} x)$, which has support in $B_ε(0)$ and
  satisfies $∫_{ℝ^{n+1}} s_\epsilon(t)dt = 1$ because
  \begin{eqnarray*}
    ∫_{ℝ^{n+1}} s_\epsilon(t)dt &=& ∫_{ℝ^{n+1}} ε^{-n-1}s(ε^{-1}t)dt \cr
    &=& ∫_{ℝ^{n+1}} s(u)du \hbox{ using } t = εu, dt = ε^{n+1}du \cr
    &=& 1
  \end{eqnarray*}
  \end{itemize}

  We define $f_ε= f ∗ s_ε$: $$f_ε(x) = ∫_{ℝ^{n+1}} f(x-t)s_ε(t) dt = ∫_{ℝ^{n+1}}
  f(x-ε u)s(u) du.$$

  From the properties of convolution product we known that $f_ε$ is $C^∞$ on
  $\SNR$. For the limit:
  \begin{eqnarray*}
    |f(x) - f_ε(x)| &=& \left|∫_{ℝ^{n+1}} (f(x) - f(t))s_{ε}(x-t) dt\right|\cr
    &<& \max_{t∈B_ε(x)} |f(x) - f(t)| → 0  \hbox{ when } ε → 0\cr
    && \hbox{because $f$ is continuous.}
  \end{eqnarray*}

  We also define $\Psi_i^σ(x,ε) = \{ t ∈ \ball{0}{ε}, x - t ∈ Δᵢ^σ \}$

  For the gradient, using the fact that $f$ is $C¹$ almost every where and that
  $|∇f(x)|$ is bounded, we have
  \begin{eqnarray*}
    ∇f_ε(x) &=& ∇∫_{ℝ^{n+1}} f(x-t)s_{ε}(t) dt\cr
    &=& ∫_{ℝ^{n+1}} ∇f(x-t)s_{ε}(t) dt\cr
    &=& Σ_{(i,σ)∈I_ε(x)}∫_{\Psi_i^σ(x,ε)} ∇f(x-t)s_{ε}(t) dt\cr
    &=& Σ_{(i,σ)∈I_ε(x)} λᵢ(ε) ∇ᵢ^σf
    \hbox{ with } λᵢ(ε) = ∫_{\Psi_i^σ(x,ε)} s_{ε}(t) dt > 0
  \end{eqnarray*}

  Hence $∇f_ε(x)$ is in $∇ᶜ_εf(x)$ and hence non zero by proposition
  \ref{ghull} because
  $$Σ_{(i,σ)∈I_ε(x)} λᵢ(ε) = Σ_{i∈V_ε(x)}∫_{\Psi_i^σ(x,ε)} s_ε(t) dt =
  ∫_{\ball{0}{ε}} s_ε(t) dt = 1$$

  Moreover, we have
  \begin{eqnarray*}
    λᵢ(ε) &=&  ∫_{\Psi_i^σ(x,ε)} s_{ε}(t) dt \cr
    &=& ∫_{\Phi_i^σ(x,ε)} s(u) du
    \hbox{ with } \Phi_i^σ(x,ε) = \{ u ∈ \ball{0}{1}, x - εu ∈ Δᵢ^σ\}
  \end{eqnarray*}

  Now, if $ε$ is small enough to have $I(x) = I_ε(x)$, then $\Phi_i^σ(x,ε)$ also
  becomes independant of $ε$.  As a consequence, $∇f_ε(x)$ is constant for $ε$
  small enough, hence convergent to a value which is in $∇ᶜf(x)$ and therefore
  non zero. Therefore,
  we define $∇₀f(x)$ the limit of $∇f_ε(x)$.

  To build the homeomorphism between the various zero levels, we consider the
  following differential equation on for $γ(ε) : ℝ ↦ ℝ^{n+1}$:

  $$ γ'(ε) = g(ε,γ(ε)) \hbox{ with } g(ε,x) = - \frac{∂f_ε}{∂ε}(x) \frac{∇f_ε(x)}{||∇f_ε(x)||²} $$

  The function $g$ is ${\cal
    C}^∞$ for $0 < ε < ε_M$ and $x ∈ \SNR$ because $∇f_ε(x) ≠ 0$.
   We need to show that it can be
  prolongated to $ε = 0$. As we already have seen how to prolongate $∇f_ε(x)$ to
  a non zero value, we only have to examine the limit of $\frac{∂f_ε(x)}{∂ε}$.

  \begin{eqnarray*}
    \frac{∂f_ε(x)}{∂ε} &=& \frac{∂}{∂ε} ∫_{ℝ^{n+1}} f(x - ε u)s(u) du \cr
        &=& - ∫_{ℝ^{n+1}} ∇f(x - ε u).u s(u) du \cr
    &=& - Σ_{(i,σ)∈I_ε(x)} ∇ᵢ^σf. ∫_{\Phiᵢ^σ(x,ε)}  u s(u) du\cr
  \end{eqnarray*}

  For that same reason as above, the vector $∫_{\Phiᵢ^σ(x,ε)}  u s(u) du$
  is constant for   $ε$ is small enough. Hence $\frac{∂f_ε(x)}{∂ε}$ has a limit for $ε → 0$.

   Hence, by Cauchy-Lipschitz theorem, the above differential equation has
   a unique solution with $γ_{x₀}(ε) = x₀$ for $ε in [0,ε_M]$. Moreover $f_ε(γ(ε))$ is constant
   because
   \begin{eqnarray*}
    \frac{∂f_ε(γ_{x₀}(ε)}{∂ε} &=& \frac{∂}{∂ε} f_ε(γ_{x₀}(ε)) +
    ∇f_ε(γ_{x₀}(ε)).g(ε,γ_{x₀}(ε)) \cr
    &=& 0
   \end{eqnarray*}

   This means that $γ_{x₀}$ gives an homeomorphism between the zero locus of $f$
   and $f_ε$.
\end{proof}

\section{Polynomials and $Δ$-linear map}

  \begin{defi}
    Let $P$ be an homogeneous polynomial in $n+1$ variables.
    Let $(Δᵢ)_{i∈I}$ be a simplicial partition of $\PNR$. We define $f_P$ the
    piecewise linear map that coincides with $P$ on every summit of $Δ$.

    $(Δᵢ)_{i∈I}$ is $P$-thin if for any $i₁,\dots,iₖ ∈ I$ such that $Δ_{i₁} ∩
    \dots ∩ Δ_{iₖ} ≠ ∅$, the convex hull of
    $$ G_{i₁,\dots,iₖ} = \{ ∇ⱼ f_P, j = i₁,\dots,iₖ \} ∪ \{ ∇P(x), x ∈ Δ_{i₁} ∩
    \dots ∩ Δ_{iₖ} \}$$
    does not contain the vector $0$.
  \end{defi}

  \begin{prop}
    Let $P$ be an homogeneous polynomial in $n+1$ variables.
    Let $(Δᵢ)_{i∈I}$ be a $P$-thin simplicial partition of $\PNR$. Then the zero
    locus of $f_P$ and $P$ are homeomorphic.
  \end{prop}

  \begin{proof}
    Let $ε_M$ such that $(Δᵢ)_{i∈I}$ is $ε_M$ fat. For $(t,ε) ∈ [0,1] ×
    [0,ε_M]$, let $f_{t,ε} = (1-t) P + t f_ε$.
  \end{proof}

### 2021-02-10 article/approximation.tex
work on article + file splitting

--- 2021-01-14 article/main.tex
@@
-\documentclass{article}
-
-\usepackage{hyperref}
-\usepackage{enumerate}
-\usepackage{enumitem}
-\usepackage{amssymb,amsmath,amsthm} %must be before unicode-math
-\usepackage[mathletters]{ucs}
-\DeclareUnicodeCharacter{8348}{_t}
-\DeclareUnicodeCharacter{8342}{_k}
-\DeclareUnicodeCharacter{8339}{_x}
-\DeclareUnicodeCharacter{8345}{_n}
-\DeclareUnicodeCharacter{7522}{_i}
-\DeclareUnicodeCharacter{11388}{_j}
-\DeclareUnicodeCharacter{7523}{_r}
-\DeclareUnicodeCharacter{7580}{^c}
-\DeclareUnicodeCharacter{7496}{^d}
-\usepackage[utf8x]{inputenc}
-\usepackage{graphicx}
-\usepackage{stmaryrd}
-\usepackage[autosize]{dot2texi}
-\usepackage{multicol}
-\setlength{\multicolsep}{0pt}
-\usepackage{tikz}
-\usetikzlibrary{shapes,arrows,tikzmark,decorations.pathreplacing,calc}
-\usepackage{adjustbox}
-
-% Title portion. Note the short title for running heads
-\title{Solving smooth system of algebraic equations}
-\author{Christophe Raffalli}
-
-\newcommand{\interior}[1]{%
-  #1^{\mathrm{o}}%
-}
-\newcommand{\cardinal}[1]{%
-  \#({#1})%
-}
-\newcommand{\hull}[1]{%
-  \mathcal H({#1})%
-}
-\newcommand{\cone}[1]{%
-  \mathcal C({#1})%
-}
-\newcommand{\vertices}[1]{%
-  \mathcal V({#1})%
-}
-\newcommand{\ball}[2]{%
-  \mathcal B_{#2}({#1})%
-}
-
-\newcommand{\PNR}{{\cal P}^n(ℝ)}
-\newcommand{\SNR}{{\cal S}^n(ℝ)}
-
-\newtheorem{theo}{Theorem}
-\newtheorem{nota}[theo]{Notation}
-\newtheorem{defi}[theo]{Definition}
-\newtheorem{prop}[theo]{Proposition}
-\newtheorem{exam}[theo]{Example}
-
-% Document starts
-\begin{document}
-
-\maketitle
-
-\section{Introduction}
-
-\section{Conventions and notations}
-
-We consider the real projective plane $\PNR$.
- We define $πₙ:ℝ^{n+1}∖\{0\} → \PNR$ the
-projection $x ↦  \{ λx, λ∈ℝ^⋆ \} ∈ \PNR$. To simplify, we often write $\overline{x}$ for $πₙ(x)$.
-
-We use on $\PNR$ and $\SNR$ the measure induced by
-the chord metric of the unit sphere:
-$$d(\overline{x},\overline{y}) = \min\left(
-\left\|{x \over \|x\|} - {y \over \|y\|}\right\|, \left\|{x \over \|x\|} + {y
-  \over \|y\|}\right\|\right) (∀\overline{x},\overline{y} ∈ \PNR).$$
-
-If $x ∈ \PNR$ (resp. $ℝ^{n+1}$), $\ball{x}{r}$ denotes the closed ball of center $x$
-and radius $r$.
-
-We write $\cardinal{S}$ the cardinal of a set $S$.
-
-For $A ⊂ ℝ^{n+1}$, $\hull{A}$ denotes the convex hull of $A$ and $\cone{A}$ its
-convex cone.
-
-We use the following notation for simplices:
-\begin{itemize}
-\item If $Δ ⊂ \PNR$ is a simplex, we denote $\vertices{Δ} ⊂ \SNR$ a finite set of
-  represents of the vertices of $Δ$.
-\item $\vertices{Δ}$ must verify that $Δ = πₙ(\hull{\vertices{Δ}})$. This is why we take $\vertices{Δ} ⊂
-    \SNR$ instead of $\vertices{Δ} ⊂ \PNR$ as the convex hull is not well defined in
-    the projective plane.
-\item Simplices should not be too big, in particular, $\PNR$ is not a simplex!
-  For this we require $\vertices{Δ}$ to fit in an open half space of
-  $\SNR$. If this is not possible, we consider that $Δ$ is not a simplex.
-\item We take $\vertices{Δ}$ to be minimal and consider only non degenerated simplex: removing one point in
-    $\vertices{Δ}$
-    changes it convex hull and the dimension of the
-    simplex $Δ$ is always exactly $\cardinal{\vertices{Δ} - 1}$. This also means that
-    $\vertices{Δ}$ is the set of extremal points of its convex hull.
-  \item Because we require simplices to be not too big $πₙ^{-1}(Δ)$ has exactly two connected components:
-    $$πₙ^{-1}(Δ) = \cone{\vertices{Δ}} ∪ -\cone{\vertices{Δ}}.$$
-    We write $Δ⁺ =  \cone{\vertices{Δ}}$ and $Δ⁻ = - Δ⁺$. Here $-A$ denotes
-    $\{-x, x ∈ A\}$.
-
-\end{itemize}
-
-\section{Simplicial partition}
-
-\begin{defi}
-  A \emph{simplicial partition} of
-  $\PNR$ is a finite set of closed simplices $(Δᵢ)_{i∈I}$ such that
-  \begin{itemize}
-  \item Each $Δᵢ$ is a simplex of dimension $n$, i.e. $\cardinal{\vertices{Δ}} = n + 1$.
-  \item $⋃_{i∈I} Δᵢ = \PNR$,
-  \item For all $i₁ < i₂ < \dots iₖ ∈ I$, $Δ_{i₁} ∩ \dots ∩ Δ_{iₖ}$ is empty or is a simplex of dimension at most
-    $n-k+1$ and $πₙ(\vertices{Δ_{i₁} ∩ \dots ∩ Δ_{iₖ}}) =
-    πₙ(\vertices{Δ_{i₁}}) ∩ \dots ∩ πₙ(\vertices{Δ_{iₖ}})$.
-    We can not require  $\vertices{Δᵢ ∩ Δⱼ} = \vertices{Δᵢ} ∩ \vertices{Δⱼ}$ because we may have $x ∈
-    \vertices{Δᵢ}$ and $y ∈ \vertices{Δⱼ}$ with $x ≠ y$ and $\overline{x} = \overline{y}$ (see
-    the example below). This conditions ensures that the intersection of
-    simplices are exactly faces of lower dimensions defined by the common vertices.
-%  \item We say that $Δᵢ$ and $Δⱼ$ are neighbour if $Δᵢ ∩ Δⱼ ≠ ∅$. The neighbourhood relation is clearly reflexive and symmetric.
-  \end{itemize}
-\end{defi}
-
-Here is as example a partition of $\PNR$ with $2ⁿ$ simplices:
-\begin{exam}\label{init_part}
-Consider $B = \{x₀,\dots,xₙ\}$, the canonical base of $ℝ^{n+1}$ and
-$(εᵢ)_{i ∈ \{1,\dots,2ⁿ\}}$ an enumeration of all sequences of length $n$ of
-$1$ or $-1$. Then, we define $(Δᵢ)_{i∈\{1,\dots,2ⁿ\}}$ by
-$$Δᵢ = πₙ(\hull{\{x₀,ε_{i,1} x₁, \dots, ε_{i,n} xₙ\}}).$$
-\end{exam}
-
-We remark in this example, that all simplices use $B$ as set of vertices. This
-means that for all $i < j ∈ \{1,\dots,2ⁿ\}$, we have
-  $πₙ(\vertices{Δᵢ}) = πₙ(\vertices{Δⱼ}) = πₙ(B)$ while $\vertices{Δᵢ} ≠ \vertices{Δⱼ}$.
-
-In this examples, we have
-\begin{eqnarray*}
-  Δ⁺ᵢ &=& \cone{\{x₀,ε_{i,1} x₁, \dots, ε_{i,n} xₙ\}} \cr
-  Δ⁻ᵢ &=& \cone{\{-x₀,-ε_{i,1} x₁, \dots, -ε_{i,n} xₙ\}} \cr
-\end{eqnarray*}
-
-\begin{defi} Let $(Δᵢ)_{i∈I}$ be a simplicial partition of $\PNR$. For $x ∈
-  ℝ^{n+1} ∖\{0\}$ we define
-  $I^Δ(x) = \{(i,σ) ∈ I × \{-,+\}, x ∈ Δᵢ^σ\}$ and
-  $I^Δ_ε(x) = \{(i,σ) ∈ I × \{-,+\}, Δᵢ^σ ∩ \ball{x}{ε\|x\|} ≠ ∅\}$. In general we only use one
-  simplicial partition at a time and we simply write $I(x)$ and $I_ε(x)$.
-\end{defi}
-
-\begin{prop}\label{Ihomo}
-  Let $(Δᵢ)_{i∈I}$ be a simplicial partition of $\PNR$.
-  For $x ∈  ℝ^{n+1} ∖\{0\}$ and $λ > 0$, we have $I(λx) = I(x)$ and $I_ε(λx) = I_ε(x)$.
-\end{prop}
-
-\begin{proof}
-  From the fact that the set $Δᵢ^σ$ are convex cones.
-\end{proof}
-
-\begin{prop}
-  Let $(Δᵢ)_{i∈I}$ be a simplicial partition of $\PNR$.
-  For any $x ∈ ℝ^{n+1} ∖\{0\}$, if $ε>0$ is small enough, then $I_ε(x) = I(x)$.
-\end{prop}
-
-\begin{proof}
-  Take $ε < \min_{(i,σ) ∉ I(x)} d(x,Δᵢ^σ)$, then we have $I_ε(x) = I(x)$.
-\end{proof}
-
-\begin{defi}
-  Let $ε$ be a positive real. A \emph{simplicial partition} $(Δᵢ)_{i∈I}$ of
-  $\PNR$ is said to be $ε$-fat if for all $x ∈ ℝ^{n+1} ∖\{0\}$ we have:
-$$ ⋂_{(i,σ) ∈ I_ε(x)} Δᵢ^σ ≠ ∅$$
-\end{defi}
-
-\begin{prop} If a simplicial partition $(Δᵢ)_{i∈I}$ is $ε$-fat for $ε > 0$
-  then it is $η$-fat if $0 < η ≤ ε$.
-\end{prop}
-
-\begin{proof} From the fact that for $x ∈ ℝ^{n+1} ∖\{0\}$, $I_η(x) ⊆ I_ε(x)$ if $η ≤ ε$.
-\end{proof}
-
-\begin{prop}
-  Any \emph{simplicial partition} $(Δᵢ)_{i∈I}$ of $\PNR$ is $ε$-fat for
-  some $ε > 0$ small enough.
-\end{prop}
-
-\begin{proof}
-  First, thanks to proposition \ref{Ihomo}, we only have to check the condition
-  for $ε$-fatness in $\SNR$.
-
-  Consider a set $J ⊂ I × \{-,+\}$ with $⋂_{(i,σ)∈J} Δⱼ^σ = ∅$ (1), we first
-  prove that there exists $ε_J > 0$ such that for all $x ∈ \SNR$, $J \not⊆
-  I_{ε_J}(x)$. For this we assume the contrary: For any $ε>0$ there exists $x_ε
-  ∈ \SNR$ such that $J ⊆ I_{ε}(x_ε)$. As $\SNR$ is compact, we can extract a
-  sequence $(εₙ,xₙ)_{n ∈ \mathbb N}$ which converges to $(0,x)$ for some $x ∈
-  \SNR$, with $J ⊆ I_{εₙ}(x_{εₙ})$ for all $n ∈ \mathbb N$. Thus, for any $(i,σ)
-  ∈ J$ and $n ∈ \mathbb N$, we have $\ball{xₙ}{εₙ} ∩ Δᵢ^σ ≠ ∅$ which implies
-  $d(xₙ,Δᵢ^σ) < εₙ$. As $Δᵢ^σ$ are closed convex cone, this implies that $x ∈
-  Δᵢ^σ$ for any $(i,σ) ∈ J$ which contradicts the hypothesis (1).
-
-  We end the proof by remarking that the simplicial partition is $ε$-fat if we
-  take $ε$ the minimum of all $ε_J$ for $J ⊂ I$ with $∩_{(i,σ)∈J} Δᵢ^σ =
-  ∅$. This is well defined as $I$ hence his power-set are finite. Indeed, if $J
-  = I_{ε}(x)$, and $∩_{(i,σ)∈J} Δᵢ^σ = ∅$, then $J \not ⊆ I_{ε_J}(x) ⊇ I_{ε}(x)
-  = J$ which is contradictory.
-\end{proof}
-
 \section{Δ-linear approximation of a polynomial}
@@
 \item $∀x ∈  \SNR, Π_ε(x) \hbox{ or } 0 ∉ \hull{\{∇p(x)\} ∪ \{∇ᵢ^σp, (i,σ) ∈ I_ε(x)\}}$
-\item\label{hb} $∀x ∈  ℝ^{n+1}∖\{0\}, Π_ε(x) \hbox{ or } ∃d ∈ ℝ^{n+1}∖\{0\},
-  \left\{\begin{array}{l} d.∇p(x) > 0 \hbox{ and}\cr
-    ∀(i,σ) ∈ I_ε(x), d.∇ᵢ^σp > 0
+\item\label{hb} $∀x ∈  ℝ^{n+1}∖\{0\}, Π_ε(x) \hbox{ or } ∃δ ∈ ℝ^{n+1}∖\{0\},
+  \left\{\begin{array}{l} δ.∇p(x) > 0 \hbox{ and}\cr
+    ∀(i,σ) ∈ I_ε(x), δ.∇ᵢ^σp > 0
   \end{array}\right.$
@@
 
-  The equivalence (2) ↔ (5) is a form of Han-Banach theorem \cite{?}.
+  The equivalence (2) ↔ (5) is a form of Han-Banach theorem ensuring the
+  existence of a supporting hyper-plane. The vector $δ$ is a normal vector of
+  this supporting hyperplane \cite{Zal02}.
 \end{proof}
@@
   Let $(Δᵢ)_{i∈I}$ be an $ε$-fat simplicial partition of $\PNR$ adapted to $p$.
-  We can find a $C^∞$ function $d$ in $ℝ^{n+1} ∖ \{0\} → ℝ^{n+1}∖\{0\} $
+  We can find a $C^∞$ function $δ$ in $ℝ^{n+1} ∖ \{0\} → ℝ^{n+1}∖\{0\} $
   and $μ > 0$ such that:
-$$∀x ∈  ℝ^{n+1}∖\{0\}, d(x).∇p(x) > μ\|x\|^{d-1} \hbox{ and }∀(i,σ) ∈
-  I_ε(x), d(x).∇ᵢ^σp > μ.$$
+  $$∀x ∈  ℝ^{n+1}∖\{0\}, Π_ε(x) \hbox{ or } \left\{
+  \begin{array}{l}δ(x).∇p(x) > μ\|x\|^{d-1} \hbox{ and } \cr ∀(i,σ) ∈
+  I_ε(x), δ(x).∇ᵢ^σp > μ.\end{array}\right.
+  $$
 \end{prop}
@@
 \begin{proof}
-From proposition \ref{adaptedeq}.\ref{hb}, for any $x ∈ ℝ^{n+1}∖\{0\}$, we find $d₀(x)
-∈ ℝ^{n+1}$ such that $d₀(x).∇p(x) > 0$ and $∀(i,σ) ∈ I_ε(x), d₀(x).∇ᵢ^σp > 0.$.
+From proposition \ref{adaptedeq}.\ref{hb}, for any $x ∈ ℝ^{n+1}∖\{0\}$, if
+$Π_ε(x)$ is not satisfied, we find $δ₀(x)
+∈ ℝ^{n+1}$ such that $δ₀(x).∇p(x) > 0$ and $∀(i,σ) ∈ I_ε(x), δ₀(x).∇ᵢ^σp > 0$.
 We can also assume that $d₀(λ x) = d₀(x)$ for $λ > 0$ for the same reason as in
@@
 $∀y ∈ \ball{x}{2η(x)}$, $d₀(x).∇p(y) > 0$ and $∀(i,σ) ∈ I_ε(y),
-d₀(x).∇ᵢ^σp > 0.$.
+d₀(x).∇ᵢ^σp > 0$.
 
@@
 \end{proof}
-
- \end{document}

### 2021-02-10 article/conventions.tex
work on article + file splitting

--- 2020-10-31 article/main.tex
@@
-\documentclass{article}
+\section{Conventions and notations}
 
-\usepackage{hyperref}
-\usepackage{enumerate}
-\usepackage{enumitem}
-\usepackage{amssymb,amsmath,amsthm} %must be before unicode-math
-\usepackage[mathletters]{ucs}
-\DeclareUnicodeCharacter{8348}{_t}
-\DeclareUnicodeCharacter{8339}{_x}
-\DeclareUnicodeCharacter{8345}{_n}
-\DeclareUnicodeCharacter{7522}{_i}
-\DeclareUnicodeCharacter{11388}{_j}
-\DeclareUnicodeCharacter{7523}{_r}
-\usepackage[utf8x]{inputenc}
-\usepackage{bussproofs}
-\usepackage{graphicx}
-\usepackage{stmaryrd}
-\usepackage[autosize]{dot2texi}
-\usepackage{multicol}
-\setlength{\multicolsep}{0pt}
-\usepackage{tikz}
-\usetikzlibrary{shapes,arrows,tikzmark,decorations.pathreplacing,calc}
-\usepackage{adjustbox}
+We consider the real projective plane $\PNR$.
+ We define $πₙ:ℝ^{n+1}∖\{0\} → \PNR$ the
+projection $x ↦  \{ λx, λ∈ℝ^⋆ \} ∈ \PNR$. To simplify, we often write $\overline{x}$ for $πₙ(x)$.
 
-% Title portion. Note the short title for running heads
-\title{Solving smooth system of algebraic equations}
-\author{Christophe Raffalli}
+We use on $\PNR$ the measure induced by
+the chord metric of the unit sphere:
+$$d(\overline{x},\overline{y}) = \min\left(
+\left\|{\frac{x}{\|x\|}} - {\frac{y}{\|y\|}}\right\|, \left\|{\frac{x}{\|x\|}} + {\frac{y}{\|y\|}}\right\|\right) (∀\overline{x},\overline{y} ∈ \PNR).$$
 
-\newcommand{\interior}[1]{%
-  #1^{\mathrm{o}}%
-}
-\newcommand{\cardinal}[1]{%
-  \#{#1}%
-}
-\newcommand{\PNR}{{\cal P}^n(ℝ)}
-\newcommand{\SNR}{{\cal S}^n(ℝ)}
-
-\newtheorem{theo}{Theorem}
-\newtheorem{nota}[theo]{Notation}
-\newtheorem{defi}[theo]{Definition}
-\newtheorem{prop}[theo]{Proposition}
-
-% Document starts
-\begin{document}
-
-\maketitle
-
-\begin{nota}
-  We consider the real projective plane $\PNR$.
-  When ${x ∈ ℝ^{n+1}}$, we write $\overline{x} = \{ λx, λ∈ℝ_* \} ∈
-  \PNR$ the equivalent class of $x$. We define $πₙ:ℝ^{n+1} → \PNR$ the
-  projection $x ↦ \overline{x}$.
-  We use on $\PNR$ the measure induced by
-  the chord metric of the unit sphere $\SNR$:
-  $$d(\overline{x},\overline{y}) = \min\left(
-  \left\|{x \over \|x\|} - {y \over \|y\|}\right\|, \left\|{x \over \|x\|} + {y
-    \over \|y\|}\right\|\right) (∀\overline{x},\overline{y} ∈ \PNR).$$
+If $x ∈ \PNR$ (resp. $ℝ^{n+1}$), $\ball{x}{r}$ denotes the closed ball of center $x$
+and radius $r$.
 
 We write $\cardinal{S}$ the cardinal of a set $S$.
-\end{nota}
 
-\begin{defi}
-  A \emph{simplicial partition} of
-  $\PNR$ is a finite set of closed simplices $(Δᵢ)_{i∈I}$ such that
+For $A ⊂ ℝ^{n+1}$, $\hull{A}$ denotes the convex hull of $A$ and $\cone{A}$ its
+convex cone.
+
+We use the following notation for simplices:
 \begin{itemize}
-  \item $⋃_{i∈I} Δᵢ = \PNR$,
-  \item for all $i≠j ∈ I$, $Δᵢ ∩ Δⱼ$ is a included in an hyperplane of $\PNR$.
-  \item for all simplices in $Δ$, there is a projective plane of $\PNR$ that do
-    not meet $Δ$.
+\item If $Δ ⊂ \PNR$ is a simplex, we denote $\vertices{Δ} ⊂ \SNR$ a finite set of
+  representatives of the vertices of $Δ$.
+\item $\vertices{Δ}$ must verify that $Δ = πₙ(\hull{\vertices{Δ}})$. This is why we take $\vertices{Δ} ⊂
+    \SNR$ instead of $\vertices{Δ} ⊂ \PNR$ as the convex hull is not well defined in
+    the projective plane.
+\item Simplices should not be too big, in particular, $\PNR$ is not a simplex!
+  For this we require $\vertices{Δ}$ to fit in an open half space of
+  $\SNR$. If this is not possible, we consider that $Δ$ is not a simplex.
+\item We take $\vertices{Δ}$ to be minimal and consider only non degenerated simplex: removing one point in
+    $\vertices{Δ}$
+    changes it convex hull and the dimension of the
+    simplex $Δ$ is always exactly $\cardinal{\vertices{Δ} - 1}$. This also means that
+    $\vertices{Δ}$ is the set of extremal points of its convex hull.
+  \item Because we require simplices to be not too big $πₙ^{-1}(Δ)$ has exactly two connected components:
+    $$πₙ^{-1}(Δ) = \cone{\vertices{Δ}} ∪ -\cone{\vertices{Δ}}.$$
+    We write $Δ⁺ =  \cone{\vertices{Δ}}$ and $Δ⁻ = - Δ⁺$. Here $-A$ denotes
+    $\{-x, x ∈ A\}$.
+
 \end{itemize}
-  We say that $Δᵢ$ and $Δⱼ$ are neighbour if $Δᵢ ∩ Δⱼ$ is infinite,
-  i.e. contains at least two points. We do not consider simplices sharing only
-  on vertex to be neighbour.  The neighbourhood relation is clearly reflexive
-  and symmetric.  For $i \in I$, we define $V(i) = \{ j \in I; \cardinal{(Δᵢ ∩
-    Δⱼ)} > 2\}$.
-\end{defi}
-
-\begin{defi}
-  Let $ε$ be a positive real. A \emph{simplicial partition} $(Δᵢ)_{i∈I}$ of $\PNR$ is said to be
-  $ε$-fat if for any $i,j ∈ I$, for any $x∈Δᵢ$ and $y ∈ Δⱼ$, if $d(x,y) <  ε$,
-  then $Δᵢ ∩ Δⱼ ≠ ∅$.
-\end{defi}
-
-\begin{prop}
-  Any \emph{simplicial partition} $(Δᵢ)_{i∈I}$ of $\PNR$ is $ε$-fat for
-  some $ε > 0$ small enough.
-\end{prop}
-
-\begin{proof}
-  Take $ε = \displaystyle{\min_{i,j ∈ I, Δᵢ ∩ Δⱼ = ∅} d(Δᵢ,Δⱼ)}$ which is positive because $I$ is
-  finite and for all $i ∈ I$, $Δᵢ$ is compact.
-\end{proof}
-
-\begin{defi}
-   Let $Δ = (Δᵢ)_{i∈I}$ be  a \emph{simplicial partition} of $\PNR$, a
-   \emph{$Δ$-piecewise linear map}
-   is a map $f : ℝ^{n+1} → ℝ$ which is
-continuous, piecewise linear and linear
-on each $πₙ^{-1}(Δᵢ)$ for $i ∈ I$.
-
-  For such a map, an for all $x ∈ π^{-1}Δᵢ$, we define $∇ᵢf(x) = ∇ᵢf = ∇f(y)$ for any $y ∈
-  π^{-1}\interior{Δᵢ}$. For
-  any point $x∈ℝ^{n+1}$, we define $∇_cf(x)$ the convex-hull of $\{∇ᵢf(x),
-  \hbox{ for } i \hbox{ s.t. } x ∈
-  π^{-1}Δᵢ\}$. For $x$ in $π^{-1}\interior{Δᵢ}$, $∇_cf(x) = \{∇f(x)\}$.
-\end{defi}
-
-\begin{defi}
-  We say that a $Δ$-map $f$ is smooth if for all $x ∈ \PNR$, $∇_cf(x)$ does not
-    contains $0$.
-\end{defi}
-
-\begin{prop}
-  Let $Δ = (Δᵢ)_{i∈I}$ be a \emph{simplicial partition} of $\PNR$ and
-  let $f$ be a smooth \emph{$Δ$-map}.
-  For any $ε_M>0$ such that $Δ$ is $ε$-fat, there exists a family of $C^∞$ function
-  $ε ↦ f_ε : \SNR → ℝ$ such that
-  \begin{itemize}
-  \item $∀x ∈ \SNR, f(x) - f_ε(x) → 0$ when $ε → 0$
-  \item $∀i ∈ I, ∀x ∈ ℝ^{n+1}, ∇f_ε(x) ∈ ∇_cf(x)$.
-  \item All functions $f_ε$ and $f$ have homeomorphic zero level.
-  \end{itemize}
-\end{prop}
-
-\begin{proof}
-  Let $B_r(x)$ denote the unit ball of center $x$ and radius $r$.
-  Let $s:ℝ^{n+1} → ℝ⁺$ a $C^∞$ map with support included in $B_1(x)$ and such
-  that $∫_{ℝ^{n+1}} s(t)dt = 1$ for the usual measure $dt$ of $ℝ^{n+1}$. We also
-  assume that $s(-x) = s(x)$.
-  We define $s_ε(x) = ε^{-n-1}s(ε^{-1} x)$, which has support in $B_ε(x)$ and
-  satisfies $∫_{ℝ^{n+1}} s_\epsilon(t)dt = 1$
-
-  We define $f_ε(x) = f ∗ s = ∫_{ℝ^{n+1}} f(x-t)s_ε(t) dt$ the convolution product of $f$ and
-  $s_{ε}$. $f_ε$ is $C^∞$ on $\SNR$. $|f(x) - f_ε(x)| = |∫_{ℝ^{n+1}} (f(x) - f(t))s_{ε}(x-t) dt| <
-  \max_{t∈B_ε(x)} |f(x) - f(t)| → 0$  when $ε → 0$ because $f$ is continuous.
-
-  Remark: $f_ε$ is not homogeneous, this is why we restrict its domain to
-  $\SNR$.
-
-  For the gradient, we have,
-  \begin{eqnarray*}
-    ∇f_ε(x) &=& ∇∫_{ℝ^{n+1}} f(x-t)s_{ε}(t) dt\cr
-     &=& ∇∫_{ℝ^{n+1}} f(u)∇s_{ε}(x-u) du\cr
-     &=& ∫_{ℝ^{n+1}} f(u)∇s_{ε}(x-u) du\cr
-    &=& Σ_{i∈V(x)}∫_{Δᵢ} f(x-t)∇s_{ε}(t) dt\cr
-    &=& Σ_{i∈v(x)}∫_{Δᵢ} ∇f(x-t)s_{ε}(t) dt\cr
-    &=& Σ_{i∈V(x)} λᵢ ∇ᵢf \hbox{ with } λᵢ = ∫_{Δᵢ} s_{ε}(x-t) dx > 0
-  \end{eqnarray*}
-
-  Hence $∇f_ε(x)$ is in the convex hull of the $∇ᵢf$ for $i ∈ V(x)$ because
-  $$Σ_{i∈I(x)} λᵢ = Σ_{i∈v(x)}∫_{Δᵢ} s_ε(x-t) dx =  1$$
-
-  To build the homeomorphism between the variaous zero levels, we consider the
-  following differential equation on for $γ(ε) : ℝ ↦ ℝ^{n+1}$:
-
-  $$ γ'(ε) = g(ε,γ(ε)) \hbox{ with } g(ε,x) = \frac{\frac{∂f_ε}{∂ε}(x) ∇f_ε(x)}{||∇f_ε(x)||} $$
-
-  The function $g$ is ${\cal
-    C}^∞$ for $0 < ε < ε_M$ and $x ∈ ℝ^{n+1}$ because $∇f_ε(x) ≠ 0$ on the
-  considered domain. the first thing to show it can be
-  prolongated to $ε = 0$. We have
-
-  \begin{eqnarray*}
-    ∇s_ε(x) &=& ∇(ε\|x\|)^{-n-1} s((ε\|x\|)^{-1}x) \cr
-                    &=& (-n-1) (ε\|x\|)^{-n-2} s((ε\|x\|)^{-1}x)
-    }\frac{x}{\|x\|} \cr
-     && + (ε\|x\|)^{-n-1} ∇s((ε\|x\|)^{-1}x) \left((ε\|x\|)^{-1} -
-      (ε\|x\|)^{-2}  \frac{x}{\|x\|}\right) \cr
-     && + (ε\|x\|)^{-n-1} ∇s((ε\|x\|)^{-1}x) \left((ε\|x\|)^{-1} -
-      (ε\|x\|)^{-2}\right)  \frac{x}{\|x\|} \cr
-  \end{eqnarray*}
-  \begin{eqnarray*}
-    \frac{∂}{∂ε} s_{ε\|x\|}(x-t)
-      &=& \frac{∂}{∂ε} (ε\|x\|)^{-n-1} s((ε\|x\|)^{-1}(x-t)) \cr
-    &=& \frac{∂}{∂ε} (-n-1)\|x\|(ε\|x\|)^{-n-2} s((ε\|x\|)^{-1}(x-t))
-                      - ε^{-1}(ε\|x\|)^{-n-2} ∇s((ε\|x\|)^{-1}(x-t)).(x-t)\cr
-    &=& \frac{∂}{∂ε} (-n-1)ε s_ε(x-t)
-                      - ε^{-1}(ε\|x\|)^{-n-2} ∇s((ε\|x\|)^{-1}(x-t)).(x-t)\cr
-  \end{eqnarray*}
-
-    \begin{eqnarray*}
-    \frac{∂f_ε(x)}{∂ε} &=& \frac{∂}{∂ε} ∫_{ℝ^{n+1}} f(x-t)s_{ε}(t) dt \cr
-    &=& \frac{∂}{∂ε} ∫_{ℝ^{n+1}} f(t)s_{ε\|x\|}(x-t) dt \cr
-    &=&  \frac{∂}{∂ε} Σ_{i∈V(x)} ∫_{Δᵢ} f(t)s_{ε\|x\|}(x-t) du \cr
-    &=&  Σ_{i∈V(x)} ∫_{Δᵢ} f(t) \frac{∂}{∂ε} s_{ε\|x\|}(x-t) du \cr
-       &=& Σ_{i∈V(x)}∫_{Δᵢ} f(x-t) s_{ε\|x\|}(t) dt
-  \end{eqnarray*}
-
-\end{proof}
-
-  \begin{prop}
-    Let $p$ be an homogeneous polynomial in $n+1$ variables.
-    Let $Δ$ be an ad
-  \end{prop}
-  \begin{proof}
-
-  \end{proof}
-\end{document}

### 2021-02-10 article/main.tex
work on article + file splitting

--- 2020-10-31 article/main.tex
@@
 \DeclareUnicodeCharacter{8348}{_t}
+\DeclareUnicodeCharacter{8342}{_k}
 \DeclareUnicodeCharacter{8339}{_x}
@@
 \DeclareUnicodeCharacter{7523}{_r}
+\DeclareUnicodeCharacter{7580}{^c}
+\DeclareUnicodeCharacter{7496}{^d}
+\DeclareUnicodeCharacter{7511}{^t}
+
 \usepackage[utf8x]{inputenc}
-\usepackage{bussproofs}
 \usepackage{graphicx}
@@
 \newcommand{\cardinal}[1]{%
-  \#{#1}%
+  \#({#1})%
 }
+\newcommand{\hull}[1]{%
+  \mathcal H({#1})%
+}
+\newcommand{\cone}[1]{%
+  \mathcal C({#1})%
+}
+\newcommand{\vertices}[1]{%
+  \mathcal V({#1})%
+}
+\newcommand{\ball}[2]{%
+  \mathcal B_{#2}({#1})%
+}
+
 \newcommand{\PNR}{{\cal P}^n(ℝ)}
@@
 
-\begin{nota}
-  We consider the real projective plane $\PNR$.
-  When ${x ∈ ℝ^{n+1}}$, we write $\overline{x} = \{ λx, λ∈ℝ_* \} ∈
-  \PNR$ the equivalent class of $x$. We define $πₙ:ℝ^{n+1} → \PNR$ the
-  projection $x ↦ \overline{x}$.
-  We use on $\PNR$ the measure induced by
-  the chord metric of the unit sphere $\SNR$:
-  $$d(\overline{x},\overline{y}) = \min\left(
-  \left\|{x \over \|x\|} - {y \over \|y\|}\right\|, \left\|{x \over \|x\|} + {y
-    \over \|y\|}\right\|\right) (∀\overline{x},\overline{y} ∈ \PNR).$$
+\input{intro}
+\input{conventions}
+\input{partition}
+\input{approximation}
+\appendix
+\input{zih}
 
-  We write $\cardinal{S}$ the cardinal of a set $S$.
-\end{nota}
+\bibliography{main}
+\bibliographystyle{plain}
 
-\begin{defi}
-  A \emph{simplicial partition} of
-  $\PNR$ is a finite set of closed simplices $(Δᵢ)_{i∈I}$ such that
-  \begin{itemize}
-  \item $⋃_{i∈I} Δᵢ = \PNR$,
-  \item for all $i≠j ∈ I$, $Δᵢ ∩ Δⱼ$ is a included in an hyperplane of $\PNR$.
-  \item for all simplices in $Δ$, there is a projective plane of $\PNR$ that do
-    not meet $Δ$.
-  \end{itemize}
-  We say that $Δᵢ$ and $Δⱼ$ are neighbour if $Δᵢ ∩ Δⱼ$ is infinite,
-  i.e. contains at least two points. We do not consider simplices sharing only
-  on vertex to be neighbour.  The neighbourhood relation is clearly reflexive
-  and symmetric.  For $i \in I$, we define $V(i) = \{ j \in I; \cardinal{(Δᵢ ∩
-    Δⱼ)} > 2\}$.
-\end{defi}
-
-\begin{defi}
-  Let $ε$ be a positive real. A \emph{simplicial partition} $(Δᵢ)_{i∈I}$ of $\PNR$ is said to be
-  $ε$-fat if for any $i,j ∈ I$, for any $x∈Δᵢ$ and $y ∈ Δⱼ$, if $d(x,y) <  ε$,
-  then $Δᵢ ∩ Δⱼ ≠ ∅$.
-\end{defi}
-
-\begin{prop}
-  Any \emph{simplicial partition} $(Δᵢ)_{i∈I}$ of $\PNR$ is $ε$-fat for
-  some $ε > 0$ small enough.
-\end{prop}
-
-\begin{proof}
-  Take $ε = \displaystyle{\min_{i,j ∈ I, Δᵢ ∩ Δⱼ = ∅} d(Δᵢ,Δⱼ)}$ which is positive because $I$ is
-  finite and for all $i ∈ I$, $Δᵢ$ is compact.
-\end{proof}
-
-\begin{defi}
-   Let $Δ = (Δᵢ)_{i∈I}$ be  a \emph{simplicial partition} of $\PNR$, a
-   \emph{$Δ$-piecewise linear map}
-   is a map $f : ℝ^{n+1} → ℝ$ which is
-continuous, piecewise linear and linear
-on each $πₙ^{-1}(Δᵢ)$ for $i ∈ I$.
-
-  For such a map, an for all $x ∈ π^{-1}Δᵢ$, we define $∇ᵢf(x) = ∇ᵢf = ∇f(y)$ for any $y ∈
-  π^{-1}\interior{Δᵢ}$. For
-  any point $x∈ℝ^{n+1}$, we define $∇_cf(x)$ the convex-hull of $\{∇ᵢf(x),
-  \hbox{ for } i \hbox{ s.t. } x ∈
-  π^{-1}Δᵢ\}$. For $x$ in $π^{-1}\interior{Δᵢ}$, $∇_cf(x) = \{∇f(x)\}$.
-\end{defi}
-
-\begin{defi}
-  We say that a $Δ$-map $f$ is smooth if for all $x ∈ \PNR$, $∇_cf(x)$ does not
-    contains $0$.
-\end{defi}
-
-\begin{prop}
-  Let $Δ = (Δᵢ)_{i∈I}$ be a \emph{simplicial partition} of $\PNR$ and
-  let $f$ be a smooth \emph{$Δ$-map}.
-  For any $ε_M>0$ such that $Δ$ is $ε$-fat, there exists a family of $C^∞$ function
-  $ε ↦ f_ε : \SNR → ℝ$ such that
-  \begin{itemize}
-  \item $∀x ∈ \SNR, f(x) - f_ε(x) → 0$ when $ε → 0$
-  \item $∀i ∈ I, ∀x ∈ ℝ^{n+1}, ∇f_ε(x) ∈ ∇_cf(x)$.
-  \item All functions $f_ε$ and $f$ have homeomorphic zero level.
-  \end{itemize}
-\end{prop}
-
-\begin{proof}
-  Let $B_r(x)$ denote the unit ball of center $x$ and radius $r$.
-  Let $s:ℝ^{n+1} → ℝ⁺$ a $C^∞$ map with support included in $B_1(x)$ and such
-  that $∫_{ℝ^{n+1}} s(t)dt = 1$ for the usual measure $dt$ of $ℝ^{n+1}$. We also
-  assume that $s(-x) = s(x)$.
-  We define $s_ε(x) = ε^{-n-1}s(ε^{-1} x)$, which has support in $B_ε(x)$ and
-  satisfies $∫_{ℝ^{n+1}} s_\epsilon(t)dt = 1$
-
-  We define $f_ε(x) = f ∗ s = ∫_{ℝ^{n+1}} f(x-t)s_ε(t) dt$ the convolution product of $f$ and
-  $s_{ε}$. $f_ε$ is $C^∞$ on $\SNR$. $|f(x) - f_ε(x)| = |∫_{ℝ^{n+1}} (f(x) - f(t))s_{ε}(x-t) dt| <
-  \max_{t∈B_ε(x)} |f(x) - f(t)| → 0$  when $ε → 0$ because $f$ is continuous.
-
-  Remark: $f_ε$ is not homogeneous, this is why we restrict its domain to
-  $\SNR$.
-
-  For the gradient, we have,
-  \begin{eqnarray*}
-    ∇f_ε(x) &=& ∇∫_{ℝ^{n+1}} f(x-t)s_{ε}(t) dt\cr
-     &=& ∇∫_{ℝ^{n+1}} f(u)∇s_{ε}(x-u) du\cr
-     &=& ∫_{ℝ^{n+1}} f(u)∇s_{ε}(x-u) du\cr
-    &=& Σ_{i∈V(x)}∫_{Δᵢ} f(x-t)∇s_{ε}(t) dt\cr
-    &=& Σ_{i∈v(x)}∫_{Δᵢ} ∇f(x-t)s_{ε}(t) dt\cr
-    &=& Σ_{i∈V(x)} λᵢ ∇ᵢf \hbox{ with } λᵢ = ∫_{Δᵢ} s_{ε}(x-t) dx > 0
-  \end{eqnarray*}
-
-  Hence $∇f_ε(x)$ is in the convex hull of the $∇ᵢf$ for $i ∈ V(x)$ because
-  $$Σ_{i∈I(x)} λᵢ = Σ_{i∈v(x)}∫_{Δᵢ} s_ε(x-t) dx =  1$$
-
-  To build the homeomorphism between the variaous zero levels, we consider the
-  following differential equation on for $γ(ε) : ℝ ↦ ℝ^{n+1}$:
-
-  $$ γ'(ε) = g(ε,γ(ε)) \hbox{ with } g(ε,x) = \frac{\frac{∂f_ε}{∂ε}(x) ∇f_ε(x)}{||∇f_ε(x)||} $$
-
-  The function $g$ is ${\cal
-    C}^∞$ for $0 < ε < ε_M$ and $x ∈ ℝ^{n+1}$ because $∇f_ε(x) ≠ 0$ on the
-  considered domain. the first thing to show it can be
-  prolongated to $ε = 0$. We have
-
-  \begin{eqnarray*}
-    ∇s_ε(x) &=& ∇(ε\|x\|)^{-n-1} s((ε\|x\|)^{-1}x) \cr
-                    &=& (-n-1) (ε\|x\|)^{-n-2} s((ε\|x\|)^{-1}x)
-    }\frac{x}{\|x\|} \cr
-     && + (ε\|x\|)^{-n-1} ∇s((ε\|x\|)^{-1}x) \left((ε\|x\|)^{-1} -
-      (ε\|x\|)^{-2}  \frac{x}{\|x\|}\right) \cr
-     && + (ε\|x\|)^{-n-1} ∇s((ε\|x\|)^{-1}x) \left((ε\|x\|)^{-1} -
-      (ε\|x\|)^{-2}\right)  \frac{x}{\|x\|} \cr
-  \end{eqnarray*}
-  \begin{eqnarray*}
-    \frac{∂}{∂ε} s_{ε\|x\|}(x-t)
-      &=& \frac{∂}{∂ε} (ε\|x\|)^{-n-1} s((ε\|x\|)^{-1}(x-t)) \cr
-    &=& \frac{∂}{∂ε} (-n-1)\|x\|(ε\|x\|)^{-n-2} s((ε\|x\|)^{-1}(x-t))
-                      - ε^{-1}(ε\|x\|)^{-n-2} ∇s((ε\|x\|)^{-1}(x-t)).(x-t)\cr
-    &=& \frac{∂}{∂ε} (-n-1)ε s_ε(x-t)
-                      - ε^{-1}(ε\|x\|)^{-n-2} ∇s((ε\|x\|)^{-1}(x-t)).(x-t)\cr
-  \end{eqnarray*}
-
-    \begin{eqnarray*}
-    \frac{∂f_ε(x)}{∂ε} &=& \frac{∂}{∂ε} ∫_{ℝ^{n+1}} f(x-t)s_{ε}(t) dt \cr
-    &=& \frac{∂}{∂ε} ∫_{ℝ^{n+1}} f(t)s_{ε\|x\|}(x-t) dt \cr
-    &=&  \frac{∂}{∂ε} Σ_{i∈V(x)} ∫_{Δᵢ} f(t)s_{ε\|x\|}(x-t) du \cr
-    &=&  Σ_{i∈V(x)} ∫_{Δᵢ} f(t) \frac{∂}{∂ε} s_{ε\|x\|}(x-t) du \cr
-       &=& Σ_{i∈V(x)}∫_{Δᵢ} f(x-t) s_{ε\|x\|}(t) dt
-  \end{eqnarray*}
-
-\end{proof}
-
-  \begin{prop}
-    Let $p$ be an homogeneous polynomial in $n+1$ variables.
-    Let $Δ$ be an ad
-  \end{prop}
-  \begin{proof}
-
-  \end{proof}
 \end{document}

### 2021-02-10 article/partition.tex
work on article + file splitting

\section{Simplicial partition}

\begin{defi}
  A \emph{simplicial partition} of
  $\PNR$ is a finite set of closed simplices $(Δᵢ)_{i∈I}$ such that
  \begin{itemize}
  \item Each $Δᵢ$ is a simplex of dimension $n$, i.e. $\cardinal{\vertices{Δ}} = n + 1$.
  \item $⋃_{i∈I} Δᵢ = \PNR$,
  \item For all $i₁ < i₂ < \dots iₖ ∈ I$, $Δ_{i₁} ∩ \dots ∩ Δ_{iₖ}$ is empty or is a simplex of dimension at most
    $n-k+1$ and $πₙ(\vertices{Δ_{i₁} ∩ \dots ∩ Δ_{iₖ}}) =
    πₙ(\vertices{Δ_{i₁}}) ∩ \dots ∩ πₙ(\vertices{Δ_{iₖ}})$.
    We can not require  $\vertices{Δᵢ ∩ Δⱼ} = \vertices{Δᵢ} ∩ \vertices{Δⱼ}$ because we may have $x ∈
    \vertices{Δᵢ}$ and $y ∈ \vertices{Δⱼ}$ with $x ≠ y$ and $\overline{x} = \overline{y}$ (see
    the example below). This conditions ensures that the intersection of
    simplices are exactly faces of lower dimensions defined by the common vertices.
%  \item We say that $Δᵢ$ and $Δⱼ$ are neighbour if $Δᵢ ∩ Δⱼ ≠ ∅$. The neighbourhood relation is clearly reflexive and symmetric.
  \end{itemize}
\end{defi}

Here is as example a partition of $\PNR$ with $2ⁿ$ simplices:
\begin{exam}\label{init_part}
Consider $B = \{x₀,\dots,xₙ\}$, the canonical base of $ℝ^{n+1}$ and
$(εᵢ)_{i ∈ \{1,\dots,2ⁿ\}}$ an enumeration of all sequences of length $n$ of
$1$ or $-1$. Then, we define $(Δᵢ)_{i∈\{1,\dots,2ⁿ\}}$ by
$$Δᵢ = πₙ(\hull{\{x₀,ε_{i,1} x₁, \dots, ε_{i,n} xₙ\}}).$$
\end{exam}

We remark in this example, that all simplices use $B$ as set of vertices. This
means that for all $i < j ∈ \{1,\dots,2ⁿ\}$, we have
  $πₙ(\vertices{Δᵢ}) = πₙ(\vertices{Δⱼ}) = πₙ(B)$ while $\vertices{Δᵢ} ≠ \vertices{Δⱼ}$.

In this examples, we have
\begin{eqnarray*}
  Δ⁺ᵢ &=& \cone{\{x₀,ε_{i,1} x₁, \dots, ε_{i,n} xₙ\}} \cr
  Δ⁻ᵢ &=& \cone{\{-x₀,-ε_{i,1} x₁, \dots, -ε_{i,n} xₙ\}} \cr
\end{eqnarray*}

\begin{defi} Let $(Δᵢ)_{i∈I}$ be a simplicial partition of $\PNR$. For $x ∈
  ℝ^{n+1} ∖\{0\}$ we define
  $I^Δ(x) = \{(i,σ) ∈ I × \{-,+\}, x ∈ Δᵢ^σ\}$ and
  $I^Δ_ε(x) = \{(i,σ) ∈ I × \{-,+\}, Δᵢ^σ ∩ \ball{x}{ε\|x\|} ≠ ∅\}$. In general we only use one
  simplicial partition at a time and we simply write $I(x)$ and $I_ε(x)$.
\end{defi}

\begin{prop}\label{Ihomo}
  Let $(Δᵢ)_{i∈I}$ be a simplicial partition of $\PNR$.
  For $x ∈  ℝ^{n+1} ∖\{0\}$ and $λ > 0$, we have $I(λx) = I(x)$ and $I_ε(λx) = I_ε(x)$.
\end{prop}

\begin{proof}
  From the fact that the set $Δᵢ^σ$ are convex cones.
\end{proof}

\begin{prop}
  Let $(Δᵢ)_{i∈I}$ be a simplicial partition of $\PNR$.
  For any $x ∈ ℝ^{n+1} ∖\{0\}$, if $ε>0$ is small enough, then $I_ε(x) = I(x)$.
\end{prop}

\begin{proof}
  Take $ε < \min_{(i,σ) ∉ I(x)} d(x,Δᵢ^σ)$, then we have $I_ε(x) = I(x)$.
\end{proof}

\begin{defi}
  Let $ε$ be a positive real. A \emph{simplicial partition} $(Δᵢ)_{i∈I}$ of
  $\PNR$ is said to be $ε$-fat if for all $x ∈ ℝ^{n+1} ∖\{0\}$ we have:
$$ ⋂_{(i,σ) ∈ I_ε(x)} Δᵢ^σ ≠ ∅$$
\end{defi}

\begin{prop} If a simplicial partition $(Δᵢ)_{i∈I}$ is $ε$-fat for $ε > 0$
  then it is $η$-fat if $0 < η ≤ ε$.
\end{prop}

\begin{proof} From the fact that for $x ∈ ℝ^{n+1} ∖\{0\}$, $I_η(x) ⊆ I_ε(x)$ if $η ≤ ε$.
\end{proof}

\begin{prop}
  Any \emph{simplicial partition} $(Δᵢ)_{i∈I}$ of $\PNR$ is $ε$-fat for
  some $ε > 0$ small enough.
\end{prop}

\begin{proof}
  First, thanks to proposition \ref{Ihomo}, we only have to check the condition
  for $ε$-fatness in $\SNR$.

  Consider a set $J ⊂ I × \{-,+\}$ with $⋂_{(i,σ)∈J} Δⱼ^σ = ∅$ (1), we first
  prove that there exists $ε_J > 0$ such that for all $x ∈ \SNR$, $J \not⊆
  I_{ε_J}(x)$. For this we assume the contrary: For any $ε>0$ there exists $x_ε
  ∈ \SNR$ such that $J ⊆ I_{ε}(x_ε)$. As $\SNR$ is compact, we can extract a
  sequence $(εₙ,xₙ)_{n ∈ \mathbb N}$ which converges to $(0,x)$ for some $x ∈
  \SNR$, with $J ⊆ I_{εₙ}(x_{εₙ})$ for all $n ∈ \mathbb N$. Thus, for any $(i,σ)
  ∈ J$ and $n ∈ \mathbb N$, we have $\ball{xₙ}{εₙ} ∩ Δᵢ^σ ≠ ∅$ which implies
  $d(xₙ,Δᵢ^σ) < εₙ$. As $Δᵢ^σ$ are closed convex cone, this implies that $x ∈
  Δᵢ^σ$ for any $(i,σ) ∈ J$ which contradicts the hypothesis (1).

  We end the proof by remarking that the simplicial partition is $ε$-fat if we
  take $ε$ the minimum of all $ε_J$ for $J ⊂ I$ with $∩_{(i,σ)∈J} Δᵢ^σ =
  ∅$. This is well defined as $I$ hence his power-set are finite. Indeed, if $J
  = I_{ε}(x)$, and $∩_{(i,σ)∈J} Δᵢ^σ = ∅$, then $J \not ⊆ I_{ε_J}(x) ⊇ I_{ε}(x)
  = J$ which is contradictory.
\end{proof}

### 2021-02-10 article/zih.tex
work on article + file splitting

\section{Testing zero in convex hull}

The central test in our algorith is to know if the null vector is in the convex
hull of a given set of vector of $ℝ^d$, or as it is clearly equivalent, in its convex
cone.

More precisely, the problem we want to solve can be defined as follows:
\begin{defi}
  \begin{tabular}{ll}
  Input:& a real $n × d$ matrix $A$. \cr
  Output:& a non nul vector $X ∈ ℝ_+^n$ such that $^tX A = 0$ \cr
  or& a vector $N ∈ ℝ^d$ such that $A N > 0$
  \end{tabular}
\end{defi}

This does correspond to our problem: if zero is in the convex hull of the lines
of the matrix $A$, then we can produce the wanted vector $X∈ ℝ_+^n$. It zero is not in
the convex hull, then we can return the normal $N∈ ℝ^d$ of a linear plane such that
all the lines of $A$ lie on the same side of this plane.

We start the algorithm with an initial vector $X_0∈ ℝ_+^n$, with positive coefficients
summing to one, for instance $X₀=\frac{1}{n}ᵗ(1,1,\dots,1,1)$.
We define $N_i = tX_i A$. We also define a vector $P_0 = 0 ∈ ℝ_+^n $.

The algorithm then perform two kind of steps:

\paragraph*{Conjugate steps}, which are somehow inspired by the conjugate
gradient method.

First we define $J ∈ ℝ_+^n = (1,1,\dots,1,1)$ and $ν(X) = \frac{1}{J.X} X$ which
normalise the vector $X$ to have all its coefficient sum to one. We will use
$ν(X)$ only one non null vector in $ℝ_+^n$.

If for all lines $Aⱼ$ of $A$ we have $Aⱼ.Nᵢ > 0$ then the algorithm
stops and output $N = Nᵢ$. Otherwise we select $Dᵢ = δⱼ$ such that $Aⱼ.Nᵢ ≤ 0$ and minimum.
Then we compute $α>0,β ∈ ℝ$, $X_{i+1} = ν(Xᵢ + αDᵢ+βPᵢ)$, such that
  $\|ᵗX_{i+1} A\|²$ is minimum. We have
  \begin{eqnarray*}
    f(α,β) &=& \|ᵗX_{i+1} A\|² \cr
    &=& \frac{\|ᵗXᵢ A + αᵗDᵢA + βᵗPᵢA\|²}{(1 + α + β)²}\cr
    &=& \frac{\|Nᵢ + αᵗAⱼ + βᵗPᵢA\|²}{(1 + α + βPᵢ.J)²}\cr
    &=& \frac{\|Nᵢ\|² + α² + β²\|ᵗPᵢA\|² + 2 α Nᵢ.Aⱼ + 2 β Nᵢ.ᵗPᵢA + 2αβ Aⱼ.ᵗPᵢA}
    {1 + α² + β²(Pᵢ.J)² + 2α + 2βPᵢ.J + 2αβPᵢJ}\cr
    \frac{∂f(α,β)}{∂α}
    &=& \frac{\begin{array}{cl}
        &(2α + 2 Nᵢ.Aⱼ + 2βAⱼ.ᵗPᵢA)(1 + α² + β²(Pᵢ.J)² + 2α + 2βPᵢ.J + 2αβPᵢJ)\cr
        - &(\|Nᵢ\|² + α² + β²\|ᵗPᵢA\|² + 2 α Nᵢ.Aⱼ + 2 β Nᵢ.ᵗPᵢA + 2αβ
      Aⱼ.ᵗPᵢA)(2α + 2 + 2βPᵢJ)
      \end{array}}{(1 + α² + β²(Pᵢ.J)² + 2α + 2βPᵢ.J + 2αβPᵢJ)²}\cr
    &=&
    {(1 + α² + β²(Pᵢ.J)² + 2α + 2βPᵢ.J + 2αβPᵢJ)²}\cr
  \end{eqnarray*}

### 2021-02-20 article/approximation.tex
work on article

@@
 Let $p$ be an homogeneous polynomial of degree $d$ on
-$ℝ^{n+1}$. Let $(Δᵢ)_{i∈I}$ be an $ε$-fat simplicial partition of $\PNR$.
+$ℝ^{n+1}$. Let $(Δᵢ)_{i∈I}$ be a simplicial partition of $\PNR$.
 Let $\overline{p}$ be the $Δ$-linear approximation of $p$.
-We define the condition $Π_ε(x)$ to be true if and only if $p$ and
-$\overline{p}$ are both positive or both negative on $\ball{x}{ε}$.
+We define the condition $Π(x)$ to be true if and only if $p(x)$ and
+$\overline{p}(x)$ are both positive or both negative.
 \end{defi}
@@
 Let $p$ be an homogeneous polynomial of degree $d$ on
-$ℝ^{n+1}$. Let $(Δᵢ)_{i∈I}$ be an $ε$-fat simplicial partition of $\PNR$.
+$ℝ^{n+1}$. Let $(Δᵢ)_{i∈I}$ be a simplicial partition of $\PNR$.
 Let $\overline{p}$ be the $Δ$-linear approximation of $p$.
@@
 \begin{enumerate}
-\item $∀x ∈  ℝ^{n+1}∖\{0\}, Π_ε(x) \hbox{ or } 0 ∉ \cone{\{∇p(x)\} ∪ \{∇ᵢ^σp, (i,σ) ∈ I_ε(x)\}}$
-\item $∀x ∈  ℝ^{n+1}∖\{0\}, Π_ε(x) \hbox{ or } 0 ∉ \hull{\{∇p(x)\} ∪ \{∇ᵢ^σp, (i,σ) ∈ I_ε(x)\}}$
-\item $∀x ∈  \SNR, Π_ε(x) \hbox{ or } 0 ∉ \cone{\{∇p(x)\} ∪ \{∇ᵢ^σp, (i,σ) ∈ I_ε(x)\}}$
-\item $∀x ∈  \SNR, Π_ε(x) \hbox{ or } 0 ∉ \hull{\{∇p(x)\} ∪ \{∇ᵢ^σp, (i,σ) ∈ I_ε(x)\}}$
-\item\label{hb} $∀x ∈  ℝ^{n+1}∖\{0\}, Π_ε(x) \hbox{ or } ∃δ ∈ ℝ^{n+1}∖\{0\},
+\item $∀x ∈  ℝ^{n+1}∖\{0\}, Π(x) \hbox{ or } 0 ∉ \cone{\{∇p(x)\} ∪ \{∇ᵢ^σp, (i,σ) ∈ I(x)\}}$
+\item $∀x ∈  ℝ^{n+1}∖\{0\}, Π(x) \hbox{ or } 0 ∉ \hull{\{∇p(x)\} ∪ \{∇ᵢ^σp, (i,σ) ∈ I(x)\}}$
+\item $∀x ∈  \SNR, Π(x) \hbox{ or } 0 ∉ \cone{\{∇p(x)\} ∪ \{∇ᵢ^σp, (i,σ) ∈ I(x)\}}$
+\item $∀x ∈  \SNR, Π(x) \hbox{ or } 0 ∉ \hull{\{∇p(x)\} ∪ \{∇ᵢ^σp, (i,σ) ∈ I(x)\}}$
+\item\label{hb} $∀x ∈  ℝ^{n+1}∖\{0\}, Π(x) \hbox{ or } ∃δ ∈ ℝ^{n+1}∖\{0\},
   \left\{\begin{array}{l} δ.∇p(x) > 0 \hbox{ and}\cr
-    ∀(i,σ) ∈ I_ε(x), δ.∇ᵢ^σp > 0
+    ∀(i,σ) ∈ I(x), δ.∇ᵢ^σp > 0
   \end{array}\right.$
@@
 
-  The equivalence (1)  ↔ (3) comes from the fact that $p$ is homogeneous hence
-  $\nabla(p)(λx) = λ^{d-1}\nabla(p)(x)$ for $λ > 0$ and from proposition $\ref{Ihomo}$.
+  The equivalence (1)  ↔ (3) comes from proposition $\ref{Ihomo}$ and the fact that $p$ is homogeneous hence
+  $\nabla(p)(λx) = λ^{d-1}\nabla(p)(x)$ for $λ > 0$.
 
   The equivalence (2) ↔ (5) is a form of Han-Banach theorem ensuring the
-  existence of a supporting hyper-plane. The vector $δ$ is a normal vector of
-  this supporting hyperplane \cite{Zal02}.
+  existence of a supporting hyper-plane for points outside a convex body. The
+  vector $δ$ is a normal vector of this supporting hyperplane \cite{Zal02}.
 \end{proof}
@@
 Let $p$ be an homogeneous polynomial of degree $d$ on
-$ℝ^{n+1}$. Let $(Δᵢ)_{i∈I}$ be an $ε$-fat simplicial partition of $\PNR$.
+$ℝ^{n+1}$. Let $(Δᵢ)_{i∈I}$ be a simplicial partition of $\PNR$.
 
@@
 $ℝ^{n+1}$.
-  Let $(Δᵢ)_{i∈I}$ be an $ε$-fat simplicial partition of $\PNR$ adapted to $p$.
+  Let $(Δᵢ)_{i∈I}$ be a simplicial partition of $\PNR$ adapted to $p$.
   We can find a $C^∞$ function $δ$ in $ℝ^{n+1} ∖ \{0\} → ℝ^{n+1}∖\{0\} $
   and $μ > 0$ such that:
-  $$∀x ∈  ℝ^{n+1}∖\{0\}, Π_ε(x) \hbox{ or } \left\{
+  $$∀x ∈  ℝ^{n+1}∖\{0\}, Π(x) \hbox{ or } \left\{
   \begin{array}{l}δ(x).∇p(x) > μ\|x\|^{d-1} \hbox{ and } \cr ∀(i,σ) ∈
-  I_ε(x), δ(x).∇ᵢ^σp > μ.\end{array}\right.
+  I(x), δ(x).∇ᵢ^σp > μ.\end{array}\right.
   $$
@@
 ∈ ℝ^{n+1}$ such that $δ₀(x).∇p(x) > 0$ and $∀(i,σ) ∈ I_ε(x), δ₀(x).∇ᵢ^σp > 0$.
-We can also assume that $d₀(λ x) = d₀(x)$ for $λ > 0$ for the same reason as in
+We can also assume that $δ₀(λ x) = δ₀(x)$ for $λ > 0$ for the same reason as in
 the proof of $(1) ↔ (3)$ above.
@@
 
-First, $(i,σ) ∈ I_ε(y) ↔ \ball{y}{ε} ∩ Δᵢ^σ ≠ ∅$ is a closed condition and the
-contrary is an open condition. Hence, for $x ∈ℝ^{n+1}∖\{0\}$, we find $η > 0$
+First, $(i,σ) ∈ I_ε(y) ↔ \cball{y}{ε} ∩ Δᵢ^σ ≠ ∅$ is a closed condition and the
+contrary is an open condition. The condition $Π_ε(x)$ is also an open
+condition. Hence, for $x ∈ℝ^{n+1}∖\{0\}$, we find $η > 0$
 small enough to have $y ∈
-\ball{x}{2η}$ gives $(i,σ) ∉ I_ε(x)$ implies $(i,σ) ∉ I_ε(y)$, which means that
-for $y ∈ \ball{x}{2η}$, we have $I_ε(y) ⊆ I_ε(x)$ and therefore,
+\ball{x}{2η}$ gives $Π_ε(x)$ or $(i,σ) ∉ I_ε(x)$ implies $(i,σ) ∉ I_ε(y)$.
 
-$$∀y ∈ \ball{x}{2η(x)}, ∀(i,σ) ∈ I_ε(y), d₀(x).∇ᵢ^σp > 0.$$
+which means that
+for $y ∈ \ball{x}{2η}$, we have $Π_ε(x)$ or $I_ε(y) ⊆ I_ε(x)$ and therefore,
+
+$$∀y ∈ \ball{x}{2η(x)}, Π_ε(x) \hbox{ or } ∀(i,σ) ∈ I_ε(y), δ₀(x).∇ᵢ^σp > 0.$$
 
@@
 small enough to have $y ∈ \ball{x}{2η}$
-implies $d₀(x).∇p(y) > 0$. Grouping both results yields the wanted real $η(x)$
+implies $Π_ε(x)$ or $δ₀(x).∇p(y) > 0$. Grouping both results yields the wanted real $η(x)$
 such that
 
-$$∀x ∈ℝ^{n+1}∖\{0\}, ∀y ∈ \ball{x}{2η(x)},
-\left\{\begin{array}{l} d₀(x).∇p(y) > 0 \hbox{ and}\cr
-∀(i,σ) ∈ I_ε(y), d₀(x).∇ᵢ^σp > 0
+$$∀x ∈ℝ^{n+1}∖\{0\}, ∀y ∈ \ball{x}{2η(x)}, Π_ε(x) \hbox{ or }
+\left\{\begin{array}{l} δ₀(x).∇p(y) > 0 \hbox{ and}\cr
+∀(i,σ) ∈ I_ε(y), δ₀(x).∇ᵢ^σp > 0
 \end{array}\right.
@@
 
-Now, for $x ∈ \SNR$, the balls $\ball{x}{η(x)}$ cover $\SNR$, so we can
+Now, for $x ∈ \SNR$, the open balls $\ball{x}{η(x)}$ cover $\SNR$, so we can
 find a finite family $(xⱼ)_{j∈J}$ such that the balls $\ball{x}{η(xⱼ)}$ cover
-$\SNR$. We also take $η = min_{j ∈ J} η(xⱼ)$.
+$\SNR$. We also take $η = \min_{j ∈ J} η(xⱼ)$.
 
-Nest, for each $xⱼ ∈ \SNR$, $j ∈ J$, we choose a measurable set
+Next, for each $xⱼ ∈ \SNR$, $j ∈ J$, we choose a measurable set
 $Dⱼ ⊂ \ball{x}{η(xⱼ)}$ such that $\SNR$ is a disjoin union of all
-$Dⱼ$. And we define $d₁ : \SNR → ℝ^{n+1}∖\{0\}$ with $d₁(x) = d₀(xⱼ)$ if $x ∈ Dⱼ$.
+$Dⱼ$. And we define $d₁ : \SNR → ℝ^{n+1}∖\{0\}$ with $δ₁(x) = δ₀(xⱼ)$ if $x ∈ Dⱼ$.
 
@@
 
-$$ d : \SNR → ℝ^{n+1}∖\{0\} \hbox{ with } d(x) = ∫_{ℝ^{n+1}} d₁(x - η t)
+$$ δ : \SNR → ℝ^{n+1}∖\{0\} \hbox{ with } δ(x) = ∫_{ℝ^{n+1}} δ₁(x - η t)
 s(t) dt$$
 
-Similarly to a convolution product, we have $d(x) = ∫_{ℝ^{n+1}} η^{n +1} d₁(u)
-s(\frac{x - u}{η}) du$ and therefore $d$ is $C^∞$ on $\SNR$.
+Similarly to a convolution product, using the change of variable $u = x - ηt$, we have $δ(x) = ∫_{ℝ^{n+1}} η^{n +1} δ₁(u)
+s(\frac{x - u}{η}) du$ and therefore $δ$ is $C^∞$ on $\SNR$.
 
 Moreover, if we take $x ∈ \SNR$, we can write
-$$ d(x) = Σ_{j∈J} d₁(xⱼ) ∫_{x - η t ∈ Dⱼ} s(t) dt$$
+$$ δ(x) = Σ_{j∈J} δ₁(xⱼ) ∫_{x - η t ∈ Dⱼ} s(t) dt$$
 
@@
 if $λⱼ(x) > 0$, we have $d(x,xⱼ) < 2η(xⱼ)$.
-which implies $d₁(xⱼ).∇p(x) > 0$ and $∀(i,σ) ∈ I_ε(x), d₁(xⱼ).∇ᵢ^σp > 0$.
+which implies $Π_ε(x)$ or both $δ₁(xⱼ).∇p(x) > 0$ and $∀(i,σ) ∈ I_ε(x), δ₁(xⱼ).∇ᵢ^σp > 0$.
 
-Moreover, the coefficient $λⱼ$ are positive. Therefore, $d(x) = Σ_{j∈J}
-λⱼ(x) d₁(xⱼ)$ implies $d(x).∇p(x) > 0$ and $∀(i,σ) ∈ I_ε(x), d(x).∇ᵢ^σp >
+Moreover, the coefficient $λⱼ$ are positive. Therefore, $δ(x) = Σ_{j∈J}
+λⱼ(x) δ₁(xⱼ)$ implies $δ(x).∇p(x) > 0$ and $∀(i,σ) ∈ I_ε(x), δ(x).∇ᵢ^σp >
 0$.  Thus, we have:
-$$∀x ∈ \SNR, d(x).∇p(x) > 0 \hbox{ and }∀(i,σ) ∈
-  I_ε(x), d(x).∇ᵢ^σp > 0.$$
+$$∀x ∈ \SNR, Π_ε(x) \hbox{ or } δ(x).∇p(x) > 0 \hbox{ and }∀(i,σ) ∈
+  I_ε(x), δ(x).∇ᵢ^σp > 0.$$
 
   As $\SNR$ is compact, we can find $μ > 0$ such that
-$$∀x ∈ \SNR, d(x).∇p(x) > μ \hbox{ and }∀(i,σ) ∈
-  I_ε(x), d(x).∇ᵢ^σp > μ.$$
+$$∀x ∈ \SNR, Π_ε(x) \hbox{ or } δ(x).∇p(x) > μ \hbox{ and }∀(i,σ) ∈
+  I_ε(x), δ(x).∇ᵢ^σp > μ.$$
 
-  To extend this to $ℝ^{n+1}∖\{0\}$, we just have to set $d(λx) = d(x)$ for $λ >
+  To extend this to $ℝ^{n+1}∖\{0\}$, we just have to set $δ(λx) = δ(x)$ for $λ >
   0$ and as $p$ is homogeneous of degree $d$, we have:
 
-  $$∀x ∈  ℝ^{n+1} ∖ \{0\}, d(x).∇p(x) > μ\|x\|^{d-1} \hbox{ and }∀(i,σ) ∈
-  I_ε(x), d(x).∇ᵢ^σp > μ.$$
+  $$∀x ∈  ℝ^{n+1} ∖ \{0\}, Π_ε(x) \hbox{ or } \left\{\begin{array}{l}
+  δ(x).∇p(x) > μ\|x\|^{d-1} \hbox{ and }\cr∀(i,σ) ∈
+  I_ε(x), δ(x).∇ᵢ^σp > μ
+  \end{array}\right.$$
 \end{proof}
@@
   at least one common cone $Δᵢ^σ$ with $(i, σ) ∈ I(x)$.
-  If they belong to more than one cone, the
-  gradient $∇ᵢ^σ . d$ coincide and are the limit.
+  If they both belong to more than one cone, as we take the gradient of linear
+  functions that coincide on the intersection of several simplex in a direction which
+  is parallel to this intersection, the gradient $∇ᵢ^σp . d$ coincide and are the limit.
   This tells us moreover that we have
@@
 
-  Next, we Consider the differential equation $x'(t) = d(x(t))$.
+  Next, we Consider the differential equation $x'(t) = δ(x(t))$.
   This differential equation has
-  unique solutions in the neighbourhood of $x$ because $d$ is $C^∞$.
+  unique solutions in the neighbourhood of $x$ because $δ$ is $C^∞$.
 
@@
   $x : L → Ω$ with $0$ in the interior of the interval $L$ and $x(0)$ in
-  the interior of $Ω$.
+  the interior of $Ω$. The same reasoning will apply in region where $p(x) ≥ 0$
+  and $\overline{p}(x) ≤ 0$.
 
@@
   no $x ∈ Ω$ satisfies the condition $Π_ε(x)$. Hence we have
-  $d(x). ∇p(x) > 0$, so the solution is increasing in $p$.
-  Similarly, $∀(i,σ) ∈ I_ε(x), d(x). ∇ᵢ^σ > 0$, hence the solution is also
+  $d(x). ∇p(x) > μ\|x\|^{d-1} > 0$, so the solution is increasing in $p$.
+  Similarly, $∀(i,σ) ∈ I_ε(x), d(x). ∇ᵢ^σ > μ > 0$, hence the solution is also
   increasing in $\overline{p}$.
@@
   \left(\frac{p(x(0))}{\|p\|}\right)^{\frac{1}{d}})$,
-  we have $\|x(t)\| > R$.
+  we have $\|x(t)\| > R$.   This exludes solution converging to $0$.
 
-  Next, consider $f(t) = p(x(t))$, $f'(t) = ∇p(x(t)).d(x(t)) > μ R^{d-1} $
-  Hence $-p(x(0)) > ∫_J⁺ f'(t) dt > t μ R^{d-1}$. Therefore the interval $J$ has
-  an upper bound $b > 0$.
+  Next, consider $f(t) = p(x(t))$, $f'(t) = ∇p(x(t)).δ(x(t)) > μ R^{d-1} $
+  Therefore $f(t) - f(0) >  ∫₀ᵗ f'(t) dt > t μ R^{d-1}$. Therefore $p(x(t)$
+  reaches the zero locus of $p$ for $0 < t < - f(0) / μ R^{d-1}$.
+  It will also reach  the zero locus of $\overline{p}$ for $0 > t > - f(0) / μ$.
+  This excludes all solution with unbounded interval definition.
 
-  Similarely, we considering $g(t) = \overline{p}(x(t))$, we find that
-  $J$ as a lower bound $a < 0$.
+  From this we can define the homeomorphism $ϕ$ between the zero loci of $p$ and
+  and $\overline{p}$. Consider a point $x₀$ such that $p(x₀) = 0$. If
+  $\overline{p}(x₀) = 0$, we take $ϕ(x₀) = x₀$. If $\overline{p}(x₀) < 0$, we
+  consider the solution of the equation $x'(t) = δ(x(t))$, with $x(0) = x₀$.
+  This solution reaches $\overline{p}(x(t))$ for some $t₁ < 0$ and we take
+  $ϕ(x₀) = x(t₁)$. If $\overline{p}(x₀) > 0$, we
+  consider the solution of the equation $x'(t) = δ(x(t))$, with $x(0) = x₀$.
+  This solution reaches $\overline{p}(x(t))$ for some $t₁ > 0$ and we take
+  $ϕ(x₀) = x(t₁)$.
 
-  %% Thus, our maximal solution may only
-  %% start at $0$, infinity or a border of $Ω$ where $\overline{p} = 0$ and may only end
-  %% at $0$, infinity or a border of $Ω$ where $p = 0$.
+  The function $ϕ$ is bijective, because its inverse can be constructed in the
+  same way and solution of the differential equation is unique. And it is
+  $C^∞$ because $δ$ is $C^∞$.
+\end{proof}
 
-  %% First, we rule out zero, as $p(x(t))$ is increasing and $p(x(t)) ≤ 0$ on the
-  %% whole region, the solution can not start at $x = 0$, because $p(0) = 0$.  as
-  %% $\overline{p}(x(t)) ≥ 0$ and $\overline{p}(x(t))$ is increasing the solution can
-  %% not end at $0$.
-
-  %% If a the solution starts at infinity, $\overline{p}(x(t))$ is increasing
-  %% and $\overline{p}(x(t)) ≥ 0$, Hence when $x(t)$ converges to the beginning of
-  %% the interval $I$, we have $\overline{p}(x(t))$ which converges to a finite
-  %% limite. And if $x(t)$ approaches infinity ...
-
-  %% $p(x(t))$ must have a finite limit at the begginning
-  %% of the solution which implies that $∇p(x(t)).x'(t)$ should converge toward $0$
-  %% when $t$ converges to the beginning of $I$. This is not possible
-
-  %% over $ℝ^{n+1} \setminus \{0\}$, it has maximal solution. We consider maximal solution
-  %% $x : [0, a[ \to ℝ^{n+1} \setminus \{0\}$ starting with $p(x(0)) = 0$, with
-  %%     $x_0 \in ℝ^{n+1} \setminus \{0\}$.
-
-  %%     We have $p(x(t))' = \nabla p(x(t)) . d(x(t)) > 0$, which means that
-  %%     $p(x(t))$ is increasing.
-
-  %%     We have $\overline{p(x(t))} = \nabla \overline{p}(x(t)). d(x(t)) > 0$
-  %%     hence $\overline{p(x(t))}$ is decreasing. If $x(t)$ would approach
-  %%     infinity, the it would do so with a derivate approaching the plane
-\end{proof}
+%<!-- Local IspellDict: british -->
+%<!-- Local IspellPersDict: ~/.ispell-british -->

### 2021-02-20 article/intro.tex
work on article

\section{Introduction}

\begin{figure}
  \begin{center}
    \includegraphics[width=\linewidth]{quartic-M-2.png}
    \caption{piecewise linear approximation of a quartic surface}
  \end{center}
\end{figure}

We present an algorithm solving smooth systems of homogeneous polynomial
equations $\{x ∈ \PNR, p₁(x) = 0, \dots, pₖ(x) = 0\}$. By \emph{smotth},
we mean than the vectors $(∇p₁(x),\dots,∇pₖ(x))$ are linearly independant for
all $x$. By
\emph{solving} we mean finding a piecewise linear approximation of the
solution that is homeomorphic to the real solution allowing for instance to
compute topological invariants of the solution and in particular the number of
connected components. We therefore do not limit ourselves to the zero
dimensional case.

To obtain the solution, we partition the projective space $\PNR$ is a
family of simplices $(Δⱼ)_{j∈J}$, then we construct
the piecewise linear functions $\overline{p}ᵢ$ that are linear on each $Δⱼ$ and
coincide with $pᵢ$ on the vertices of the simplices $Δⱼ$.

Then, we give a criteria to ensure that the set $\{x ∈ \PNR,
\overline{p}₁(x) = 0, \dots, \overline{p}ₖ(x) = 0\}$ is homeomorphic to the
solution of the original system.

The criteria can be summarised as follows:
\begin{itemize}
  \item For each point $x$ of $\PNR$, consider the set of simplices $\{Δ_{j₁},
    \dots, Δ_{jₘ}\} = \{Δⱼ, x ∈ Δⱼ\}$.
  \item For each polynomial $pᵢ$, this gives a set of $m+1$ vector: the gradient
    of the original polynomial $pᵢ$ at $x$, and the gradient of each linear
    function ${\overline{p}ᵢ}_{\restriction Δ_{jₖ}}$ at $x$:
    $$Gᵢ(x) = \{∇pᵢ(x),∇{\overline{p}ᵢ}_{\restriction Δ_{j₁}}(x),  \dots,
      ∇{\overline{p}ᵢ}_{\restriction Δ_{jₘ}}(x)\}$$
    \item Then the criteria is satisfied if for any $x \in \PNR$ such that ...
      and for any
      $(ε₁,\dots,εₖ) ∈ \{-,+\}ᵏ$, $0$ is not in the convex hull of
      $ε₁ G₁(x) ∪ \dots ∪ εₖ Gₖ(x) $.
\end{itemize}

This gives the spirit of the criterion. The real criterion needs a bit more care
as gradient of polynomials are not well defined
This criteria can be checked in practice with a sufficient condition as precise
as we want (up to more computation) using the fact that polynomials written in
the Berstein bases are in the convex hull of their coefficients.

The part of the algorithm is to construct a partition of $\PNR$ that satisfy the
above criterion. We are not yet able to prove that this part of our algorithm
terminates. But it does terminate in practice. It even seem that it requires a
partition whose size is bounded by a constant that only depends upon the number
of variables, number of polynomials and their degree (see conjecture \ref{?}).

Is important to remark that the correction of the algorithm only requires the
criterion to be proved correct, which is done in that paper.

%<!-- Local IspellDict: british -->
%<!-- Local IspellPersDict: ~/.ispell-british -->

### 2021-02-20 article/partition.tex
work on article

@@
   ℝ^{n+1} ∖\{0\}$ we define
-  $I^Δ(x) = \{(i,σ) ∈ I × \{-,+\}, x ∈ Δᵢ^σ\}$ and
-  $I^Δ_ε(x) = \{(i,σ) ∈ I × \{-,+\}, Δᵢ^σ ∩ \ball{x}{ε\|x\|} ≠ ∅\}$. In general we only use one
-  simplicial partition at a time and we simply write $I(x)$ and $I_ε(x)$.
+  $I^Δ(x) = \{(i,σ) ∈ I × \{-,+\}, x ∈ Δᵢ^σ\}$. In general we only use one
+  simplicial partition at a time and we simply write $I(x)$.
 \end{defi}
@@
   Let $(Δᵢ)_{i∈I}$ be a simplicial partition of $\PNR$.
-  For $x ∈  ℝ^{n+1} ∖\{0\}$ and $λ > 0$, we have $I(λx) = I(x)$ and $I_ε(λx) = I_ε(x)$.
+  For $x ∈  ℝ^{n+1} ∖\{0\}$ and $λ > 0$, we have $I(λx) = I(x)$.
 \end{prop}
@@
 
-\begin{prop}
-  Let $(Δᵢ)_{i∈I}$ be a simplicial partition of $\PNR$.
-  For any $x ∈ ℝ^{n+1} ∖\{0\}$, if $ε>0$ is small enough, then $I_ε(x) = I(x)$.
-\end{prop}
-
-\begin{proof}
-  Take $ε < \min_{(i,σ) ∉ I(x)} d(x,Δᵢ^σ)$, then we have $I_ε(x) = I(x)$.
-\end{proof}
-
-\begin{defi}
-  Let $ε$ be a positive real. A \emph{simplicial partition} $(Δᵢ)_{i∈I}$ of
-  $\PNR$ is said to be $ε$-fat if for all $x ∈ ℝ^{n+1} ∖\{0\}$ we have:
-$$ ⋂_{(i,σ) ∈ I_ε(x)} Δᵢ^σ ≠ ∅$$
-\end{defi}
-
-\begin{prop} If a simplicial partition $(Δᵢ)_{i∈I}$ is $ε$-fat for $ε > 0$
-  then it is $η$-fat if $0 < η ≤ ε$.
-\end{prop}
-
-\begin{proof} From the fact that for $x ∈ ℝ^{n+1} ∖\{0\}$, $I_η(x) ⊆ I_ε(x)$ if $η ≤ ε$.
-\end{proof}
-
-\begin{prop}
-  Any \emph{simplicial partition} $(Δᵢ)_{i∈I}$ of $\PNR$ is $ε$-fat for
-  some $ε > 0$ small enough.
-\end{prop}
-
-\begin{proof}
-  First, thanks to proposition \ref{Ihomo}, we only have to check the condition
-  for $ε$-fatness in $\SNR$.
-
-  Consider a set $J ⊂ I × \{-,+\}$ with $⋂_{(i,σ)∈J} Δⱼ^σ = ∅$ (1), we first
-  prove that there exists $ε_J > 0$ such that for all $x ∈ \SNR$, $J \not⊆
-  I_{ε_J}(x)$. For this we assume the contrary: For any $ε>0$ there exists $x_ε
-  ∈ \SNR$ such that $J ⊆ I_{ε}(x_ε)$. As $\SNR$ is compact, we can extract a
-  sequence $(εₙ,xₙ)_{n ∈ \mathbb N}$ which converges to $(0,x)$ for some $x ∈
-  \SNR$, with $J ⊆ I_{εₙ}(x_{εₙ})$ for all $n ∈ \mathbb N$. Thus, for any $(i,σ)
-  ∈ J$ and $n ∈ \mathbb N$, we have $\ball{xₙ}{εₙ} ∩ Δᵢ^σ ≠ ∅$ which implies
-  $d(xₙ,Δᵢ^σ) < εₙ$. As $Δᵢ^σ$ are closed convex cone, this implies that $x ∈
-  Δᵢ^σ$ for any $(i,σ) ∈ J$ which contradicts the hypothesis (1).
-
-  We end the proof by remarking that the simplicial partition is $ε$-fat if we
-  take $ε$ the minimum of all $ε_J$ for $J ⊂ I$ with $∩_{(i,σ)∈J} Δᵢ^σ =
-  ∅$. This is well defined as $I$ hence his power-set are finite. Indeed, if $J
-  = I_{ε}(x)$, and $∩_{(i,σ)∈J} Δᵢ^σ = ∅$, then $J \not ⊆ I_{ε_J}(x) ⊇ I_{ε}(x)
-  = J$ which is contradictory.
-\end{proof}
+%<!-- Local IspellDict: british -->
+%<!-- Local IspellPersDict: ~/.ispell-british -->

### 2021-02-20 article/zih.tex
work on article

@@
 
-The central test in our algorith is to know if the null vector is in the convex
+The central test in our algorithm is to know if the null vector is in the convex
 hull of a given set of vector of $ℝ^d$, or as it is clearly equivalent, in its convex
@@
   \end{eqnarray*}
+
+%<!-- Local IspellDict: british -->
+%<!-- Local IspellPersDict: ~/.ispell-british -->

### 2021-05-28 article/conventions.tex
work on article
article

@@
 
-We use on $\PNR$ the measure induced by
+We use on $\PNR$ the measure and topology induced by
 the chord metric of the unit sphere:
@@
 
-If $x ∈ \PNR$ (resp. $ℝ^{n+1}$), $\ball{x}{r}$ denotes the closed ball of center $x$
-and radius $r$.
+If $x ∈ \PNR$ (resp. $ℝ^{n+1}$), $\ball{x}{r}$ denotes the open ball of center $x$
+and radius $r$ and $\cball{x}{r}$ denotes its closure.
 
@@
 For $A ⊂ ℝ^{n+1}$, $\hull{A}$ denotes the convex hull of $A$ and $\cone{A}$ its
-convex cone.
+convex cone:
+$$\cone{A} = \{ ∑_{i=0}ⁿ λᵢ xᵢ, x₀,\dots,xₙ ∈ A, λ₀,\dots,λₙ∈ℝ^⋆₊\}$$
+$$\hull{A} = \{ ∑_{i=0}ⁿ λᵢ xᵢ, x₀,\dots,xₙ ∈ A, λ₀,\dots,λₙ∈ℝ^⋆₊,
+∑_{i=1}ⁿ λᵢ=1 \}$$
 
@@
 \end{itemize}
+
+%<!-- Local IspellDict: british -->
+%<!-- Local IspellPersDict: ~/.ispell-british -->

### 2021-06-15 article/approximation.tex
work on article

@@
 For $i ∈ I$, $σ ∈ \{+,-\}$, we define $∇ᵢ^σp = ∇\overline{p}(x)$
-for any $x ∈ Δ^σᵢ$, as the gradient is constant over $Δ^σᵢ$ for a linear function.
+for any $x ∈ Δ^σᵢ$, as the gradient is constant over $Δ^σᵢ$ for a linear
+function.
+
+We also define $\hat p(x) = \sgn(\overline{p}(x))^{d-1} \overline{p}^d(x)$. $\hat p$
+is homogeneous of degree $d$, i.e. for $x \in ℝ^{n+1}$ and $λ>0$, $\hat p(λx) = λᵈ
+\hat p(x)$. The function $\overline{p}$ and $\hat p$ obviously have the same sign and
+zero locus on $ℝ^{n+1}$.
 \end{defi}
 
-Remark: if $d$ is even (resp. odd), $\overline{p}$ is even (resp. odd).
+\begin{lemm}
+Let $p$ be an homogeneous polynomial of degree $d$ on
+$ℝ^{n+1}$. Let $(Δᵢ)_{i∈I}$ be a simplicial partition of $\PNR$.
+The function $\overline{p}$ and $\hat p$ have derivatives at $x ∈ ℝ^{n+1} ∖\{0\}$ in the
+direction $v$ if the point $I(x + h v)$ is constant
+for $h ∈ [-ε,ε]$ with $ε > 0$ is small enough.
+
+This means that for any line segment $\overline{p}$ and $\hat p$ have
+derivatives almost everywhere in the direction of this line.
+\end{lemm}
+
+\begin{proof}
+  Lines can only meet transversaly intersections $πₙ^{-1}$ of the intersection
+  of at least two simplices of $Δ$ in finitely many points.
+\end{proof}
+
+\begin{lemm}
+  From the previous lemma, with the same hypothesis, we find that $\hat p$ is
+  Lipschitz in $\ball{0}{M}$ for any $M ∈ ℝ₊$.
+\end{lemm}
+
+\begin{proof}
+  Let $L$ be the maximum of the differential of $\hat p$, where it is defined in
+  $\ball{0}{M}$. At a point $x$ in $D = \ball{0}{M} ∩ πₙ^{-1} (Δ_{i₁} ∩ \dots ∩
+  Δ_{iₖ})$, if $v$ is a direction tangent to this intersection, then $\nabla
+  \hat p_{i₁}(x) . v = \dots = \nabla \hat p_{iₖ}(x) . v$ because the functions
+  $\hat p_{i₁}, \dots, \hat p_{iₖ}$ coincide on $D$. We will denote this number
+  by $\nabla \hat p(x) . v$, which for $v$ fixed is defined almost every where,
+  and we have $\nabla \hat p(x) . v ≤ \min_{j ∈ (i₁,\dots,iₖ)} \|\nabla \hat
+  pⱼ(x)\| \|v\| ≤ L \|v\|$.
+
+  Then, we have
+  \begin{eqnarray*}
+    |\hat p(x) - \hat p(y)| &=& \left. ∫₀¹ \nabla \hat p(x + (1-t) y) . (x - y)
+    dt\right. \cr
+    &≤&   ∫₀¹ L \|(x - y)\| dt \cr
+    &≤& L \|x - y\|
+  \end{eqnarray*}
+\end{proof}
 
@@
 Let $\overline{p}$ be the $Δ$-linear approximation of $p$.
-We define the condition $Π(x)$ to be true if and only if $p(x)$ and
-$\overline{p}(x)$ are both positive or both negative.
+We define
+\begin{itemize}
+  \item the condition $Π_p(x)$ to be true if and only if $p(x)$ and
+$\overline{p}(x)$ are both positive or both negative (i.e. $p(x)
+    \overline{p}(x) > 0$),
+  \item The set $\ncone{p}{x} = \cone{\{∇p(x)\} ∪ \{∇ᵢ^σp, (i,σ) ∈ I(x)\}}$
+  \item The set $\nhull{p}{x} = \hull{\{∇p(x)\} ∪ \{∇ᵢ^σp, (i,σ) ∈ I(x)\}}$
+\end{itemize}
 \end{defi}
@@
 \begin{enumerate}
-\item $∀x ∈  ℝ^{n+1}∖\{0\}, Π(x) \hbox{ or } 0 ∉ \cone{\{∇p(x)\} ∪ \{∇ᵢ^σp, (i,σ) ∈ I(x)\}}$
-\item $∀x ∈  ℝ^{n+1}∖\{0\}, Π(x) \hbox{ or } 0 ∉ \hull{\{∇p(x)\} ∪ \{∇ᵢ^σp, (i,σ) ∈ I(x)\}}$
-\item $∀x ∈  \SNR, Π(x) \hbox{ or } 0 ∉ \cone{\{∇p(x)\} ∪ \{∇ᵢ^σp, (i,σ) ∈ I(x)\}}$
-\item $∀x ∈  \SNR, Π(x) \hbox{ or } 0 ∉ \hull{\{∇p(x)\} ∪ \{∇ᵢ^σp, (i,σ) ∈ I(x)\}}$
-\item\label{hb} $∀x ∈  ℝ^{n+1}∖\{0\}, Π(x) \hbox{ or } ∃δ ∈ ℝ^{n+1}∖\{0\},
+\item $∀x ∈  ℝ^{n+1}∖\{0\}, Π_p(x) \hbox{ or } 0 ∉ \ncone{p}{x}$
+\item $∀x ∈  ℝ^{n+1}∖\{0\}, Π_p(x) \hbox{ or } 0 ∉ \nhull{p}{x}$
+\item $∀x ∈  \SNR, Π_p(x) \hbox{ or } 0 ∉ \ncone{p}{x}$
+\item $∀x ∈  \SNR, Π_p(x) \hbox{ or } 0 ∉ \nhull{p}{x}$
+\item\label{hb} $∀x ∈  ℝ^{n+1}∖\{0\}, Π_p(x) \hbox{ or } ∃δ ∈ ℝ^{n+1}∖\{0\},
   \left\{\begin{array}{l} δ.∇p(x) > 0 \hbox{ and}\cr
@@
 $ℝ^{n+1}$. Let $(Δᵢ)_{i∈I}$ be a simplicial partition of $\PNR$.
-
-We say that the partition is \emph{adapted} to $p$ if it satisfies the condition
+We say that the partition is \emph{adapted} to $p$ if it satisfies the conditions
 of proposition \ref{adaptedeq}.
@@
 
-\begin{prop}
+\begin{coro}
   Let $p$ be an homogeneous polynomial of degree $d$ on
-$ℝ^{n+1}$.
-  Let $(Δᵢ)_{i∈I}$ be a simplicial partition of $\PNR$ adapted to $p$.
-  We can find a $C^∞$ function $δ$ in $ℝ^{n+1} ∖ \{0\} → ℝ^{n+1}∖\{0\} $
-  and $μ > 0$ such that:
-  $$∀x ∈  ℝ^{n+1}∖\{0\}, Π(x) \hbox{ or } \left\{
-  \begin{array}{l}δ(x).∇p(x) > μ\|x\|^{d-1} \hbox{ and } \cr ∀(i,σ) ∈
-  I(x), δ(x).∇ᵢ^σp > μ.\end{array}\right.
-  $$
-\end{prop}
+  $ℝ^{n+1}$. Let $(Δᵢ)_{i∈I}$ be a simplicial partition of $\PNR$ adapted to $p$.
+  Then, the zero-locus of $p$ and $\overline{p}$ the $\Delta$ approximation of
+  $p$ are isomorphic.
+\end{coro}
 
-\begin{proof}
-From proposition \ref{adaptedeq}.\ref{hb}, for any $x ∈ ℝ^{n+1}∖\{0\}$, if
-$Π_ε(x)$ is not satisfied, we find $δ₀(x)
-∈ ℝ^{n+1}$ such that $δ₀(x).∇p(x) > 0$ and $∀(i,σ) ∈ I_ε(x), δ₀(x).∇ᵢ^σp > 0$.
-We can also assume that $δ₀(λ x) = δ₀(x)$ for $λ > 0$ for the same reason as in
-the proof of $(1) ↔ (3)$ above.
+This theorem is a consequence of the theorem \ref{maintheo} to come.
 
-We start with the following lemma: for each $x ∈
-ℝ^{n+1}∖\{0\}$, we find $0 < η(x) < ε$ such that
-$∀y ∈ \ball{x}{2η(x)}$, $d₀(x).∇p(y) > 0$ and $∀(i,σ) ∈ I_ε(y),
-d₀(x).∇ᵢ^σp > 0$.
+\begin{defi}
+Let $p_1,\dots,p_k$ be $k$ homogeneous polynomial of degree $d_1,\dots,d_k$ on
+$ℝ^{n+1}$. Let $(Δᵢ)_{i∈I}$ be a simplicial partition of $\PNR$.
 
-First, $(i,σ) ∈ I_ε(y) ↔ \cball{y}{ε} ∩ Δᵢ^σ ≠ ∅$ is a closed condition and the
-contrary is an open condition. The condition $Π_ε(x)$ is also an open
-condition. Hence, for $x ∈ℝ^{n+1}∖\{0\}$, we find $η > 0$
-small enough to have $y ∈
-\ball{x}{2η}$ gives $Π_ε(x)$ or $(i,σ) ∉ I_ε(x)$ implies $(i,σ) ∉ I_ε(y)$.
+We say that the partition is \emph{adapted} to $p_1,\dots,p_k$ if it satisfies
+the following condition: for all $x \in ℝ^{n+1}$, either $\Pi_{p_j}(x)$ is true
+for some $1 \leq j \leq k$ or $\ncone{p₁}{x} × \dots × \ncone{pₖ}{x}$ contains
+only linear independant tuple of vectors.
+\end{defi}
 
-which means that
-for $y ∈ \ball{x}{2η}$, we have $Π_ε(x)$ or $I_ε(y) ⊆ I_ε(x)$ and therefore,
+\begin{theo}\label{maintheo}
+  Let $p_1,\dots,p_k$ be $k$ homogeneous polynomial of degree $d_1,\dots,d_k$ on
+$ℝ^{n+1}$. Let $(Δᵢ)_{i∈I}$ be a simplicial partition of $\PNR$ adapted to
+  $p₁,\dots,pₖ$. Then, the zero locus of $p₁,\dots,pₙ$ is isomorphic to the zero
+  locus of $\overline{p}₁,\dots,\overline{p}ₖ$.
+\end{theo}
 
-$$∀y ∈ \ball{x}{2η(x)}, Π_ε(x) \hbox{ or } ∀(i,σ) ∈ I_ε(y), δ₀(x).∇ᵢ^σp > 0.$$
-
-Second, $∇p(x)$ is continuous, thus for  $x ∈ℝ^{n+1}∖\{0\}$, we find $η > 0$
-small enough to have $y ∈ \ball{x}{2η}$
-implies $Π_ε(x)$ or $δ₀(x).∇p(y) > 0$. Grouping both results yields the wanted real $η(x)$
-such that
-
-$$∀x ∈ℝ^{n+1}∖\{0\}, ∀y ∈ \ball{x}{2η(x)}, Π_ε(x) \hbox{ or }
-\left\{\begin{array}{l} δ₀(x).∇p(y) > 0 \hbox{ and}\cr
-∀(i,σ) ∈ I_ε(y), δ₀(x).∇ᵢ^σp > 0
-\end{array}\right.
-$$
-
-Now, for $x ∈ \SNR$, the open balls $\ball{x}{η(x)}$ cover $\SNR$, so we can
-find a finite family $(xⱼ)_{j∈J}$ such that the balls $\ball{x}{η(xⱼ)}$ cover
-$\SNR$. We also take $η = \min_{j ∈ J} η(xⱼ)$.
-
-Next, for each $xⱼ ∈ \SNR$, $j ∈ J$, we choose a measurable set
-$Dⱼ ⊂ \ball{x}{η(xⱼ)}$ such that $\SNR$ is a disjoin union of all
-$Dⱼ$. And we define $d₁ : \SNR → ℝ^{n+1}∖\{0\}$ with $δ₁(x) = δ₀(xⱼ)$ if $x ∈ Dⱼ$.
-
-We choose $s : ℝ^{n+1} → ℝ$, a $C^∞$ function with support in
-$\ball{0}{1}$ and $∫_{ℝ^{n+1}} s(t) dt = 1$ for the standard measure $dt$
-on $ℝ^{n+1}$.
-
-We define
-
-$$ δ : \SNR → ℝ^{n+1}∖\{0\} \hbox{ with } δ(x) = ∫_{ℝ^{n+1}} δ₁(x - η t)
-s(t) dt$$
-
-Similarly to a convolution product, using the change of variable $u = x - ηt$, we have $δ(x) = ∫_{ℝ^{n+1}} η^{n +1} δ₁(u)
-s(\frac{x - u}{η}) du$ and therefore $δ$ is $C^∞$ on $\SNR$.
-
-Moreover, if we take $x ∈ \SNR$, we can write
-$$ δ(x) = Σ_{j∈J} δ₁(xⱼ) ∫_{x - η t ∈ Dⱼ} s(t) dt$$
-
-Let us define $λⱼ(x) = ∫_{x - η t ∈ Dⱼ} s(t) dt$. As $Dⱼ ⊂ \ball{xⱼ}{η(xⱼ)}$,
-if $λⱼ(x) > 0$, we have $d(x - η t,xⱼ) ≤ η(xⱼ)$ otherwise $x  - η t ∉ Dⱼ$
-and $d(x, x - η t) < η ≤ η(xⱼ)$ otherwise $s(t) = 0$. Therefore,
-if $λⱼ(x) > 0$, we have $d(x,xⱼ) < 2η(xⱼ)$.
-which implies $Π_ε(x)$ or both $δ₁(xⱼ).∇p(x) > 0$ and $∀(i,σ) ∈ I_ε(x), δ₁(xⱼ).∇ᵢ^σp > 0$.
-
-Moreover, the coefficient $λⱼ$ are positive. Therefore, $δ(x) = Σ_{j∈J}
-λⱼ(x) δ₁(xⱼ)$ implies $δ(x).∇p(x) > 0$ and $∀(i,σ) ∈ I_ε(x), δ(x).∇ᵢ^σp >
-0$.  Thus, we have:
-$$∀x ∈ \SNR, Π_ε(x) \hbox{ or } δ(x).∇p(x) > 0 \hbox{ and }∀(i,σ) ∈
-  I_ε(x), δ(x).∇ᵢ^σp > 0.$$
-
-  As $\SNR$ is compact, we can find $μ > 0$ such that
-$$∀x ∈ \SNR, Π_ε(x) \hbox{ or } δ(x).∇p(x) > μ \hbox{ and }∀(i,σ) ∈
-  I_ε(x), δ(x).∇ᵢ^σp > μ.$$
-
-  To extend this to $ℝ^{n+1}∖\{0\}$, we just have to set $δ(λx) = δ(x)$ for $λ >
-  0$ and as $p$ is homogeneous of degree $d$, we have:
-
-  $$∀x ∈  ℝ^{n+1} ∖ \{0\}, Π_ε(x) \hbox{ or } \left\{\begin{array}{l}
-  δ(x).∇p(x) > μ\|x\|^{d-1} \hbox{ and }\cr∀(i,σ) ∈
-  I_ε(x), δ(x).∇ᵢ^σp > μ
-  \end{array}\right.$$
-\end{proof}
-
-\begin{prop}
-  Let $p$ be an homogeneous polynomial of degree $d$ on
-$ℝ^{n+1}$.
-  Let $(Δᵢ)_{i∈I}$ be an $ε$-fat simplicial partition of $\PNR$ adapted to $p$.
-  the function  $p$ and $\overline{p}$ have homeomorphic zero locus on
-  $ℝ^{n+1}∖\{0\}$.
-\end{prop}
-
-\begin{proof}
-  The function $\overline{p}$ as a gradient defined in any direction $d$ which
-  may be defined as
-  $$
-  \nabla \overline{p}(x). d = \lim_{h → 0⁺} \frac{\overline{p}(x + hd) - \overline{p}(x)}{h}
-  $$
-  This is true because for $h > 0$ and small enough, $x + hd$ and $x$ belong to
-  at least one common cone $Δᵢ^σ$ with $(i, σ) ∈ I(x)$.
-  If they both belong to more than one cone, as we take the gradient of linear
-  functions that coincide on the intersection of several simplex in a direction which
-  is parallel to this intersection, the gradient $∇ᵢ^σp . d$ coincide and are the limit.
-  This tells us moreover that we have
-  $$\nabla \overline{p}(x). d = ∇ᵢ^σp . d \hbox{ for some }
-  (i, σ) ∈ I(x).$$
-
-  Next, we Consider the differential equation $x'(t) = δ(x(t))$.
-  This differential equation has
-  unique solutions in the neighbourhood of $x$ because $δ$ is $C^∞$.
-
-  Now consider a closed and connnected region $Ω$ of $ℝ^{n+1} ∖ \{0\}$
-  where $p(x) ≤ 0$ and $\overline{p}(x) ≥ 0$, and a maximal solution
-  $x : L → Ω$ with $0$ in the interior of the interval $L$ and $x(0)$ in
-  the interior of $Ω$. The same reasoning will apply in region where $p(x) ≥ 0$
-  and $\overline{p}(x) ≤ 0$.
-
-  We define $\|p\| = max_{x ∈ \SNR} |p(x)|$ and  $\|\overline{p}\| = max_{x ∈
-    \SNR} |\overline{p}(x)|$.
-
-  From the definition of this region,
-  no $x ∈ Ω$ satisfies the condition $Π_ε(x)$. Hence we have
-  $d(x). ∇p(x) > μ\|x\|^{d-1} > 0$, so the solution is increasing in $p$.
-  Similarly, $∀(i,σ) ∈ I_ε(x), d(x). ∇ᵢ^σ > μ > 0$, hence the solution is also
-  increasing in $\overline{p}$.
-
-  Therefore, for $t < 0$, we have $|p(x(0))| < |p(x(t))| < \|p\| \|x(t)\|ᵈ$.
-  for $t > 0$, we have  $|\overline{p}(x(0))| < |\overline{p}(x(t))| <
-  \|\overline{p}\| \|x(t)\|$.
-  Let use take $R = min(\frac{\overline{p}(x(0))}{\|\overline{p}\|},
-  \left(\frac{p(x(0))}{\|p\|}\right)^{\frac{1}{d}})$,
-  we have $\|x(t)\| > R$.   This exludes solution converging to $0$.
-
-  Next, consider $f(t) = p(x(t))$, $f'(t) = ∇p(x(t)).δ(x(t)) > μ R^{d-1} $
-  Therefore $f(t) - f(0) >  ∫₀ᵗ f'(t) dt > t μ R^{d-1}$. Therefore $p(x(t)$
-  reaches the zero locus of $p$ for $0 < t < - f(0) / μ R^{d-1}$.
-  It will also reach  the zero locus of $\overline{p}$ for $0 > t > - f(0) / μ$.
-  This excludes all solution with unbounded interval definition.
-
-  From this we can define the homeomorphism $ϕ$ between the zero loci of $p$ and
-  and $\overline{p}$. Consider a point $x₀$ such that $p(x₀) = 0$. If
-  $\overline{p}(x₀) = 0$, we take $ϕ(x₀) = x₀$. If $\overline{p}(x₀) < 0$, we
-  consider the solution of the equation $x'(t) = δ(x(t))$, with $x(0) = x₀$.
-  This solution reaches $\overline{p}(x(t))$ for some $t₁ < 0$ and we take
-  $ϕ(x₀) = x(t₁)$. If $\overline{p}(x₀) > 0$, we
-  consider the solution of the equation $x'(t) = δ(x(t))$, with $x(0) = x₀$.
-  This solution reaches $\overline{p}(x(t))$ for some $t₁ > 0$ and we take
-  $ϕ(x₀) = x(t₁)$.
-
-  The function $ϕ$ is bijective, because its inverse can be constructed in the
-  same way and solution of the differential equation is unique. And it is
-  $C^∞$ because $δ$ is $C^∞$.
-\end{proof}
+We will prove our main theorem is the next two sections. The rest of the paper
+explains how to test that a simplicial partition is adapted to a finite set of
+polynomials.
 

### 2021-06-15 article/attic.tex
work on article

@@
+We say that the partition is \emph{adapted} to $p$ if it satisfies the condition
+of proposition \ref{adaptedeq}.
+\begin{prop}
+  Let $p$ be an homogeneous polynomial of degree $d$ on
+$ℝ^{n+1}$.
+  Let $(Δᵢ)_{i∈I}$ be a simplicial partition of $\PNR$ adapted to $p$.
+  We can find a $C^∞$ function $δ$ in $ℝ^{n+1} ∖ \{0\} → ℝ^{n+1}∖\{0\} $
+  and $μ > 0$ such that:
+  $$∀x ∈  ℝ^{n+1}∖\{0\}, Π(x) \hbox{ or } \left\{
+  \begin{array}{l}δ(x).∇p(x) > μ\|x\|^{d-1} \hbox{ and } \cr ∀(i,σ) ∈
+  I(x), δ(x).∇ᵢ^σp > μ.\end{array}\right.
+  $$
+\end{prop}
+
+\begin{proof}
+From proposition \ref{adaptedeq}.\ref{hb}, for any $x ∈ ℝ^{n+1}∖\{0\}$, if
+$Π_ε(x)$ is not satisfied, we find $δ₀(x)
+∈ ℝ^{n+1}$ such that $δ₀(x).∇p(x) > 0$ and $∀(i,σ) ∈ I_ε(x), δ₀(x).∇ᵢ^σp > 0$.
+We can also assume that $δ₀(λ x) = δ₀(x)$ for $λ > 0$ for the same reason as in
+the proof of $(1) ↔ (3)$ above.
+
+We start with the following lemma: for each $x ∈
+ℝ^{n+1}∖\{0\}$, we find $0 < η(x) < ε$ such that
+$∀y ∈ \ball{x}{2η(x)}$, $d₀(x).∇p(y) > 0$ and $∀(i,σ) ∈ I_ε(y),
+d₀(x).∇ᵢ^σp > 0$.
+
+First, $(i,σ) ∈ I_ε(y) ↔ \cball{y}{ε} ∩ Δᵢ^σ ≠ ∅$ is a closed condition and the
+contrary is an open condition. The condition $Π_ε(x)$ is also an open
+condition. Hence, for $x ∈ℝ^{n+1}∖\{0\}$, we find $η > 0$
+small enough to have $y ∈
+\ball{x}{2η}$ gives $Π_ε(x)$ or $(i,σ) ∉ I_ε(x)$ implies $(i,σ) ∉ I_ε(y)$.
+
+which means that
+for $y ∈ \ball{x}{2η}$, we have $Π_ε(x)$ or $I_ε(y) ⊆ I_ε(x)$ and therefore,
+
+$$∀y ∈ \ball{x}{2η(x)}, Π_ε(x) \hbox{ or } ∀(i,σ) ∈ I_ε(y), δ₀(x).∇ᵢ^σp > 0.$$
+
+Second, $∇p(x)$ is continuous, thus for  $x ∈ℝ^{n+1}∖\{0\}$, we find $η > 0$
+small enough to have $y ∈ \ball{x}{2η}$
+implies $Π_ε(x)$ or $δ₀(x).∇p(y) > 0$. Grouping both results yields the wanted real $η(x)$
+such that
+
+$$∀x ∈ℝ^{n+1}∖\{0\}, ∀y ∈ \ball{x}{2η(x)}, Π_ε(x) \hbox{ or }
+\left\{\begin{array}{l} δ₀(x).∇p(y) > 0 \hbox{ and}\cr
+∀(i,σ) ∈ I_ε(y), δ₀(x).∇ᵢ^σp > 0
+\end{array}\right.
+$$
+
+Now, for $x ∈ \SNR$, the open balls $\ball{x}{η(x)}$ cover $\SNR$, so we can
+find a finite family $(xⱼ)_{j∈J}$ such that the balls $\ball{x}{η(xⱼ)}$ cover
+$\SNR$. We also take $η = \min_{j ∈ J} η(xⱼ)$.
+
+Next, for each $xⱼ ∈ \SNR$, $j ∈ J$, we choose a measurable set
+$Dⱼ ⊂ \ball{x}{η(xⱼ)}$ such that $\SNR$ is a disjoin union of all
+$Dⱼ$. And we define $d₁ : \SNR → ℝ^{n+1}∖\{0\}$ with $δ₁(x) = δ₀(xⱼ)$ if $x ∈ Dⱼ$.
+
+We choose $s : ℝ^{n+1} → ℝ$, a $C^∞$ function with support in
+$\ball{0}{1}$ and $∫_{ℝ^{n+1}} s(t) dt = 1$ for the standard measure $dt$
+on $ℝ^{n+1}$.
+
+We define
+
+$$ δ : \SNR → ℝ^{n+1}∖\{0\} \hbox{ with } δ(x) = ∫_{ℝ^{n+1}} δ₁(x - η t)
+s(t) dt$$
+
+Similarly to a convolution product, using the change of variable $u = x - ηt$, we have $δ(x) = ∫_{ℝ^{n+1}} η^{n +1} δ₁(u)
+s(\frac{x - u}{η}) du$ and therefore $δ$ is $C^∞$ on $\SNR$.
+
+Moreover, if we take $x ∈ \SNR$, we can write
+$$ δ(x) = Σ_{j∈J} δ₁(xⱼ) ∫_{x - η t ∈ Dⱼ} s(t) dt$$
+
+Let us define $λⱼ(x) = ∫_{x - η t ∈ Dⱼ} s(t) dt$. As $Dⱼ ⊂ \ball{xⱼ}{η(xⱼ)}$,
+if $λⱼ(x) > 0$, we have $d(x - η t,xⱼ) ≤ η(xⱼ)$ otherwise $x  - η t ∉ Dⱼ$
+and $d(x, x - η t) < η ≤ η(xⱼ)$ otherwise $s(t) = 0$. Therefore,
+if $λⱼ(x) > 0$, we have $d(x,xⱼ) < 2η(xⱼ)$.
+which implies $Π_ε(x)$ or both $δ₁(xⱼ).∇p(x) > 0$ and $∀(i,σ) ∈ I_ε(x), δ₁(xⱼ).∇ᵢ^σp > 0$.
+
+Moreover, the coefficient $λⱼ$ are positive. Therefore, $δ(x) = Σ_{j∈J}
+λⱼ(x) δ₁(xⱼ)$ implies $δ(x).∇p(x) > 0$ and $∀(i,σ) ∈ I_ε(x), δ(x).∇ᵢ^σp >
+0$.  Thus, we have:
+$$∀x ∈ \SNR, Π_ε(x) \hbox{ or } δ(x).∇p(x) > 0 \hbox{ and }∀(i,σ) ∈
+  I_ε(x), δ(x).∇ᵢ^σp > 0.$$
+
+  As $\SNR$ is compact, we can find $μ > 0$ such that
+$$∀x ∈ \SNR, Π_ε(x) \hbox{ or } δ(x).∇p(x) > μ \hbox{ and }∀(i,σ) ∈
+  I_ε(x), δ(x).∇ᵢ^σp > μ.$$
+
+  To extend this to $ℝ^{n+1}∖\{0\}$, we just have to set $δ(λx) = δ(x)$ for $λ >
+  0$ and as $p$ is homogeneous of degree $d$, we have:
+
+  $$∀x ∈  ℝ^{n+1} ∖ \{0\}, Π_ε(x) \hbox{ or } \left\{\begin{array}{l}
+  δ(x).∇p(x) > μ\|x\|^{d-1} \hbox{ and }\cr∀(i,σ) ∈
+  I_ε(x), δ(x).∇ᵢ^σp > μ
+  \end{array}\right.$$
+\end{proof}
+
+\begin{prop}
+  Let $p$ be an homogeneous polynomial of degree $d$ on
+$ℝ^{n+1}$.
+  Let $(Δᵢ)_{i∈I}$ be an $ε$-fat simplicial partition of $\PNR$ adapted to $p$.
+  the function  $p$ and $\overline{p}$ have homeomorphic zero locus on
+  $ℝ^{n+1}∖\{0\}$.
+\end{prop}
+
+\begin{proof}
+  The function $\overline{p}$ as a gradient defined in any direction $d$ which
+  may be defined as
+  $$
+  \nabla \overline{p}(x). d = \lim_{h → 0⁺} \frac{\overline{p}(x + hd) - \overline{p}(x)}{h}
+  $$
+  This is true because for $h > 0$ and small enough, $x + hd$ and $x$ belong to
+  at least one common cone $Δᵢ^σ$ with $(i, σ) ∈ I(x)$.
+  If they both belong to more than one cone, as we take the gradient of linear
+  functions that coincide on the intersection of several simplex in a direction which
+  is parallel to this intersection, the gradient $∇ᵢ^σp . d$ coincide and are the limit.
+  This tells us moreover that we have
+  $$\nabla \overline{p}(x). d = ∇ᵢ^σp . d \hbox{ for some }
+  (i, σ) ∈ I(x).$$
+
+  Next, we Consider the differential equation $x'(t) = δ(x(t))$.
+  This differential equation has
+  unique solutions in the neighbourhood of $x$ because $δ$ is $C^∞$.
+
+  Now consider a closed and connnected region $Ω$ of $ℝ^{n+1} ∖ \{0\}$
+  where $p(x) ≤ 0$ and $\overline{p}(x) ≥ 0$, and a maximal solution
+  $x : L → Ω$ with $0$ in the interior of the interval $L$ and $x(0)$ in
+  the interior of $Ω$. The same reasoning will apply in region where $p(x) ≥ 0$
+  and $\overline{p}(x) ≤ 0$.
+
+  We define $\|p\| = max_{x ∈ \SNR} |p(x)|$ and  $\|\overline{p}\| = max_{x ∈
+    \SNR} |\overline{p}(x)|$.
+
+  From the definition of this region,
+  no $x ∈ Ω$ satisfies the condition $Π_ε(x)$. Hence we have
+  $d(x). ∇p(x) > μ\|x\|^{d-1} > 0$, so the solution is increasing in $p$.
+  Similarly, $∀(i,σ) ∈ I_ε(x), d(x). ∇ᵢ^σ > μ > 0$, hence the solution is also
+  increasing in $\overline{p}$.
+
+  Therefore, for $t < 0$, we have $|p(x(0))| < |p(x(t))| < \|p\| \|x(t)\|ᵈ$.
+  for $t > 0$, we have  $|\overline{p}(x(0))| < |\overline{p}(x(t))| <
+  \|\overline{p}\| \|x(t)\|$.
+  Let use take $R = min(\frac{\overline{p}(x(0))}{\|\overline{p}\|},
+  \left(\frac{p(x(0))}{\|p\|}\right)^{\frac{1}{d}})$,
+  we have $\|x(t)\| > R$.   This exludes solution converging to $0$.
+
+  Next, consider $f(t) = p(x(t))$, $f'(t) = ∇p(x(t)).δ(x(t)) > μ R^{d-1} $
+  Therefore $f(t) - f(0) >  ∫₀ᵗ f'(t) dt > t μ R^{d-1}$. Therefore $p(x(t)$
+  reaches the zero locus of $p$ for $0 < t < - f(0) / μ R^{d-1}$.
+  It will also reach  the zero locus of $\overline{p}$ for $0 > t > - f(0) / μ$.
+  This excludes all solution with unbounded interval definition.
+
+  From this we can define the homeomorphism $ϕ$ between the zero loci of $p$ and
+  and $\overline{p}$. Consider a point $x₀$ such that $p(x₀) = 0$. If
+  $\overline{p}(x₀) = 0$, we take $ϕ(x₀) = x₀$. If $\overline{p}(x₀) < 0$, we
+  consider the solution of the equation $x'(t) = δ(x(t))$, with $x(0) = x₀$.
+  This solution reaches $\overline{p}(x(t))$ for some $t₁ < 0$ and we take
+  $ϕ(x₀) = x(t₁)$. If $\overline{p}(x₀) > 0$, we
+  consider the solution of the equation $x'(t) = δ(x(t))$, with $x(0) = x₀$.
+  This solution reaches $\overline{p}(x(t))$ for some $t₁ > 0$ and we take
+  $ϕ(x₀) = x(t₁)$.
+
+  The function $ϕ$ is bijective, because its inverse can be constructed in the
+  same way and solution of the differential equation is unique. And it is
+  $C^∞$ because $δ$ is $C^∞$.
+\end{proof}
+
 $$f_{ε,u,v}(x) = v p(x) + u \|x\|^{d-1} ∫ f(x - ε v \|x\| t) s(t) dt  $$

### 2021-06-15 article/conventions.tex
work on article

@@
 
-We use the following notation for simplices:
+We use the following notation for closed simplices:
 \begin{itemize}
-\item If $Δ ⊂ \PNR$ is a simplex, we denote $\vertices{Δ} ⊂ \SNR$ a finite set of
+\item If $Δ ⊂ \PNR$ is a closed simplex, we denote $\vertices{Δ} ⊂ \SNR$ a finite set of
   representatives of the vertices of $Δ$.

### 2021-06-15 article/lipshitz.tex
work on article

\section{A variation on Cauchy-Lipschitz theorem}

To prove our main theorem we need a theorem of existence and uniqueness
of solutions for ordinary differential equations that accepts non continuous
function for $t=0$. Here is our lemma:

\begin{lemm}
  Let $Ω$ be a compact set in a Banach space with a norm $\|.\|$.  Let $f$ be a
  function in $]0,1] × Ω → Ω$. We assume that $f$ is $(L,α)$-Lipschitz for
  some $L > 0$ and $α ≥ 0$ which we define by:

  \begin{enumerate}
  \item $f$ is continuous and bounded on $]0,1] × Ω$,
  \item $∀t ∈ ]0,1], ∀x,y ∈ Ω, \|f(t,y) - f(t,x)\| ≤ \frac{L}{tᵅ} \|y - x\|$ and
  \end{enumerate}

  Then, the differential equation
  \begin{eqnarray}
    x'(t) = f(t,x(t)) \label{lipschitz-diffeq}
  \end{eqnarray}
  has unique maximal
  solution defined for $t ∈ [0,1]$ for any initial condition $x(t₀) = x₀ ∈ Ω$
  with $t₀ ∈ [0,1]$. This solutions are of class ${\cal C}¹$
\end{lemm}

\begin{proof}

We remark that if $f$ is $(L,α)$-Lipschitz on $[0,1] × Ω$ then it
is $\frac{L}{tᵅ}$-Lipschitz on $[t,1] × Ω$ for any $t ∈ ]0,1[$.

This proves by the standard Cauchy-Lipschitz result that for any initial condition
$x(t₀) = x₀ ∈ Ω$ with $t₀ ∈ ]0,1]$, we have a unique solution on $[t,1]$ for
        any $0 < t < t₀$ and therefore a unique solution in $]0,1]$. Then, as
            $f$ is bounded on $[0,1] × Ω$ and by compacity $x(t)$ and $x'(t)$
            both admit a limit in $t = 0$ and the limit of the latter is the
            derivative of $x$ in $0$ by
            the usual result on the limit of derivatives.

It remains to show the existance and unicity of solutions for initial conditions
in $0$.

We define $n₁(t) = t^{2L}$ and $n_α(t) = e^{-\frac{2L}{α-1} t^{1-α}}$ when $α ≥
0$ and $α ≠ 1$.
In all cases, we have  $n'_α(t) = \frac{2L}{tᵅ} n_α(t)$. Indeed:
\begin{itemize}
\item For $α = 1$, $n'₁(t) = 2L t^{2L-1} = \frac{2L}{t} n₁(t)$
\item For $α > 0, α≠ 1$, $n'_α(t) = 2L t^{-α} e^{- \frac{2L}{α-1} t^{1-α}} = \frac{2L}{tᵅ} n_α(t)$
\end{itemize}

Then, we define the
following norms on the set of continuous functions from $[0,1]$ to $Ω$:
$$\|x\|_α = \max_{t ∈ ]0,1]} \frac{\|x(t)\|}{n_α(t)}$$

Remark: if $\|x\| = 0$ and $x(0) ≠ 0$ then, as $x$ is continuous, we can find $t
> 0$ such that $x(t) > \frac{x(0)}{2}$, hence $\|x\|_α >
\frac{x(0)}{2 n_α(t)}$ which is a contradiction. Therefore, $\|.\|_α$ is indeed
a norm.

We assume that the initial condition of the differential equation
\ref{lipschitz-diffeq} is
$x(0) = x₀ ∈ Ω$.
We define the following operator on continuous function from $[0,1]$ to
$Ω$:
$$F(x) = x₀ + ∫^t_0 f(u,x(u)).{\rm d} u$$

For ant $t ∈ ]0,1]$, we have:
\begin{eqnarray*}
  \|F(y)(t) - F(x)(t)\| &≤& ∫^t_0 \|f(u,y(u)) - f(u,x(u))\| {\rm d} u \cr
  &≤& ∫^t_0 \frac{L}{uᵅ} \|y(u) - x(u)\| {\rm d} u \cr
  &≤& \|y - x\|_α ∫^t_0 \frac{L}{uᵅ} n_α(u)  {\rm d} u \cr
  &≤& \|y - x\|_α ∫^t_0 \frac{1}{2} n'_α(u)  {\rm d} u \cr
  &≤&\frac{1}{2} \|y - x\|_α n_α(t) \cr
\|F(y) - F(x)\|_α &≤& \frac{1}{2} \|y - x\|_α
\end{eqnarray*}

Therefore, $F$ is
contracting, this ensures the existence and unicity of a fixpoint of $F$, hence
of a solution of the differentiel equation \ref{lipschitz-diffeq} with initial
condition $x(0) = x₀$. Again by compacity and boundedness of $f$ this solution
is of class ${\cal C}¹$.

\end{proof}

%% We choose $s : ℝ^{n+1} → ℝ$, a $C^∞$ function with support in
%% $\ball{0}{1}$ and $∫_{ℝ^{n+1}} s(t) dt = 1$ for the standard measure $dt$
%% on $ℝ^{n+1}$. We will use the same function $s$ in the rest of this paper.

%% \begin{lemm}
%% Let $g$ be a homogeneous continuous function of degree $d$ in $ℝ^{n+1} → ℝ$. We define
%% $f(t,x) = ∫_{ℝ^{n+1}} g(x - t ε u) s(u) {\rm d} u$.
%% Then, $\nablaₓ f$ is L-Lipschitz¹ on $\SNR$.
%% \end{lemm}

%% \begin{proof}
%%   We have
%%   \begin{eqnarray*}
%%     f(t,x) &=& ∫_{ℝ^{n+1}} g(x - t ε u) s(u) {\rm d} u \cr
%%     &=& \frac{1}{(tε)^{n+1}} ∫_{ℝ^{n+1}} g(v) s(\frac{x - v}{tε}) {\rm d} v \cr
%%     \nablaₓ f(t,x) &=&
%%     \frac{1}{(tε)^{n+2}} ∫_{ℝ^{n+1}} g(v) ∇s(\frac{x - v}{tε}) {\rm d} v \cr
%%   \end{eqnarray*}
%% \end{proof}

### 2021-06-15 article/partition.tex
article
work on article

@@
     \vertices{Δᵢ}$ and $y ∈ \vertices{Δⱼ}$ with $x ≠ y$ and $\overline{x} = \overline{y}$ (see
-    the example below). This conditions ensures that the intersection of
-    simplices are exactly faces of lower dimensions defined by the common vertices.
+    the example below). This conditions ensures that an intersection of
+    simplices consists exactly in a face of lower dimensions defined by the
+    common vertices of the simplices.
 %  \item We say that $Δᵢ$ and $Δⱼ$ are neighbour if $Δᵢ ∩ Δⱼ ≠ ∅$. The neighbourhood relation is clearly reflexive and symmetric.
@@
   ℝ^{n+1} ∖\{0\}$ we define
-  $I^Δ(x) = \{(i,σ) ∈ I × \{-,+\}, x ∈ Δᵢ^σ\}$. In general we only use one
-  simplicial partition at a time and we simply write $I(x)$.
+  $I^Δ(x) = \{(i,σ) ∈ I × \{-,+\}, x ∈ Δᵢ^σ\}$.
+  We also define $I^Δ(x,ε) = \{(i,σ) ∈ I × \{-,+\}, \ball(x,ε) ∩ Δᵢ^σ ≠ \{\}\}$.
+
+  In general we only use one
+  simplicial partition at a time and we simply write $I(x)$ and $I(x,ε)$.
 \end{defi}
@@
   Let $(Δᵢ)_{i∈I}$ be a simplicial partition of $\PNR$.
-  For $x ∈  ℝ^{n+1} ∖\{0\}$ and $λ > 0$, we have $I(λx) = I(x)$.
+  For $x ∈  ℝ^{n+1} ∖\{0\}$ and $λ > 0$, we have $I(λx) = I(x)$ and $I(λx,λε) = I(x,ε)$.
 \end{prop}
@@
 
+\begin{defi}
+  Let $(Δᵢ)_{i∈I}$ be a simplicial partition of $\PNR$.
+  We say that it is $ε$-fat if for any $x ∈ ℝ^{n+1} ∖\{0\}$
+  we have
+   $$ ⋂_{(i,σ) ∈ I(x,ε)} Δᵢ^σ ≠ ∅$$
+\end{defi}
+
+\begin{lemm}
+  Let $(Δᵢ)_{i∈I}$ be an $ε$-fat  simplicial partition of $\PNR$.
+  For any $x ∈ ℝ^{n+1} ∖\{0\}$,
+  there exists $y ∈
+  ℝ^{n+1} ∖\{0\}$, such that $I(x,ε\|x\|) = I(y)$.
+
+\end{lemm}
+
+\begin{proof}
+  First, we have $I(x,ε\|x\|) = I(x',ε)$ with $x' = \frac{x}{\|x\|}$.
+  Second, we know by definition of $ε$-fatness that $ F = ⋂_{(i,σ) ∈ I(x,ε)} Δᵢ^σ ≠
+  ∅$. By definition of simplicial partition, $πₙ(F)$ if
+  the common face to all simplicies $Δᵢ$. It suffices to take $y ∈ F$ such that
+  $πₙ(y)$ not in a face of lower dimension than $πₙ(F)$.
+\end{proof}
+
+\begin{prop} If a simplicial partition $(Δᵢ)_{i∈I}$ is $ε$-fat for $ε > 0$
+  then it is $η$-fat if $0 < η ≤ ε$.
+\end{prop}
+
+\begin{proof} From the fact that for $x ∈ ℝ^{n+1} ∖\{0\}$, $I(x,η) ⊆ I(x,ε)$ if $η ≤ ε$.
+\end{proof}
+
+\begin{prop}
+  Any \emph{simplicial partition} $(Δᵢ)_{i∈I}$ of $\PNR$ is $ε$-fat for
+  some $ε > 0$ small enough.
+\end{prop}
+
+\begin{proof}
+  First, thanks to proposition \ref{Ihomo}, we only have to check the condition
+  for $ε$-fatness in $\SNR$.
+
+  Consider a set $J ⊂ I × \{-,+\}$ with $⋂_{(i,σ)∈J} Δⱼ^σ = ∅$ (1), we first
+  prove that there exists $ε_J > 0$ such that for all $x ∈ \SNR$, $J \not⊆
+  I(x,ε_J)$. For this we assume the contrary: For any $ε>0$ there exists $x_ε
+  ∈ \SNR$ such that $J ⊆ I(x_ε,ε)$. As $\SNR$ is compact, we can extract a
+  sequence $(εₙ,xₙ)_{n ∈ \mathbb N}$ which converges to $(0,x)$ for some $x ∈
+  \SNR$, with $J ⊆ I(x_n,εₙ)$ for all $n ∈ \mathbb N$. Thus, for any $(i,σ)
+  ∈ J$ and $n ∈ \mathbb N$, we have $\ball{xₙ}{εₙ} ∩ Δᵢ^σ ≠ ∅$ which implies
+  $d(xₙ,Δᵢ^σ) < εₙ$. As $Δᵢ^σ$ are closed convex cone, this implies that $x ∈
+  Δᵢ^σ$ for any $(i,σ) ∈ J$ which contradicts the hypothesis (1).
+
+  We end the proof by remarking that the simplicial partition is $ε$-fat if we
+  take $ε$ the minimum of all $ε_J$ for $J ⊂ I$ with $∩_{(i,σ)∈J} Δᵢ^σ =
+  ∅$. This is well defined as $I$ hence his power-set are finite. Indeed, if $J
+  = I(x,ε)$, and $∩_{(i,σ)∈J} Δᵢ^σ = ∅$, then $J \not ⊆ I(x,ε_J) ⊇ I(x,ε)
+  = J$ which is contradictory.
+\end{proof}
+
 %<!-- Local IspellDict: british -->

### 2021-06-15 article/proof.tex
work on article

\section{Proof of main theorem}

In this section, we consider that $p₁,\dots,pₖ$ are homogeneous polynomial of
degree $d_1,\dots,d_k$ on $ℝ^{n+1}$ and that $(Δᵢ)_{i∈I}$ is a simplicial
partition of $\PNR$ adapted to $p₁,\dots,pₖ$ and $ε$-thin for some $ε>0$.

We also choose $s:ℝ^{n+1} → ℝ⁺$ a $C^∞$ map with support included in $B_1(0)$
and such that $∫_{ℝ^{n+1}} s(u)du = 1$ for the usual measure $du$ of
$ℝ^{n+1}$. We also assume that $s(-x) = s(x)$.

First, for $t > 0$ and $x ∈ ℝ^{n+1}$, we define $$\hat pⱼ(t,x) = ∫_{ℝ^{n+1}} \hat
pⱼ(x - tεu) s(u)du$$ If we define $fₜ(y) = \hat pⱼ(tεy)$, then $\hat pⱼ(t,x) = (fₜ ⋆
s)(\frac{x}{tε})$ where $fₜ ⋆ s$ denotes the convolution product. Therefore
$\hat pⱼ(t,x)$ is $C^∞$ for its second variable.

We prove a few lemmas about the $\hat pⱼ(t,x)$.

\begin{lemm}[Homogeneity]\label{proof-homogeneity}
  for $t > 0$ and $x ∈ ℝ^{n+1}$, $\hat pⱼ(λt,λx) = λᵈ \hat pⱼ(t,x)$.
\end{lemm}

\begin{proof}
  From the homogeneity of $\hat pⱼ$.
\end{proof}

\begin{lemm}[Derivation]\label{proof-derivation}
  \begin{eqnarray*}
    ∇ₓ pⱼ(t,x) &=& ∇ₓ ∫_{ℝ^{n+1}} \hat pⱼ(x - t ε u)s(u) du \cr
        &=& ∫_{ℝ^{n+1}} ∇\hat pⱼ(x - t ε u) s(u) du \cr
        &=& ∫_{ℝ^{n+1}} ∇\overline pⱼ(x - t ε u) |\overline{pⱼ}^{d-1}(x - tε u)| s(u) du \cr
        &=& d Σ_{(i,σ)∈I_{tε}(x)} ∇ᵢ^σpⱼ. ∫_{\Phiᵢ^σ(x,tε)} |\overline{pⱼ}^{d-1}(x - tε u)| s(u) du\cr
  \end{eqnarray*}

  As the integrals on the last line are positive, this implies that $∇ₓ pⱼ(t,x)$
  is in the convex hull of the vector $∇ᵢ^σpⱼ$ for $(i,σ)∈I_{tε}(x)$.

  \begin{eqnarray*}
    \frac{∂\hat pⱼ(t,x)}{∂t} &=& \frac{∂}{∂t} ∫_{ℝ^{n+1}} \hat pⱼ(x - t ε u)s(u) du \cr
        &=& - ε  ∫_{ℝ^{n+1}} ∇\hat pⱼ(x - t ε u) u s(u) du \cr
        &=& - εd ∫_{ℝ^{n+1}} ∇\overline pⱼ(x - t ε u) |\overline{pⱼ}^{d-1}(x -
    tε u)| u s(u) du \cr
        &=& - εd Σ_{(i,σ)∈I_{tε}(x)} ∇ᵢ^σpⱼ. ∫_{\Phiᵢ^σ(x,tε)} |\overline{pⱼ}^{d-1}(x - tε u)| u s(u) du\cr
  \end{eqnarray*}

  This implies that if $0 < t < \|x\|$ then $\frac{∂\hat pⱼ(t,x)}{∂t} < ε Kⱼ \|x\|^{d-1}$ for some
  constant $Kⱼ > 0$.
\end{lemm}

\begin{lemm}[Limit]\label{proof-limit}
  $$\lim_{t → 0} \hat pⱼ(t,x) = \hat pⱼ(x)$$
  $$\lim_{t → 0} ∇ₓ \hat pⱼ(t,x) =  d Σ_{(i,σ)∈I(x)}
  ∇ᵢ^σpⱼ. |\overline{pⱼ}^{d-1}(x)|  ∫_{\Phiᵢ^σ(x,ε)} s(u) du$$
\end{lemm}

We now consider that $∇ₓ \hat pⱼ(t,x)$ is defined on $[0,1] × ℝ^{n+1}$ using the
above limit for $t = 0$. However $∇ₓ \hat pⱼ(t,x)$ is not in general continuous
in $(0,x)$. Still it is in $∇ₓ \hat pⱼ(t,x) ∈ \ncone{pⱼ}{x}$. We will not really
use $∇ₓ \hat pⱼ(t,x)$ for $t = 0$, but it is more practical if it is defined in
$t = 0$.

\begin{proof}
  \dots
\end{proof}

\begin{lemm}
  Assume $\|x\|<1,\|y\|<1$ and $0 < t ≤ 1$, then we find a constant $L>0$ such that:
  \begin{eqnarray*}
    \|∇ₓ pⱼ(t,x) - ∇_y pⱼ(t,y)\| &=& \left\|∇ₓ ∫_{ℝ^{n+1}} \hat pⱼ(x - t ε u)s(u)
    du - ∇_y ∫_{ℝ^{n+1}} \hat
    pⱼ(y - t ε u)s(u) du \right\| \cr
    &=& \left\|∇ₓ ∫_{ℝ^{n+1}} \hat pⱼ(v)s(\frac{x-v}{tε})\frac{dv}{(tε)^{n+1}} \right.
    \cr
    && \hspace{3em} \left. - ∇_y ∫_{ℝ^{n+1}} \hat
    pⱼ(v) s(\frac{y-v}{tε}) \frac{dv}{(tε)^{n+1}} \right\| \cr
    &=& \left\|∫_{ℝ^{n+1}} \hat pⱼ(v)∇s(\frac{x-v}{tε})\frac{dv}{(tε)^{n+2}} \right.
    \cr
    && \hspace{3em} \left. - ∫_{ℝ^{n+1}} \hat
    pⱼ(v) ∇s(\frac{y-v}{tε}) \frac{dv}{(tε)^{n+2}} \right\| \cr
    &=& \frac{1}{tε} \left\|∫_{ℝ^{n+1}} \hat pⱼ(x - tεu)∇s(u) du
    - ∫_{ℝ^{n+1}} \hat
    pⱼ(y - tεu) ∇s(u) du \right\| \cr
    &≤& \frac{1}{tε} ∫_{ℝ^{n+1}} |\hat pⱼ(x - tεu) - \hat pⱼ(y - tεu)|
    \|∇s(u)\| du \cr
    &≤& L \frac{\|x-y\|}{tε}
  \end{eqnarray*}
\end{lemm}

\begin{defi}
  For $(t,x) ∈ [0,1] × ℝ^{n+1}$, we define
  \begin{itemize}
  \item $Ω$ the compact set defined by $$Ω = \{ x ∈ ℝ^{n+1}, ∀j∈\{1,\dots,k\},
    pⱼ(x) \overline{p}ⱼ(x) ≤ 0 \}$$

  \item $P(t,x)$ the vector in $ℝᵏ$ whose coefficients are
    $$Pⱼ(t,x) = t pⱼ(x) + (1-t) \hat pⱼ(t,x)$$

  \item $G(t,x) = ∇ₓ P(t,x)$ the $(n+1)×k$ matrix whose $k$ columns are the vector
    $$Gⱼ(t,x) = t ∇pⱼ(x) + (1-t) ∇ₓ \hat pⱼ(t,x)$$

  \item $Q(t,x) = \frac{∂P}{∂t}(t,x)$ the vector in $ℝᵏ$ whose coefficients are
    $$Pⱼ(t,x) = pⱼ(x) - \hat pⱼ(t,x) + (1-t) \frac{∂\hat pⱼ}{∂t}(t,x)$$
  \end{itemize}
\end{defi}

\begin{prop}
  The matrix $G(t,x)$ is of rank $k$ for $(t,x) ∈ [0,1] × Ω$ and therefore the
  $k × k$ matrix ${ᵗG}(t,x) G(t,x)$ is invertible.
\end{prop}

\begin{proof}
  From the definition of adapted simplicial partition, we have that the column
  of $G(t,x)$ are linearly independant.
\end{proof}

\begin{defi}
  We define $Gᵀ(t,x)$ the orthogonal projection of $G(t,x)$ on the tangent plane
  to the unit sphere at $x$, column by column.
\end{defi}

\begin{prop}
  We can find $ε$ small enough and a neighbourhood $Ψ$ of $[0,1] × Ω$, open for
  the topology of $[0,1] ×  ℝ^{n+1}$ such that  the matrix $Gᵀ(t,x)$ is still of
  rank $k$ for $(t,x) ∈ Ψ$.
\end{prop}

\begin{proof}
  Using the homogeneity, we get:
  \begin{eqnarray*}
    Gⱼ(t,x).x &=& t ∇pⱼ(x).x + (1-t) (∇ₓ \hat pⱼ(t,x).x) \cr
    &=& t ∇pⱼ(x).x + (1-t) (\frac{∂\hat pⱼ(t,x)}{∂t}, ∇ₓ \hat pⱼ(t,x)).(t, x) -
    t (1-t) \frac{∂\hat pⱼ}{∂}(t,x) \cr
    &=& t d pⱼ(x) + (1-t) d \hat pⱼ(t,x) - t (1-t) \frac{∂\hat pⱼ}{∂t}(t,x) \cr
    &=& d P(t,x)  - t (1-t) \frac{∂\hat pⱼ}{∂t}(t,x) \cr
  \end{eqnarray*}

  For each $x ∈ ...$, the family of matrices in $\nhull{p₁,\dots,pₖ}{x}$ are all
  of rank $k$. This family of matrix is a compact and as $\Delta$ is adapted, it
  is of rank $k$ for any $x ∈ Ω$. Moreover, being of rank $k$ is an open
  condition, therefore we can find a neighbourhood $Ψ$ of $Ω$ and a parameter
  $η$ such that for any  $x ∈ Ψ$ and any $n+1 × k$ matrices $H$ such that $\|G(t,x) - H\| < η$, then we have $H$ of rank $k$.

  Therefore, if $ε$ is small enough and $x ∈ Ψ$ we have $\|G(t,x) - Gᵀ(t,x)\| < η$
  and therefore $Gᵀ(t,x)$ of rank $k$.
\end{proof}

\begin{defi}
  For $x ∈ Ψ$, we define
  $$
  f(t,x) = - Gᵀ(t,x) ({ᵗGᵀ}(t,x) Gᵀ(t,x))^{-1} Q(t,x)
  $$
  and we consider the differential equation $$x'(t) = f(t,x(t))$$
\end{defi}

\begin{prop}
  Let $x : I → Ψ$ be a maximal solution of the above differential equation with
  the initial condition $x(t₀) = x₀$ with $P(t₀,x₀) = 0$. Then, $I = [0,1]$ and
  $P(t,x(t)) = 0$ for all $t ∈ [0,1]$.
\end{prop}

\begin{proof}
  \dots
\end{proof}
%<!-- Local IspellDict: british -->
%<!-- Local IspellPersDict: ~/.ispell-british -->

### 2021-06-17 article/lipshitz.tex
work on article

@@
 \begin{lemm}
-  Let $Ω$ be a compact set in a Banach space with a norm $\|.\|$.  Let $f$ be a
-  function in $]0,1] × Ω → Ω$. We assume that $f$ is $(L,α)$-Lipschitz for
+  Let $Ω$ be an open set of $\SNR$ for the topology of the sphere.
+  Let $f$ be a
+  function in $]0,1] × Ω → ℝ^{n+1}$ such that $f(t,x)$ is tangent to $\SNR$ at $x$. We assume that $f$ is $(L,α)$-Lipschitz for
   some $L > 0$ and $α ≥ 0$ which we define by:
@@
   \item $f$ is continuous and bounded on $]0,1] × Ω$,
-  \item $∀t ∈ ]0,1], ∀x,y ∈ Ω, \|f(t,y) - f(t,x)\| ≤ \frac{L}{tᵅ} \|y - x\|$ and
+  \item $∀t ∈ ]0,1], ∀x,y ∈ Ω, \|f(t,x) - f(t,y)\| ≤ \frac{L}{tᵅ} \|x - y\|$ and
   \end{enumerate}
@@
   \end{eqnarray}
-  has unique maximal
-  solution defined for $t ∈ [0,1]$ for any initial condition $x(t₀) = x₀ ∈ Ω$
-  with $t₀ ∈ [0,1]$. This solutions are of class ${\cal C}¹$
+  has unique maximal for any initial condition $x(t₀) = x₀ ∈ Ω$
+  with $t₀ ∈ [0,1]$. This solutions are of class ${\cal C}¹$.
+
+  Moreover, if we can prove that a solution can't converge to a point outside
+  $Ψ$, then this solution is total, i.e. defined on $[0,1]$.
 \end{lemm}
@@
 $x(t₀) = x₀ ∈ Ω$ with $t₀ ∈ ]0,1]$, we have a unique solution on $[t,1]$ for
-        any $0 < t < t₀$ and therefore a unique solution in $]0,1]$. Then, as
-            $f$ is bounded on $[0,1] × Ω$ and by compacity $x(t)$ and $x'(t)$
-            both admit a limit in $t = 0$ and the limit of the latter is the
-            derivative of $x$ in $0$ by
-            the usual result on the limit of derivatives.
+    any $0 < t < t₀$ and therefore a unique maximal solution.
+
+    It remains to show that the solution is of class ${\cal C}¹$ even in $0$.
+    If a maximal solution is defined on $]0,b]$, then by compacity and because
+        $f(t,x)$ is bounded, both $x(t)$ and $x'(t)$ have limits for $t=0$ (this
+        limit may be outside of $Ψ$).  The limit of the latter is the derivative
+        of $x$ in $0$ by the usual result on the limit of derivatives.
+        We do not have that $x'(0) = f(0,x(0))$ as $f$ is not even defined in $0$.
 
@@
 
-We define $n₁(t) = t^{2L}$ and $n_α(t) = e^{-\frac{2L}{α-1} t^{1-α}}$ when $α ≥
-0$ and $α ≠ 1$.
-In all cases, we have  $n'_α(t) = \frac{2L}{tᵅ} n_α(t)$. Indeed:
+We define $n₁(t) = t^{2L}$ and $n_α(t) = e^{-\frac{2L}{α-1} t^{1-α}}$ when $α >
+1$. In all cases, we have $n(t) → 0$ when $t → 0$ and $n'_α(t) = \frac{2L}{tᵅ}
+n_α(t)$. Indeed:
 \begin{itemize}
 \item For $α = 1$, $n'₁(t) = 2L t^{2L-1} = \frac{2L}{t} n₁(t)$
-\item For $α > 0, α≠ 1$, $n'_α(t) = 2L t^{-α} e^{- \frac{2L}{α-1} t^{1-α}} = \frac{2L}{tᵅ} n_α(t)$
+\item For $α ≥ 0, α≠ 1$, $n'_α(t) = 2L t^{-α} e^{- \frac{2L}{α-1} t^{1-α}} = \frac{2L}{tᵅ} n_α(t)$
 \end{itemize}
@@
 Then, we define the
-following norms on the set of continuous functions from $[0,1]$ to $Ω$:
-$$\|x\|_α = \max_{t ∈ ]0,1]} \frac{\|x(t)\|}{n_α(t)}$$
+following norms on the set of continuous, partial functions from $[0,1]$ to $Ω$:
+$$\|x\|_α = \max_{t ∈ ]
+0,1], x(t) \rm defined} \frac{\|x(t)\|}{n_α(t)}$$
 
@@
 $x(0) = x₀ ∈ Ω$.
-We define the following operator on continuous function from $[0,1]$ to
+We define the following operator on continuous partial function from $[0,1]$ to
 $Ω$:
-$$F(x) = x₀ + ∫^t_0 f(u,x(u)).{\rm d} u$$
+$$F(x)(t) = x₀ + ∫^t_0 f(u,x(u)).{\rm d} u$$
 
-For ant $t ∈ ]0,1]$, we have:
+For any $t ∈ ]0,1]$, we have:
 \begin{eqnarray*}
-  \|F(y)(t) - F(x)(t)\| &≤& ∫^t_0 \|f(u,y(u)) - f(u,x(u))\| {\rm d} u \cr
-  &≤& ∫^t_0 \frac{L}{uᵅ} \|y(u) - x(u)\| {\rm d} u \cr
-  &≤& \|y - x\|_α ∫^t_0 \frac{L}{uᵅ} n_α(u)  {\rm d} u \cr
-  &≤& \|y - x\|_α ∫^t_0 \frac{1}{2} n'_α(u)  {\rm d} u \cr
-  &≤&\frac{1}{2} \|y - x\|_α n_α(t) \cr
-\|F(y) - F(x)\|_α &≤& \frac{1}{2} \|y - x\|_α
+  \|F(x)(t) - F(y)(t)\| &≤& ∫^t_0 \|f(u,x(u)) - f(u,y(u))\| {\rm d} u \cr
+  &≤& ∫^t_0 \frac{L}{uᵅ} \|x(u) - y(u)\| {\rm d} u \cr
+  &≤& \|x - y\|_α ∫^t_0 \frac{L}{uᵅ} n_α(u)  {\rm d} u \cr
+  &≤& \|x - y\|_α ∫^t_0 \frac{1}{2} n'_α(u)  {\rm d} u \cr
+  &≤&\frac{1}{2} \|x - y\|_α n_α(t) \cr
+\|F(x) - F(y)\|_α &≤& \frac{1}{2} \|x - y\|_α
 \end{eqnarray*}
@@
 %% \end{proof}
+
+%<!-- Local IspellDict: british -->
+%<!-- Local IspellPersDict: ~/.ispell-british -->
